---
title: "CAREER_prelim"
author: "Katz et al."
date: "5/23/2021"
output: html_document
---






```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light() +
            theme(plot.title = element_text(hjust= 0.5, size = 9)))
```

```{r}
library(psych)
library(tidyverse)
library(tidymodels)
library(ranger)
library(purrrlyr)
library(purrr)
library(randomForest)
library(pander)
library(kableExtra)
library(knitr)
library(scales)

```



Script for creating random forests for Q5 and Q16

```{r}
setwd("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering")

# climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/updated_climate_df_2.csv")


#original data set
#climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/climate_data.csv")

# read in the imputed dataset
climate_imp_long_full <- read_csv("climate_imp_long_40_full_inf_cl_hdb_agg_20210518.csv")
```


```{r}
pub_ds_ver <- 1
climate_data <- climate_imp_long_full %>% filter(.imp == pub_ds_ver)

rm(climate_imp_long_full)

```


## Q8j


```{r}

climate_data %>% 
  ggplot(aes(x = Q8j)) + 
  geom_histogram() +
  labs(title = "Q8j")

climate_data %>% 
  ggplot(aes(x = Q8j, y = major)) +
  geom_boxplot() +
  labs(title = "Q8j")

```




## Q8n:



```{r}

climate_data %>% 
  ggplot(aes(x = Q8n)) + 
  geom_histogram() +
  labs(title = "Q8n")

climate_data %>% 
  ggplot(aes(x = Q8n, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q8n") +
  theme(legend.position = "none")

```



## Q13a

```{r}

climate_data %>% 
  ggplot(aes(x = Q13a)) + 
  geom_histogram() +
  labs(title = "Q13a")

climate_data %>% 
  ggplot(aes(x = Q13a, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q13a") +
  theme(legend.position = "none")

```



## Q13b

```{r}

climate_data %>% 
  ggplot(aes(x = Q13b)) + 
  geom_histogram() +
  labs(title = "Q13b")

climate_data %>% 
  ggplot(aes(x = Q13b, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q13b") +
  theme(legend.position = "none")

```





## Q13c

```{r}

climate_data %>% 
  ggplot(aes(x = Q13c)) + 
  geom_histogram() +
  labs(title = "Q13c")

climate_data %>% 
  ggplot(aes(x = Q13c, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q13c") +
  theme(legend.position = "none")

```



## Q14a

```{r}

climate_data %>% 
  ggplot(aes(x = Q14b)) + 
  geom_histogram() +
  labs(title = "Q14b")

climate_data %>% 
  ggplot(aes(x = Q14b, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q14b") +
  theme(legend.position = "none")

```




## Q14c

```{r}

climate_data %>% 
  ggplot(aes(x = Q14c)) + 
  geom_histogram() +
  labs(title = "Q14c")

climate_data %>% 
  ggplot(aes(x = Q14c, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q14c") +
  theme(legend.position = "none")

```



## Q14d

```{r}

climate_data %>% 
  ggplot(aes(x = Q14d)) + 
  geom_histogram() +
  labs(title = "Q14d")

climate_data %>% 
  ggplot(aes(x = Q14d, y = major)) +
  geom_boxplot(aes(fill = major)) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  labs(title = "Q14d") +
  theme(legend.position = "none")

```


Q8: Please indicate how often the following occurred in your most recent engineering design course.


Q8j = The teacher related course concepts to contemporary issues in the world
Q8n = The teacher related course concepts to helping people


Q13a = I sometimes find it difficult to see things from another person’s point of view
Q13b = I try to look at everybody’s side of a disagreement before I make a decision
Q13c = When I am upset at someone, I usually try to “put myself in their shoes” for a while



Q14a = I seek input from those with a different perspective from me
Q14b = I identify relationships between topics from different courses
Q14c = I analyze projects broadly to find a solution that will have the greatest impact
Q14d = When problem solving, I focus on the relationship between issues
Q14e = I hope to gain general knowledge across multiple fields
Q14f = I often learn from my classmates
Q14g = I seek feedback and suggestions for personal improvement


Q15: How confident are you in your ability to do the following:
Q15a = Find sources of inspiration not obviously related to a given problem
Q15b = Effectively work on a problem that does not have an obvious solution
Q15c = Change the definition of a problem you are working on
Q15d = Adapt an engineering solution for a culture different from your own
Q15e = Shape or change your external environment to help you be more creative
Q15f = Share your work with other before it is finished
Q15g = Try an approach to a problem that may not be the final or best solution
Q15h = Continue work on a problem after experiencing a significant failure
Q15i = Help others be more creative
Q15j = Identify and implement ways to enhance your own creativity
Q15k = Explicitly define or describe your creative process
Q15l = Solve problems in ways that others would consider creative



Q17: In your opinion, to what extent are the following associated with the field of engineering?
Q17a = Creating economic growth
Q17b = Preserving national security
Q17c = Improving quality of life
Q17d = Saving lives
Q17e = Caring for communities
Q17f = Protecting the environment
Q17g = Including women as participants in the field
Q17h = Including racial and ethnic minorities as participants in the field
Q17i = Addressing societal concerns
Q17j = Feeling a moral obligation to other people


Q18: To what extent do you disagree or agree with the following.
Q18a = We can pursue sustainability without lowering our standard of living
Q18b = Human ingenuity will ensure that we do not make the earth unlivable
Q18c = I feel a responsibility to deal with environmental problems
Q18d = Environmental problems make the future look hopeless
Q18e = I can personally contribute to a sustainable future
Q18f = Nothing I can do will make things better in other places on the planet
Q18g = Pursuit of sustainability will threaten jobs for people like me
Q18h = Sustainable options typically cost more
Q18i = I have the knowledge to understand most sustainability issues
Q18j = I think of myself as part of nature, not separate from it
Q18k = We should be taking stronger actions to address climate change
Q18l = Engineers are responsible for the majority of environmental problems society faces today



```{r}
Q14_vars <- paste0("Q14", letters[1:7])
Q15_vars <- paste0("Q15", letters[1:12])
Q16_vars <- paste0("Q16", letters[1:12])
Q17_vars <- paste0("Q17", letters[1:10])
Q18_vars <- paste0("Q18", letters[1:12])

select_vars <- c("student_id", "major", "Q8j", "Q8n", "Q13a", "Q13b", "Q13c",
                 Q14_vars, Q15_vars, Q17_vars, Q16_vars, Q18_vars)
```


```{r}
nested_items <- climate_data %>% 
  select(all_of(select_vars)) %>% 
  pivot_longer(cols = -c(student_id, major), names_to = "variable_name", values_to = "variable_value") %>% 
  group_by(variable_name) %>% 
  nest() %>% 
  ungroup()

nested_items


```


```{r}
# create list with full text of items
full_text_list <- c("Q8j = The teacher related course concepts to contemporary issues in the world",
                    "Q8n = The teacher related course concepts to helping people",
                    "Q13a = I sometimes find it difficult to see things from another person’s point of view",
                    "Q13b = I try to look at everybody’s side of a disagreement before I make a decision",
                    "Q13c = When I am upset at someone, I usually try to “put myself in their shoes” for a while",
                    "Q14a = I seek input from those with a different perspective from me",
                    "Q14b = I identify relationships between topics from different courses",
                    "Q14c = I analyze projects broadly to find a solution that will have the greatest impact",
                    "Q14d = When problem solving, I focus on the relationship between issues",
                    "Q14e = I hope to gain general knowledge across multiple fields",
                    "Q14f = I often learn from my classmates",
                    "Q14g = I seek feedback and suggestions for personal improvement",
                    "Q15a = Find sources of inspiration not obviously related to a given problem",
                    "Q15b = Effectively work on a problem that does not have an obvious solution",
                    "Q15c = Change the definition of a problem you are working on",
                    "Q15d = Adapt an engineering solution for a culture different from your own",
                    "Q15e = Shape or change your external environment to help you be more creative",
                    "Q15f = Share your work with other before it is finished",
                    "Q15g = Try an approach to a problem that may not be the final or best solution",
                    "Q15h = Continue work on a problem after experiencing a significant failure",
                    "Q15i = Help others be more creative",
                    "Q15j = Identify and implement ways to enhance your own creativity",
                    "Q15k = Explicitly define or describe your creative process",
                    "Q15l = Solve problems in ways that others would consider creative",
                    "Q17a = Creating economic growth",
                    "Q17b = Preserving national security",
                    "Q17c = Improving quality of life",
                    "Q17d = Saving lives",
                    "Q17e = Caring for communities",
                    "Q17f = Protecting the environment",
                    "Q17g = Including women as participants in the field",
                    "Q17h = Including racial and ethnic minorities as participants in the field",
                    "Q17i = Addressing societal concerns",
                    "Q17j = Feeling a moral obligation to other people",
                    "Q18a = We can pursue sustainability without lowering our standard of living",
                    "Q18b = Human ingenuity will ensure that we do not make the earth unlivable",
                    "Q18c = I feel a responsibility to deal with environmental problems",
                    "Q18d = Environmental problems make the future look hopeless",
                    "Q18e = I can personally contribute to a sustainable future",
                    "Q18f = Nothing I can do will make things better in other places on the planet",
                    "Q18g = Pursuit of sustainability will threaten jobs for people like me",
                    "Q18h = Sustainable options typically cost more",
                    "Q18i = I have the knowledge to understand most sustainability issues",
                    "Q18j = I think of myself as part of nature, not separate from it",
                    "Q18k = We should be taking stronger actions to address climate change",
                    "Q18l = Engineers are responsible for the majority of environmental problems society faces today")

full_text_list <- as.list(full_text_list)


```







```{r}
# nested_items$data[[1]]

```

```{r}
var_names_list <- as.list(nested_items$variable_name)
```


```{r}
purrr::map2(.x = nested_items$data, .y = full_text_list,
            ~ ggplot(.x, aes(x = variable_value)) + 
              geom_histogram() +
              facet_wrap(.~major) +
              labs(title = .y))

```



```{r}
major_num <- length(unique(nested_items$data[[1]]$major))
major_colors <- viridis_pal(begin = 0.01, end = 0.99)(major_num)


purrr::map2(.x = nested_items$data, .y = var_names_list,
           ~ ggplot(.x, aes(x = variable_value, y = major)) +
             geom_boxplot(aes(fill = .$major)) +
             geom_jitter(width = 0.1, alpha = 0.2, height = 0.3) +
             labs(title = .y,
                  x = "Variable Value",
                  y = "Major") +
             theme(legend.position = "none") +
             scale_fill_manual(values = major_colors))

```







```{r}

purrr::map2(.x = nested_items$data, .y = full_text_list,
           ~ ggplot(.x, aes(x = variable_value, y = major)) +
             geom_boxplot(aes(fill = major)) +
             geom_jitter(width = 0.1, alpha = 0.2, height = 0.3) +
             labs(title = .y,
                  x = "Variable Value",
                  y = "Major") +
             theme(legend.position = "none") +
             scale_fill_manual(values = major_colors))

```



### Sources of understanding about global climate change

```{r}


climate_data %>% 
  pivot_longer(cols = Q21a:Q21f, names_to = "Q21_item", values_to = "Q21_value") %>% 
  select(student_id, cluster_time_rank_agg, Q21_item, Q21_value) %>% 
  mutate(Cluster = as_factor(cluster_time_rank_agg)) %>% 
  ggplot(aes(x = Q21_value, y = Cluster)) +
  geom_boxplot() +
  facet_wrap(.~Q21_item)


```

```{r}


climate_data %>% 
  pivot_longer(cols = Q21a:Q21f, names_to = "Q21_item", values_to = "Q21_value") %>% 
  select(student_id, cluster_time_rank_agg, Q21_item, Q21_value) %>% 
  mutate(Cluster = as_factor(cluster_time_rank_agg),
         Q21_item = case_when(Q21_item == "Q21a" ~ "Courses",
                              Q21_item == "Q21b" ~ "Internet/Books",
                              Q21_item == "Q21c" ~ "Friend/Family",
                              Q21_item == "Q21d" ~ "Sci/Acad Pubs",
                              Q21_item == "Q21e" ~ "Climate Scientists",
                              Q21_item == "Q21f" ~ "Mainstream Media")) %>% 
  ggplot(aes(x = Q21_value)) +
  geom_bar() +
  facet_grid(Cluster ~ Q21_item) +
  labs(title = "Information Sources by Cluster",
       x = "Which has contributed most to your understanding of global climate change? (0 = Not at all, 4 = A lot",
       y = "Count")


```


```{r}
climate_data %>% 
  ggplot(aes(x = cluster_time_rank_agg, y = major)) +
  geom_boxplot()

climate_data %>% 
  ggplot(aes(x = cluster_time_rank_agg)) +
  geom_histogram() +
  facet_grid(major ~. )
```


```{r}
climate_data %>% count(major)

climate_data %>% 
  add_count(major) %>% 
  select(student_id, major, n)
```


```{r}
climate_data %>% 
  count(major)

climate_data %>% 
  group_by(major, cluster_time_rank_agg) %>% 
  summarize(major_cluster_count = n()) %>% 
  ungroup() %>% 
  group_by(major) %>% 
  add_tally(major_cluster_count, name = "major_total") %>% 
  ungroup() %>% 
  mutate(major_cluster_proportion = major_cluster_count / major_total) %>% 
  ggplot(aes(x = cluster_time_rank_agg, y = major_cluster_proportion)) +
  geom_col() +
  facet_grid(major ~.) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(x = "Spatiotemporal Belief Pattern Cluster (1 = Everything affected now, 9 = Nothing ever affected",
       y = "Proportion of Major in Each Cluster",
       title = "Spatiotemporal Belief Pattern Portions by Major")


climate_data %>% count(Q37)



```









# Ordinal forest for students feeling responsibility to deal with environmental problems




Turn the variables into factors

```{r}
# turning variables into factors


#rf_df <- dmap(rf_df, as.factor)
```


Remove additional columns that will not feed into the random forest algorithm

```{r}

# remove columns with majority na (noticed from visual inspection)
removal_vars <- c("School", "Litho", "major", "Q33_", 
                  "Q37_", "Q38_", "Q39_", "Q40", "abe", "Q16abc", "lm", "dfg", "hijk",
                  "spec", "other", "tally", "ele", "Q16_bin", "_ind")

# Q13, Q14 were originally on the removal list - not sure why - need to add back in

# consider removing "sum" from the above

removal_vars_start <- paste0("^(", paste(removal_vars, collapse="|"), ")")
removal_vars_end <- paste0("(", paste(removal_vars, collapse="|"), ")$")


# create a dataframe called train_df that we'll use for training the random forests
train_df <- climate_data %>% dplyr::select(-matches(removal_vars_start))
train_df <- train_df %>% dplyr::select(-matches(removal_vars_end))

train_df <- train_df %>% 
  dplyr::select(-Q28_tech, -Q28_social, -Q12abc, -Q12defghi)
train_df <- train_df %>% dplyr::select(-Q28_vars)
train_df <- train_df %>% dplyr::select(-Q1_vars)



# remove the original Q7 vars because they were too messy - use tallies instead

# remove other Q5 variables aside from 5e
## probably want to change this to Q16 removals

# forest_outcome_var <- "Q16d"

# Q16_removals <- Q16_vars[Q16_vars != forest_outcome_var]
# Q16_removals <- c("Q5a","Q5b", "Q5c", "Q5d", "Q5e", "Q5f", "Q5g", "Q5i", "Q5j")

train_df <- train_df %>% dplyr::select(-Q7_vars)
# train_df <- train_df %>% dplyr::select(-Q5_vars) # drop Q5 vars for Q16 training
# train_df <- train_df %>% dplyr::select(-Q16_removals)
#train_df <- train_df %>% dplyr::select(-Q16_energy)

factor_vars <- c("Q29", "Q32", "Q37")

train_df <- train_df %>% 
  mutate_at(factor_vars, as.factor)
  
  # mutate(Q29 = as.factor(Q29),
  #        Q37 = as.factor(Q37))

train_df %>% count(Q18c)

```


```{r}
extra_removal_vars <- c(".id", ".imp", "student_id", "full_hdb_cluster", "full_agg_cluster",
                        "cluster_time_rank_hdb", "cluster_avg_hdb", "cluster_avg_agg",
                        "dim1", "dim2")

train_df <- train_df %>% 
  select(-one_of(extra_removal_vars))
```




### Option 2: Ordinal Forest instead of Regression Random Forest


```{r}
train_df
```


```{r}
train_df <- train_df %>% 
  mutate(Q18c = as.ordered(Q18c))
```


```{r}


train_df %>% drop_na(Q32, Q33, Q37)

ord_rf_df <- train_df %>% 
  select(-one_of("Q30", "Q31", "Q34", "Q35", "Q36a", "Q36b", "Q38", Q39_vars, "Q40")) %>% 
  drop_na(Q32, Q33, Q37)
```


```{r}

set.seed(42)

ord_rf_df %>% select(Q18c)

ord_rf_df <- as.data.frame(ord_rf_df)
# default mtry
rf_mod_ord <- ordfor(depvar = "Q18c", 
                     data = ord_rf_df, 
                     perffunction = "proportional")


```




#### Identify top 30 most important variables for ordinal prediction

```{r}
# sort(rf_mod_ord$varimp, decreasing=TRUE)

var_imp <- rf_mod_ord$varimp
# var_imp
# names(var_imp)

var_imp_df <- tibble(variable = names(var_imp),
                     var_importance = var_imp)

```

For ordinal forest variable importance measures

```{r}

p <- var_imp_df %>% 
  top_n(30, var_importance) %>% 
  ggplot(aes(x = reorder(variable, -var_importance), y = var_importance)) +
  geom_bar(stat = "identity", fill = "#53cfff", width = 0.65) +
  coord_flip() + 
  theme_light(base_size = 20) +
  theme(axis.title.x = element_text(size = 10, color = "black"),
        axis.title.y = element_blank(),
        axis.text.x  = element_text(size = 10, color = "black"),
        axis.text.y  = element_text(size = 10, color = "black"),
        plot.title = element_text(size = 10, hjust = 0.5)) +
  ggtitle("Ordinal Forest Variable Importance for Responsibility to Deal with Environmental Problems")

p

```










