---
title: "Q16abce_modeling"
author: "Katz et al."
date: "6/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(psych)
library(tidyverse)
library(tidymodels)
library(ranger)
library(purrrlyr)
library(purrr)
library(randomForest)
library(pander)
library(kableExtra)
library(knitr)

library(mice)

library(brms)
library(tidybayes)
library(sjPlot)

```



Script for creating random forests for Q5 and Q16

```{r}
setwd("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering")

# climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/updated_climate_df_2.csv")


#original data set
#climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/climate_data.csv")

# read in the imputed dataset
climate_imp_long_full <- read_csv("climate_imp_long_40_full_inf_cl_hdb_agg_20210518.csv")
```


```{r}
pub_ds_ver <- 1
climate_data <- climate_imp_long_full %>% filter(.imp == pub_ds_ver)



```

Q14d "When problem solving I focus on the relationship between issues
```{r}
climate_data %>% 
  count(Q14d)
```





# Create a new dataframe for the random forest work

Perform EFA for Q28

```{r}



Q28_vars <- paste0("Q28", letters[1:12])


Q28_df <- climate_data %>% drop_na(Q28_vars) %>% select(Q28_vars)

Q28_fa <- fa(Q28_df, nfactors = 2, fm = "ml", rotate = "oblimin")
print(Q28_fa, cut = 0.3, digits = 3)
# use `print(fa, digits = 3)` to view FLs < .3

```

Calculate Cronbach's alpha for internal consistency reliability

```{r}


FA1 <- c("Q28a", "Q28f", "Q28g", "Q28h", "Q28i", "Q28k")
FA2 <- c("Q28c", "Q28d", "Q28e", "Q28j", "Q28l")

alpha.fa1 <- psych::alpha(Q28_df[FA1])
print(alpha.fa1, digits = 3) #0.91

alpha.fa2 <- psych::alpha(Q28_df[FA2])
print(alpha.fa2, digits = 3) #0.80


```



Add variables for Q28_tech_norm ((Q28a + Q28f + Q28g + Q28h + Q28i + Q28k) / 6) and Q28_social_norm ((Q28c + Q28d + Q28e + Q28j + Q28l) / 5)
```{r}

climate_data <- climate_data %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

```


```{r}

climate_data <- climate_data %>% 
  mutate(Q16abce = Q16a + Q16b + Q16c + Q16e)

```


From ordinal regression forest with Q16a as outcome, top predictors are:




# Bayesian modeling



Top variables from Ordinal Forest
Q18c
Q20d
Q18e
Q17f
Q18i
Q12defghi_norm
Q18k
Q18a





### Method using Bayesian ordinal regression


Add major column back to replace Q29 in regression models

```{r}
climate_data <- climate_data %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"),
         major = as_factor(major))

```


```{r}


str(climate_data$major)

# set reference discipline

climate_data$major <- fct_relevel(climate_data$major, "Mec") 

str(climate_data$major)

```



```{r}
priors1 <- set_prior("normal(0, 1)", class = "b")
```









# Modeling outcome as function of design thinking self-report and design course activities


Items to include as predictors: 
Q8b, Q8d, Q8e, Q8f, Q8g, Q8h, 
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g, 
Q18e, Q18f


## Need to relevel the predictors
Question 8 options
1 = “Never”, 2 = “Rarely”, 3 = “Monthly”, 4 = “Weekly”, 5 = “Daily”

```{r}
# First, create new variables that use text rather than numbers to indicate students' responses

climate_data <- climate_data %>% 
  mutate(Q8b_ord = case_when(Q8b == 1 ~ "Never",
                         Q8b == 2 ~ "Rarely",
                         Q8b == 3 ~ "Monthly",
                         Q8b == 4 ~ "Weekly",
                         Q8b == 5 ~ "Daily"),
         Q8d_ord = case_when(Q8d == 1 ~ "Never",
                         Q8d == 2 ~ "Rarely",
                         Q8d == 3 ~ "Monthly",
                         Q8d == 4 ~ "Weekly",
                         Q8d == 5 ~ "Daily"),
         Q8e_ord = case_when(Q8e == 1 ~ "Never",
                         Q8e == 2 ~ "Rarely",
                         Q8e == 3 ~ "Monthly",
                         Q8e == 4 ~ "Weekly",
                         Q8e == 5 ~ "Daily"),
         Q8f_ord = case_when(Q8f == 1 ~ "Never",
                         Q8f == 2 ~ "Rarely",
                         Q8f == 3 ~ "Monthly",
                         Q8f == 4 ~ "Weekly",
                         Q8f == 5 ~ "Daily"),
         Q8g_ord = case_when(Q8g == 1 ~ "Never",
                         Q8g == 2 ~ "Rarely",
                         Q8g == 3 ~ "Monthly",
                         Q8g == 4 ~ "Weekly",
                         Q8g == 5 ~ "Daily"),
         Q8h_ord = case_when(Q8h == 1 ~ "Never",
                         Q8h == 2 ~ "Rarely",
                         Q8h == 3 ~ "Monthly",
                         Q8h == 4 ~ "Weekly",
                         Q8h == 5 ~ "Daily")
         )


```

Question 14
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g
Question 14 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 

Question 18
Q18e, Q18f
Question 18 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 
```{r}

climate_data %>% count(Q14a)

climate_data <- climate_data %>% 
  mutate(Q14a_ord = case_when(Q14a == 0 ~ "Strongly disagree",
                              Q14a == 1 ~ "Disagree",
                              Q14a == 2 ~ "Neutral",
                              Q14a == 3 ~ "Agree",
                              Q14a == 4 ~ "Strongly agree"),
         Q14b_ord = case_when(Q14b == 0 ~ "Strongly disagree",
                              Q14b == 1 ~ "Disagree",
                              Q14b == 2 ~ "Neutral",
                              Q14b == 3 ~ "Agree",
                              Q14b == 4 ~ "Strongly agree"),
         Q14c_ord = case_when(Q14c == 0 ~ "Strongly disagree",
                              Q14c == 1 ~ "Disagree",
                              Q14c == 2 ~ "Neutral",
                              Q14c == 3 ~ "Agree",
                              Q14c == 4 ~ "Strongly agree"),
         Q14d_ord = case_when(Q14d == 0 ~ "Strongly disagree",
                              Q14d == 1 ~ "Disagree",
                              Q14d == 2 ~ "Neutral",
                              Q14d == 3 ~ "Agree",
                              Q14d == 4 ~ "Strongly agree"),
         Q14e_ord = case_when(Q14e == 0 ~ "Strongly disagree",
                              Q14e == 1 ~ "Disagree",
                              Q14e == 2 ~ "Neutral",
                              Q14e == 3 ~ "Agree",
                              Q14e == 4 ~ "Strongly agree"),
         Q14f_ord = case_when(Q14f == 0 ~ "Strongly disagree",
                              Q14f == 1 ~ "Disagree",
                              Q14f == 2 ~ "Neutral",
                              Q14f == 3 ~ "Agree",
                              Q14f == 4 ~ "Strongly agree"),
         Q14g_ord = case_when(Q14g == 0 ~ "Strongly disagree",
                              Q14g == 1 ~ "Disagree",
                              Q14g == 2 ~ "Neutral",
                              Q14g == 3 ~ "Agree",
                              Q14g == 4 ~ "Strongly agree"),
         Q18e_ord = case_when(Q18e == 0 ~ "Strongly disagree",
                              Q18e == 1 ~ "Disagree",
                              Q18e == 2 ~ "Neutral",
                              Q18e == 3 ~ "Agree",
                              Q18e == 4 ~ "Strongly agree"),
         Q18f_ord = case_when(Q18f == 0 ~ "Strongly disagree",
                              Q18f == 1 ~ "Disagree",
                              Q18f == 2 ~ "Neutral",
                              Q18f == 3 ~ "Agree",
                              Q18f == 4 ~ "Strongly agree"))


```




```{r}

climate_data %>% count(Q14g)
climate_data %>% count(Q14g_ord)

```



```{r}
str(climate_data$Q8b_ord)
Q8_ord_vars <- c("Q8b_ord", "Q8d_ord", "Q8e_ord", "Q8f_ord", "Q8g_ord", "Q8h_ord")
Q8_levels <- c("Never", "Rarely", "Monthly", "Weekly", "Daily")

Q14_ord_vars <- c("Q14a_ord", "Q14b_ord", "Q14c_ord", "Q14d_ord", "Q14e_ord", "Q14f_ord", "Q14g_ord")
Q14_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

Q18_ord_vars <- c("Q18e_ord", "Q18f_ord")
Q18_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

climate_data <- climate_data %>% 
  mutate_at(Q8_ord_vars, ~factor(., ordered = TRUE, levels = Q8_levels)) %>% 
  mutate_at(Q14_ord_vars, ~factor(., ordered = TRUE, levels = Q14_levels)) %>% 
  mutate_at(Q18_ord_vars, ~factor(., ordered = TRUE, levels = Q18_levels))


```


```{r}

str(climate_data$Q14d_ord)

```

```{r}

climate_data %>% count(Q14d)
climate_data %>% count(Q14d_ord)

```




#### Data Preparation for multiple imputation

```{r}
# try converting nested datasets back to a mids object (if working from the nested_imp data)
# climate_imp_long_full <- nested_imp  %>% select(.imp, data) %>% unnest()

# write this to csv to avoid having to recreate some of the Q6 items with more descriptive titles
# climate_imp_long_full %>% write_csv(paste0("climate_imp_long_hc_cl_full_40_acad_", Sys.Date(), ".csv"))


# or reading in from saved version

## version with hdbscan clusters
# climate_imp_long_full <- read_csv("climate_imp_long_cl_full_40_2021-05-01.csv") 

## version with agglomerative clusters
climate_imp_long_full <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering/climate_imp_long_hc_cl_full_40_2021-05-05.csv")
```


```{r}
# need to get .imp == 0 back to combine into mids object
climate_imp_csv <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering/climate_imputed_40_2021-05-01.csv")
climate_imp_csv <- climate_imp_csv %>% filter(.imp == 0)
```




```{r}
# convert Q40 to character (may not be necessary if reading in data)
#climate_imp_csv <- climate_imp_csv %>% mutate(Q40 = as.character(Q40))

# bind imp == 0 (the original incomplete dataset) back to the full imputed, augmented dataset
```


```{r}
# need to drop Q7a:Q7v from climat_imp_csv because they get imported as chr instead of dbl
climate_imp_csv <- climate_imp_csv %>%
  select(-(Q7a:Q7v))

```


```{r}
test_bind <- bind_rows(climate_imp_csv, climate_imp_long_full)
```


```{r}
# spot check
# test_bind %>% select(cluster_time_rank) %>% filter(cluster_time_rank == 1)
# test_bind %>% group_by(.imp) %>% summarize(n = n())
# test_bind %>% count(student_id) %>% filter(n != 41) 


# apparently student with student_id 1982 only shows up in original dataset and not the others

test_bind %>% filter(student_id == 1982) # it looks like they didn't have a Litho or a School

test_bind %>% count(student_id) %>% filter(n == 41) # this has 4363 students

# remove student with student_id 1982 
test_bind <- test_bind %>% 
  filter(student_id != 1982)



# drop a bunch of unnecessary columns (i.e., the ones from IPEDS)
```

```{r}
# just to get ipeds_vars
data_path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/"
file_name <- "ipeds_inst_char_2018.csv"

school_info <- read_csv(paste0(data_path, file_name))

ipeds_vars <- names(school_info)
rm(school_info)
```


```{r}
# drop ipeds
test_bind <- test_bind %>% 
  select(-one_of(ipeds_vars))



```

```{r}
# drop Q7 individual items

Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")
Q7wt_sum_vars <- paste0("Q7", letters[1:22], "_wt_sum")
Q7other_vars <- paste0("Q7", letters[1:22], "_other")
Q7disc_vars <- paste0("Q7", letters[1:22], "_disc_spec")
Q7eng_ele_vars <- paste0("Q7", letters[1:22], "_eng_ele")
Q7non_eng_vars <- paste0("Q7", letters[1:22], "_non_eng_ele")
```


```{r}
test_bind <- test_bind %>% 
  select(-one_of(Q7other_vars)) %>% 
  select(-one_of(Q7disc_vars)) %>% 
  select(-one_of(Q7eng_ele_vars)) %>% 
  select(-one_of(Q7non_eng_vars))



```


```{r}
# remove Q10-Q15
Q1_vars <- paste0("Q1", letters[1:20])
Q2_vars <- paste0("Q2", letters[1:7])
Q3_vars <- paste0("Q3", letters[1:7])
Q4_vars <- paste0("Q4", letters[1:16])
Q5_vars <- paste0("Q5", letters[1:10])
Q6_vars <- paste0("Q6", letters[1:11])
  


Q10_vars <- paste0("Q10", letters[1:9])
Q11_vars <- paste0("Q11", letters[1:14])
Q12_vars <- paste0("Q12", letters[1:9])
Q13_vars <- paste0("Q13", letters[1:7])
Q14_vars <- paste0("Q14", letters[1:7])
Q15_vars <- paste0("Q15", letters[1:15])

Q19_vars <- paste0("Q19", letters[1:8])
Q20_vars <- paste0("Q20", letters[1:5])
Q21_vars <- paste0("Q21", letters[1:6])
Q24_vars <- paste0("Q24", letters[1:11])
Q23_vars <- paste0("Q23", letters[1:10])

```


```{r}
test_bind <- test_bind %>% 
  select(-one_of(Q1_vars)) %>% 
  select(-one_of(Q2_vars)) %>% 
  select(-one_of(Q3_vars)) %>% 
  select(-one_of(Q4_vars)) %>% 
  select(-one_of(Q5_vars)) %>%
  select(-one_of(Q6_vars)) %>% 
  select(-one_of(Q10_vars)) %>% 
  select(-one_of(Q11_vars)) %>% 
  select(-one_of(Q12_vars)) %>% 
  select(-one_of(Q13_vars)) %>% 
  select(-one_of(Q19_vars)) %>% 
  select(-one_of(Q20_vars)) %>% 
  select(-one_of(Q21_vars)) %>% 
  select(-one_of(Q23_vars)) %>% 
  select(-one_of(Q24_vars)) %>% 
  select(-one_of(Q15_vars))



```


Add variables for Q28_tech_norm ((Q28a + Q28f + Q28g + Q28h + Q28i + Q28k) / 6) and Q28_social_norm ((Q28c + Q28d + Q28e + Q28j + Q28l) / 5)
```{r}

test_bind <- test_bind %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

```


```{r}

test_bind <- test_bind %>% 
  mutate(Q16abce = Q16a + Q16b + Q16c + Q16e)

```






### Method using Bayesian ordinal regression


Add major column back to replace Q29 in regression models

```{r}
test_bind <- test_bind %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"),
         major = as_factor(major))

```


```{r}


str(test_bind$major)

# set reference discipline

test_bind$major <- fct_relevel(test_bind$major, "Mec") 

str(test_bind$major)

```



```{r}

climate_data %>%
  #drop_na(Q37) %>% 
  count(Q37) %>% 
  summarize(percent = n / sum(n))

```



# Modeling outcome as function of design thinking self-report and design course activities


Items to include as predictors: 
Q8b, Q8d, Q8e, Q8f, Q8g, Q8h, 
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g, 
Q18e, Q18f


## Need to relevel the predictors
Question 8 options
1 = “Never”, 2 = “Rarely”, 3 = “Monthly”, 4 = “Weekly”, 5 = “Daily”

```{r}
# First, create new variables that use text rather than numbers to indicate students' responses

test_bind <- test_bind %>% 
  mutate(Q8b_ord = case_when(Q8b == 1 ~ "Never",
                         Q8b == 2 ~ "Rarely",
                         Q8b == 3 ~ "Monthly",
                         Q8b == 4 ~ "Weekly",
                         Q8b == 5 ~ "Daily"),
         Q8d_ord = case_when(Q8d == 1 ~ "Never",
                         Q8d == 2 ~ "Rarely",
                         Q8d == 3 ~ "Monthly",
                         Q8d == 4 ~ "Weekly",
                         Q8d == 5 ~ "Daily"),
         Q8e_ord = case_when(Q8e == 1 ~ "Never",
                         Q8e == 2 ~ "Rarely",
                         Q8e == 3 ~ "Monthly",
                         Q8e == 4 ~ "Weekly",
                         Q8e == 5 ~ "Daily"),
         Q8f_ord = case_when(Q8f == 1 ~ "Never",
                         Q8f == 2 ~ "Rarely",
                         Q8f == 3 ~ "Monthly",
                         Q8f == 4 ~ "Weekly",
                         Q8f == 5 ~ "Daily"),
         Q8g_ord = case_when(Q8g == 1 ~ "Never",
                         Q8g == 2 ~ "Rarely",
                         Q8g == 3 ~ "Monthly",
                         Q8g == 4 ~ "Weekly",
                         Q8g == 5 ~ "Daily"),
         Q8h_ord = case_when(Q8h == 1 ~ "Never",
                         Q8h == 2 ~ "Rarely",
                         Q8h == 3 ~ "Monthly",
                         Q8h == 4 ~ "Weekly",
                         Q8h == 5 ~ "Daily")
         )


```

Question 14
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g
Question 14 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 

Question 18
Q18e, Q18f
Question 18 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 
```{r}

test_bind %>% count(Q14a)

test_bind <- test_bind %>% 
  mutate(Q14a_ord = case_when(Q14a == 0 ~ "Strongly disagree",
                              Q14a == 1 ~ "Disagree",
                              Q14a == 2 ~ "Neutral",
                              Q14a == 3 ~ "Agree",
                              Q14a == 4 ~ "Strongly agree"),
         Q14b_ord = case_when(Q14b == 0 ~ "Strongly disagree",
                              Q14b == 1 ~ "Disagree",
                              Q14b == 2 ~ "Neutral",
                              Q14b == 3 ~ "Agree",
                              Q14b == 4 ~ "Strongly agree"),
         Q14c_ord = case_when(Q14c == 0 ~ "Strongly disagree",
                              Q14c == 1 ~ "Disagree",
                              Q14c == 2 ~ "Neutral",
                              Q14c == 3 ~ "Agree",
                              Q14c == 4 ~ "Strongly agree"),
         Q14d_ord = case_when(Q14d == 0 ~ "Strongly disagree",
                              Q14d == 1 ~ "Disagree",
                              Q14d == 2 ~ "Neutral",
                              Q14d == 3 ~ "Agree",
                              Q14d == 4 ~ "Strongly agree"),
         Q14e_ord = case_when(Q14e == 0 ~ "Strongly disagree",
                              Q14e == 1 ~ "Disagree",
                              Q14e == 2 ~ "Neutral",
                              Q14e == 3 ~ "Agree",
                              Q14e == 4 ~ "Strongly agree"),
         Q14f_ord = case_when(Q14f == 0 ~ "Strongly disagree",
                              Q14f == 1 ~ "Disagree",
                              Q14f == 2 ~ "Neutral",
                              Q14f == 3 ~ "Agree",
                              Q14f == 4 ~ "Strongly agree"),
         Q14g_ord = case_when(Q14g == 0 ~ "Strongly disagree",
                              Q14g == 1 ~ "Disagree",
                              Q14g == 2 ~ "Neutral",
                              Q14g == 3 ~ "Agree",
                              Q14g == 4 ~ "Strongly agree"),
         Q18e_ord = case_when(Q18e == 0 ~ "Strongly disagree",
                              Q18e == 1 ~ "Disagree",
                              Q18e == 2 ~ "Neutral",
                              Q18e == 3 ~ "Agree",
                              Q18e == 4 ~ "Strongly agree"),
         Q18f_ord = case_when(Q18f == 0 ~ "Strongly disagree",
                              Q18f == 1 ~ "Disagree",
                              Q18f == 2 ~ "Neutral",
                              Q18f == 3 ~ "Agree",
                              Q18f == 4 ~ "Strongly agree"))


```




```{r}

test_bind %>% count(Q14g)
test_bind %>% count(Q14g_ord)

```



```{r}
str(test_bind$Q8b_ord)
Q8_ord_vars <- c("Q8b_ord", "Q8d_ord", "Q8e_ord", "Q8f_ord", "Q8g_ord", "Q8h_ord")
Q8_levels <- c("Never", "Rarely", "Monthly", "Weekly", "Daily")

Q14_ord_vars <- c("Q14a_ord", "Q14b_ord", "Q14c_ord", "Q14d_ord", "Q14e_ord", "Q14f_ord", "Q14g_ord")
Q14_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

Q18_ord_vars <- c("Q18e_ord", "Q18f_ord")
Q18_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

test_bind <- test_bind %>% 
  mutate_at(Q8_ord_vars, ~factor(., ordered = TRUE, levels = Q8_levels)) %>% 
  mutate_at(Q14_ord_vars, ~factor(., ordered = TRUE, levels = Q14_levels)) %>% 
  mutate_at(Q18_ord_vars, ~factor(., ordered = TRUE, levels = Q18_levels))


```



```{r}

test_bind %>% count(Q14d)
test_bind %>% count(Q14d_ord)

```



```{r}
rm(climate_imp_long_full)
```



```{r}

# only use 10 imputed datasets instead of 40
test_bind_2 <- test_bind %>% filter(.imp < 11)
```



```{r}
test_mids <- as.mids(test_bind_2)
```

Try this source for CFA code
https://statistics.ohlsen-web.de/multiple-imputation-with-mice/



```{r}

library("survey")
library("mice")
library("mitools")
library("semTools")
library("lavaan")
library("lavaan.survey")

```


```{r}

# Create data with missings
# set.seed(20170110)
# HSMiss <- HolzingerSwineford1939[,paste("x", 1:9, sep="")]
# randomMiss <- rbinom(prod(dim(HSMiss)), 1, 0.1)
# randomMiss <- matrix(as.logical(randomMiss), nrow=nrow(HSMiss))
# HSMiss[randomMiss] <- NA

# lavaan model
design.model <- ' feedback  =~ Q14a + Q14g
integrative =~ Q14c + Q14b
optimism   =~ Q18e + Q18f
experimentalism =~ Q14d
collaboration =~ Q14e + Q14f '

```



```{r}
out2 <- runMI(design.model, 
              data=test_mids,
              fun="cfa",
              meanstructure = TRUE)
```


```{r}
summary(out2)
```


```{r}
fitMeasures(out2, "all") 

```









```{r}

# take previously imputed data from variant 2 and convert it to svydesign-object
mice.imp2<-lapply(seq(HSMiss_imp$m),function(im) complete(HSMiss_imp,im))
mice.imp2<-mitools::imputationList(mice.imp2) 
svy.df_imp<-survey::svydesign(id=~1,weights=~1,data=mice.imp2)                    #survey-Objekt erstellen 


```



```{r}

lavaan_fit_design.model <- cfa(design.model, meanstructure = TRUE)
out3 <- lavaan.survey(lavaan_fit_design.model, test_mids)
summary(out3)
fitMeasures(out3, "chisq")

```





```{r}

q16.model <- ' energy  =~ Q16a + Q16b + Q16c + Q16e'


#clim_cha =~ Q16d + Q16f + Q16g
#defense =~ Q16h + Q16i + Q16j + Q16k 
#resources =~ Q16l + Q16m

```



```{r}

out4 <- runMI(q16.model, 
              data=test_mids,
              fun="cfa",
              meanstructure = TRUE)

```





```{r}

fitMeasures(out4, "all") 

```














## Model 0: Testing ordinal predictor

```{r}

mod0_lin_mono_des_Q16abce <- brm(formula = Q16abce ~  mo(Q8b_ord) + mo(Q8d_ord) + mo(Q8e_ord) + mo(Q8f_ord) + mo(Q8g_ord) + mo(Q8h_ord) +mo(Q14a_ord) + mo(Q14b_ord) + mo(Q14c_ord) + mo(Q14d_ord) + mo(Q14e_ord),
                     data = climate_data,
                     family = gaussian(),
                     cores = parallel::detectCores())


```




```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod0_lin_mono_des_Q16abce.rds"

mod0_lin_mono_des_Q16abce %>% write_rds(file = paste0(path, file_name))


```



```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod0_lin_mono_des_Q16abce.rds"

mod0_lin_mono_des_Q16abce <- read_rds(file = paste0(path, file_name))


```


```{r}
tab_model(mod0_lin_mono_des_Q16abce)
```


```{r}

plot(conditional_effects(mod0_lin_mono_des_Q16abce))

```




## Model 1: Summing the Q16 items and then modeling with _ordinal_ monotonic effects for Q8, Q14, and Q18 items

```{r}

mod1_lin_mono_des_Q16abce <- brm(formula = Q16abce ~  mo(Q8b_ord) + mo(Q8d_ord) + mo(Q8e_ord) + mo(Q8f_ord) + mo(Q8g_ord) + mo(Q8h_ord) +mo(Q14a_ord) + mo(Q14b_ord) + mo(Q14c_ord) + mo(Q14d_ord) + mo(Q14e_ord)+ mo(Q14f_ord) + mo(Q14g_ord) + mo(Q18e_ord) + mo(Q18f_ord),
                     data = climate_data,
                     family = gaussian(),
                     cores = parallel::detectCores())

```




```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_lin_mono_des_Q16abce.rds"

mod1_lin_mono_des_Q16abce %>% write_rds(file = paste0(path, file_name))


```



```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_lin_mono_des_Q16abce.rds"

mod1_lin_mono_des_Q16abce <- read_rds(file = paste0(path, file_name))


```




### multiple imputation version

```{r}

mod1_lin_mono_des_Q16abce_mi <- brm_multiple(formula = Q16abce ~  mo(Q8b_ord) + mo(Q8d_ord) + mo(Q8e_ord) + mo(Q8f_ord) + mo(Q8g_ord) + mo(Q8h_ord) +mo(Q14a_ord) + mo(Q14b_ord) + mo(Q14c_ord) + mo(Q14d_ord) + mo(Q14e_ord)+ mo(Q14f_ord) + mo(Q14g_ord) + mo(Q18e_ord) + mo(Q18f_ord),
                     data = test_mids,
                     family = gaussian(),
                     cores = parallel::detectCores())

```


```{r}


path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_lin_mono_des_Q16abce_mi.rds"

mod1_lin_mono_des_Q16abce_mi %>% write_rds(file = paste0(path, file_name))



```


```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_lin_mono_des_Q16abce_mi.rds"

mod1_lin_mono_des_Q16abce_mi <- read_rds(file = paste0(path, file_name))

```


```{r}
tab_model(mod1_lin_mono_des_Q16abce_mi)
```



```{r}


param_plot_q16abce_mod1_lin_mi <- mod1_lin_mono_des_Q16abce_mi %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q8b = bsp_moQ8b_ord,
         Q8d = bsp_moQ8d_ord,
         Q8e = bsp_moQ8e_ord,
         Q8f = bsp_moQ8f_ord,
         Q8g = bsp_moQ8g_ord,
         Q8h = bsp_moQ8h_ord) %>% 
  pivot_longer(cols = Q8b:Q8h, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter, levels = c("Q8b", "Q8e", "Q8d", "Q8f", "Q8g", "Q8h")), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16abce",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot_q16abce_mod1_lin_mi

```


```{r}

ggsave(filename = paste0("fig_q16abce_mod1_Q8_mi_param_plot_mi", Sys.Date(),".png"),
       plot = param_plot_q16abce_mod1_lin_mi,
       dpi = 450,
       width = 8,
       height = 6)

```



```{r}


param_plot_q16abce_mod1_q14_lin_mi <- mod1_lin_mono_des_Q16abce_mi %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q14a = bsp_moQ14a_ord,
         Q14b = bsp_moQ14b_ord,
         Q14c = bsp_moQ14c_ord,
         Q14d = bsp_moQ14d_ord,
         Q14e = bsp_moQ14e_ord,
         Q14f = bsp_moQ14f_ord,
         Q14g = bsp_moQ14g_ord,
         Q18e = bsp_moQ18e_ord,
         Q18f = bsp_moQ18f_ord) %>% 
  pivot_longer(cols = Q14a:Q18f, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter, levels = c("Q14a", "Q14g", "Q14c", "Q14b", "Q18e", "Q18f", "Q14d", "Q14e", "Q14f")), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16abce",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")


param_plot_q16abce_mod1_q14_lin_mi

```



```{r}

ggsave(filename = paste0("fig_q16abce_mod1_q14_mi_param_plot_", Sys.Date(),".png"),
       plot = param_plot_q16abce_mod1_q14_lin_mi,
       dpi = 450,
       width = 8,
       height = 6)

```











## Model 2: Summing the Q16 items and then modeling with monotonic effects for Q8, Q14, and Q18 items
** Missing Q14g

```{r}

mod2_lin_des_Q16abce <- brm(formula = Q16abce ~  mo(Q8b) + mo(Q8d) + mo(Q8e) + mo(Q8f) + mo(Q8g) + mo(Q8h) +mo(Q14a) + mo(Q14b) + mo(Q14c) + mo(Q14d) + mo(Q14e)+ mo(Q14f) + mo(Q18e) + mo(Q18f),
                     data = climate_data,
                     family = gaussian(),
                     cores = parallel::detectCores())

```

```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod2_lin_mono_des_Q16abce.rds"

mod2_lin_des_Q16abce %>% write_rds(file = paste0(path, file_name))


```



```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod2_lin_mono_des_Q16abce.rds"

mod2_lin_mono_des_Q16abce <- read_rds(file = paste0(path, file_name))


```





```{r}

mod2_lin_mono_des_Q16abce %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q14a = bsp_moQ14a_ord,
         Q14b = bsp_moQ14b_ord,
         Q14c = bsp_moQ14c_ord,
         Q14d = bsp_moQ14d_ord,
         Q14e = bsp_moQ14e_ord,
         Q14f = bsp_moQ14f_ord,
         Q14g = bsp_moQ14g_ord,
         Q18e = bsp_moQ18e_ord,
         Q18f = bsp_moQ18f_ord) %>% 
  pivot_longer(cols = Q14a:Q18f, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16a",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

```






```{r}
climate_data <- climate_data %>% 
  mutate(Q16abce = Q16a + Q16b + Q16c + Q16e)


lm_1 <- lm(Q16abce ~  Q8b + Q8d + Q8e + Q8f + Q8g + Q8h + Q14a + Q14b + Q14c + Q14d + Q14e+ Q14f + Q14g + Q18e + Q18f, data = climate_data)

```

```{r}
summary(lm_1)
```



