---
title: "Q16a_modeling"
author: "Katz et al."
date: "6/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(psych)
library(tidyverse)
library(tidymodels)
library(ranger)
library(purrrlyr)
library(purrr)
library(randomForest)
library(pander)
library(kableExtra)
library(knitr)

library(brms)
library(tidybayes)

```



Script for creating random forests for Q5 and Q16

```{r}
setwd("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering")

# climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/updated_climate_df_2.csv")


#original data set
#climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/climate_data.csv")

# read in the imputed dataset
climate_imp_long_full <- read_csv("climate_imp_long_40_full_inf_cl_hdb_agg_20210518.csv")
```


```{r}
pub_ds_ver <- 1
climate_data <- climate_imp_long_full %>% filter(.imp == pub_ds_ver)



```






# Create a new dataframe for the random forest work

Perform EFA for Q28

```{r}



Q28_vars <- paste0("Q28", letters[1:12])


Q28_df <- climate_data %>% drop_na(Q28_vars) %>% select(Q28_vars)

Q28_fa <- fa(Q28_df, nfactors = 2, fm = "ml", rotate = "oblimin")
print(Q28_fa, cut = 0.3, digits = 3)
# use `print(fa, digits = 3)` to view FLs < .3

```

Calculate Cronbach's alpha for internal consistency reliability

```{r}


FA1 <- c("Q28a", "Q28f", "Q28g", "Q28h", "Q28i", "Q28k")
FA2 <- c("Q28c", "Q28d", "Q28e", "Q28j", "Q28l")

alpha.fa1 <- psych::alpha(Q28_df[FA1])
print(alpha.fa1, digits = 3) #0.91

alpha.fa2 <- psych::alpha(Q28_df[FA2])
print(alpha.fa2, digits = 3) #0.80


```



Add variables for Q28_tech_norm ((Q28a + Q28f + Q28g + Q28h + Q28i + Q28k) / 6) and Q28_social_norm ((Q28c + Q28d + Q28e + Q28j + Q28l) / 5)
```{r}

climate_data <- climate_data %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

```


```{r}

climate_data <- climate_data %>% 
  mutate(Q16abce = Q16a + Q16b + Q16c + Q16e)

```


From ordinal regression forest with Q16a as outcome, top predictors are:




# Bayesian modeling



Top variables from Ordinal Forest
Q18c
Q20d
Q18e
Q17f
Q18i
Q12defghi_norm
Q18k
Q18a





### Method using Bayesian ordinal regression


Add major column back to replace Q29 in regression models

```{r}
climate_data <- climate_data %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"),
         major = as_factor(major))

```


```{r}


str(climate_data$major)

# set reference discipline

climate_data$major <- fct_relevel(climate_data$major, "Mec") 

str(climate_data$major)

```



```{r}
priors1 <- set_prior("normal(0, 1)", class = "b")
```









# Modeling outcome as function of design thinking self-report and design course activities


Items to include as predictors: 
Q8b, Q8d, Q8e, Q8f, Q8g, Q8h, 
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g, 
Q18e, Q18f


## Need to relevel the predictors
Question 8 options
1 = “Never”, 2 = “Rarely”, 3 = “Monthly”, 4 = “Weekly”, 5 = “Daily”

```{r}
# First, create new variables that use text rather than numbers to indicate students' responses

climate_data <- climate_data %>% 
  mutate(Q8b_ord = case_when(Q8b == 1 ~ "Never",
                         Q8b == 2 ~ "Rarely",
                         Q8b == 3 ~ "Monthly",
                         Q8b == 4 ~ "Weekly",
                         Q8b == 5 ~ "Daily"),
         Q8d_ord = case_when(Q8d == 1 ~ "Never",
                         Q8d == 2 ~ "Rarely",
                         Q8d == 3 ~ "Monthly",
                         Q8d == 4 ~ "Weekly",
                         Q8d == 5 ~ "Daily"),
         Q8e_ord = case_when(Q8e == 1 ~ "Never",
                         Q8e == 2 ~ "Rarely",
                         Q8e == 3 ~ "Monthly",
                         Q8e == 4 ~ "Weekly",
                         Q8e == 5 ~ "Daily"),
         Q8f_ord = case_when(Q8f == 1 ~ "Never",
                         Q8f == 2 ~ "Rarely",
                         Q8f == 3 ~ "Monthly",
                         Q8f == 4 ~ "Weekly",
                         Q8f == 5 ~ "Daily"),
         Q8g_ord = case_when(Q8g == 1 ~ "Never",
                         Q8g == 2 ~ "Rarely",
                         Q8g == 3 ~ "Monthly",
                         Q8g == 4 ~ "Weekly",
                         Q8g == 5 ~ "Daily"),
         Q8h_ord = case_when(Q8h == 1 ~ "Never",
                         Q8h == 2 ~ "Rarely",
                         Q8h == 3 ~ "Monthly",
                         Q8h == 4 ~ "Weekly",
                         Q8h == 5 ~ "Daily")
         )


```

Question 14
Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g
Question 14 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 

Question 18
Q18e, Q18f
Question 18 options
0 = “Strongly disagree”, 4 = “Strongly agree”, 
```{r}

climate_data %>% count(Q14a)

climate_data <- climate_data %>% 
  mutate(Q14a_ord = case_when(Q14a == 0 ~ "Strongly disagree",
                              Q14a == 1 ~ "Disagree",
                              Q14a == 2 ~ "Neutral",
                              Q14a == 3 ~ "Agree",
                              Q14a == 4 ~ "Strongly agree"),
         Q14b_ord = case_when(Q14b == 0 ~ "Strongly disagree",
                              Q14b == 1 ~ "Disagree",
                              Q14b == 2 ~ "Neutral",
                              Q14b == 3 ~ "Agree",
                              Q14b == 4 ~ "Strongly agree"),
         Q14c_ord = case_when(Q14c == 0 ~ "Strongly disagree",
                              Q14c == 1 ~ "Disagree",
                              Q14c == 2 ~ "Neutral",
                              Q14c == 3 ~ "Agree",
                              Q14c == 4 ~ "Strongly agree"),
         Q14d_ord = case_when(Q14d == 0 ~ "Strongly disagree",
                              Q14d == 1 ~ "Disagree",
                              Q14d == 2 ~ "Neutral",
                              Q14d == 3 ~ "Agree",
                              Q14d == 4 ~ "Strongly agree"),
         Q14e_ord = case_when(Q14e == 0 ~ "Strongly disagree",
                              Q14e == 1 ~ "Disagree",
                              Q14e == 2 ~ "Neutral",
                              Q14e == 3 ~ "Agree",
                              Q14e == 4 ~ "Strongly agree"),
         Q14f_ord = case_when(Q14f == 0 ~ "Strongly disagree",
                              Q14f == 1 ~ "Disagree",
                              Q14f == 2 ~ "Neutral",
                              Q14f == 3 ~ "Agree",
                              Q14f == 4 ~ "Strongly agree"),
         Q14g_ord = case_when(Q14g == 0 ~ "Strongly disagree",
                              Q14g == 1 ~ "Disagree",
                              Q14g == 2 ~ "Neutral",
                              Q14g == 3 ~ "Agree",
                              Q14g == 4 ~ "Strongly agree"),
         Q18e_ord = case_when(Q18e == 0 ~ "Strongly disagree",
                              Q18e == 1 ~ "Disagree",
                              Q18e == 2 ~ "Neutral",
                              Q18e == 3 ~ "Agree",
                              Q18e == 4 ~ "Strongly agree"),
         Q18f_ord = case_when(Q18f == 0 ~ "Strongly disagree",
                              Q18f == 1 ~ "Disagree",
                              Q18f == 2 ~ "Neutral",
                              Q18f == 3 ~ "Agree",
                              Q18f == 4 ~ "Strongly agree"))


```




```{r}

climate_data %>% count(Q14g)
climate_data %>% count(Q14g_ord)

```



```{r}
str(climate_data$Q8b_ord)
Q8_ord_vars <- c("Q8b_ord", "Q8d_ord", "Q8e_ord", "Q8f_ord", "Q8g_ord", "Q8h_ord")
Q8_levels <- c("Never", "Rarely", "Monthly", "Weekly", "Daily")

Q14_ord_vars <- c("Q14a_ord", "Q14b_ord", "Q14c_ord", "Q14d_ord", "Q14e_ord", "Q14f_ord", "Q14g_ord")
Q14_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

Q18_ord_vars <- c("Q18e_ord", "Q18f_ord")
Q18_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

climate_data <- climate_data %>% 
  mutate_at(Q8_ord_vars, ~factor(., ordered = TRUE, levels = Q8_levels)) %>% 
  mutate_at(Q14_ord_vars, ~factor(., ordered = TRUE, levels = Q14_levels)) %>% 
  mutate_at(Q18_ord_vars, ~factor(., ordered = TRUE, levels = Q18_levels))


```


```{r}

str(climate_data$Q14d_ord)

```

```{r}

climate_data %>% count(Q14d)
climate_data %>% count(Q14d_ord)

```




### Model 1: ordinal outcome, monotonic effects from Q8b, Q8d, Q8e, Q8f, Q8g, Q8h, Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g, Q18e, Q18f

```{r}

mod1_ord_mono_des_Q16a <- brm(formula = ordered(Q16a) ~  mo(Q8b_ord) + mo(Q8d_ord) + mo(Q8e_ord) + mo(Q8f_ord) + mo(Q8g_ord) + mo(Q8h_ord) + mo(Q14a_ord) + mo(Q14b_ord) + mo(Q14c_ord) + mo(Q14d_ord) + mo(Q14e_ord)+ mo(Q14f_ord) + mo(Q14g_ord) + mo(Q18e_ord) + mo(Q18f_ord),
                     data = climate_data,
                     family = cumulative("logit"),
                     cores = parallel::detectCores())

```



```{r}
path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_ord_mono_des_Q16a_2.rds"

mod1_ord_mono_des_Q16a %>% write_rds(file = paste0(path, file_name))
```


```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod1_ord_mono_des_Q16a_2.rds"

mod1_ord_mono_des_Q16a <- read_rds(file = paste0(path, file_name))


```



```{r}

get_variables(mod1_ord_mono_des_Q16a)


```



```{r}
summary(mod1_ord_mono_des_Q16a)
```



```{r}

# conditional_effects(mod1_ord_mono_des_Q16a) # doesn't work

```

Q8b, Q8d, Q8e, Q8f, Q8g, Q8h, 

```{r}

param_plot_q16a_q8 <- mod1_ord_mono_des_Q16a %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q8b = bsp_moQ8b_ord,
         Q8d = bsp_moQ8d_ord,
         Q8e = bsp_moQ8e_ord,
         Q8f = bsp_moQ8f_ord,
         Q8g = bsp_moQ8g_ord,
         Q8h = bsp_moQ8h_ord) %>% 
  pivot_longer(cols = Q8b:Q8h, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16a",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot_q16a_q8

```


```{r}

ggsave(filename = paste0("fig_q16a_mod1_Q8_param_plot_", Sys.Date(),".png"),
       plot = param_plot_q16a_q8,
       dpi = 450,
       width = 8,
       height = 6)

```



Q14a, Q14b, Q14c, Q14d, Q14e, Q14f, Q14g, Q18e, Q18f

```{r}

param_plot_q16a_q14 <- mod1_ord_mono_des_Q16a %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q14a = bsp_moQ14a_ord,
         Q14b = bsp_moQ14b_ord,
         Q14c = bsp_moQ14c_ord,
         Q14d = bsp_moQ14d_ord,
         Q14e = bsp_moQ14e_ord,
         Q14f = bsp_moQ14f_ord,
         Q14g = bsp_moQ14g_ord,
         Q18e = bsp_moQ18e_ord,
         Q18f = bsp_moQ18f_ord) %>% 
  pivot_longer(cols = Q14a:Q18f, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16a",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot_q16a_q14

```



```{r}

ggsave(filename = paste0("fig_q16a_mod1_param_plot_", Sys.Date(),".png"),
       plot = param_plot_q16a_q14,
       dpi = 450,
       width = 8,
       height = 6)

```







## Model 2: Summing the Q16 items and then modeling with monotonic effects for Q8, Q14, and Q18 items

```{r}

mod2_lin_des_Q16abce <- brm(formula = Q16abce ~  mo(Q8b) + mo(Q8d) + mo(Q8e) + mo(Q8f) + mo(Q8g) + mo(Q8h) +mo(Q14a) + mo(Q14b) + mo(Q14c) + mo(Q14d) + mo(Q14e)+ mo(Q14f) + mo(Q18e) + mo(Q18f),
                     data = climate_data,
                     family = gaussian(),
                     cores = parallel::detectCores())

```

```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod2_lin_mono_des_Q16abce.rds"

mod2_lin_des_Q16abce %>% write_rds(file = paste0(path, file_name))


```



```{r}

path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/random forest Q5/Q16 random forests/"

file_name <- "mod2_lin_mono_des_Q16abce.rds"

mod2_lin_mono_des_Q16abce <- read_rds(file = paste0(path, file_name))


```





```{r}

mod2_lin_mono_des_Q16abce %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q14a = bsp_moQ14a_ord,
         Q14b = bsp_moQ14b_ord,
         Q14c = bsp_moQ14c_ord,
         Q14d = bsp_moQ14d_ord,
         Q14e = bsp_moQ14e_ord,
         Q14f = bsp_moQ14f_ord,
         Q14g = bsp_moQ14g_ord,
         Q18e = bsp_moQ18e_ord,
         Q18f = bsp_moQ18f_ord) %>% 
  pivot_longer(cols = Q14a:Q18f, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Ordinal Predictors for Q16a",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

```




## Model 2: Summing the Q16 items and then modeling with monotonic effects for Q8, Q14, and Q18 items

```{r}

mod3_lin_des_Q16abce <- brm(formula = Q16abce ~  mo(Q8b) + mo(Q8d) + mo(Q8e) + mo(Q8f) + mo(Q8g) + mo(Q8h) +mo(Q14a) + mo(Q14b) + mo(Q14c) + mo(Q14d) + mo(Q14e)+ mo(Q14f) + mo(Q18e) + mo(Q18f),
                     data = climate_data,
                     family = gaussian(),
                     cores = parallel::detectCores())

```



