---
title: "q27 clustering and career goals"
author: "Katz"
date: "9/6/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}

library(RColorBrewer)
library(tidyverse)
library(dbscan)
library(umap)
library(psych)
library(gmodels)
library(graphics)
library(knitr)
library(purrr)
library(tidytext)
library(ggmosaic)


library(maps)
library(ggmap)


```




```{r}

climate_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/updated_climate_df_2.csv")


## Drop duplicates
climate_df <- climate_df %>% distinct(Litho, .keep_all = TRUE)



## Add in major as string instead of number

climate_df <- climate_df %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))


```



```{r}
climate_df %>% count(Q29, sort = TRUE)

climate_df %>% count(Q32)

climate_df %>% filter(is.na(Q29)) %>% count(Q32)


climate_df %>% count(Q33)

climate_df %>% filter(!is.na(Q29)) %>% count(Q33, sort = TRUE)

climate_df %>% count(Q37)


```



Drop NAs for specific questions and filter out disciplines with fewer than 30 (the cutoff) students in sample

```{r}

Q2_vars <- paste0("Q2", letters[1:7])
#Q3_vars <- paste0("Q3", letters[1:7])

#climate_df %>% mutate_at(vars(Q3_vars), ~ replace_na(.,0))


Q27_vars <- paste0("Q27", letters[1:9])
Q28_vars <- paste0("Q28", letters[1:12])


# climate_df <- climate_df %>% 
#   drop_na(Q29, Q18k, Q20a, Q20b, Q20d, Q18k, Q22) %>%
#   drop_na(Q23a, Q23b, Q23c, Q23d, Q23e, Q23f, Q23g, Q23h, Q23i, Q23j) %>%
#   drop_na(Q24a, Q24b, Q24c, Q24d, Q24e, Q24f, Q24g, Q24h, Q24i, Q24j, Q24k) %>%
#   drop_na(Q25a, Q25b, Q25c) %>%
#   drop_na(Q26a, Q26b, Q26c, Q26d, Q26e, Q26f, Q26g, Q26h) %>%
#   drop_na(Q27_vars) %>%
#   drop_na(Q28_vars)

climate_df <- climate_df %>% 
  drop_na(Q29, Q27_vars, Q32, Q37, Q40, Q6a, Q6d, Q6e, Q6i, Q6j, Q8j, Q8n)

climate_df %>% count(Q29, sort = TRUE)

#cutoff <- 30


climate_df <- climate_df %>% 
  add_count(Q29, name = "major_count") %>% 
  filter(major_count > 30)


climate_df %>% count(Q29, sort = TRUE)

count_tbl <- climate_df %>% count(Q29, major, sort = TRUE)

```


Major counts and percentages
```{r}
count_tbl %>% 
  mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
  mutate(cumulat_pct = round(cumsum(n)/sum(n)*100, 2)) %>% 
  kable()
```

Gender counts overall
```{r}
climate_df %>% count(Q37) %>% 
  mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
  kable()
```



fill in 0s for NAs for specific items (Q1, Q3, Q5)
```{r}


### Fill in NAs for specific items ---- 

Q1_vars <- paste0("Q1", letters[1:20])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])
Q16_vars <- paste0("Q16", letters[1:13])
Q27_vars <- paste0("Q27", letters[1:9])
Q28_vars <- paste0("Q28", letters[1:12])
Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])

Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")




#climate_df[, Q1_vars]
climate_df <- climate_df %>% mutate_at(vars(Q1_vars), ~replace_na(., 0))
#climate_df[, Q1_vars]

#climate_df[, Q3_vars]
climate_df <- climate_df %>% mutate_at(vars(Q3_vars), ~ replace_na(.,0))
#climate_df[, Q3_vars]

#climate_df[,Q5_vars]
climate_df <- climate_df %>% mutate_at(vars(Q5_vars), ~ replace_na(.,0))
#climate_df[, Q5_vars]

#climate_df[, Q7_vars]
climate_df <- climate_df %>% mutate_at(vars(Q7_vars), ~ replace_na(., 0))
#climate_df[,Q7_vars]

#climate_df[, Q35_vars]
climate_df <- climate_df %>% mutate_at(vars(Q35_vars), ~ replace_na(., 0))
#climate_df[,Q35_vars]

#climate_df[, Q39_vars]
climate_df <- climate_df %>% mutate_at(vars(Q39_vars), ~ replace_na(., 0))
#climate_df[,Q39_vars]


#climate_df[, Q28_vars]
#climate_df <- climate_df %>% drop_na(Q28_vars)
#climate_df[, Q28_vars]
#climate_df <- climate_df %>% drop_na(Q16_vars)





```



```{r}

climate_df <- climate_df %>% drop_na(all_of(Q28_vars))
climate_df <- climate_df %>% drop_na(all_of(Q27_vars)) #should have 3313 observations



climate_df <- climate_df %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)


```


Drop majors with low counts (below 30 students in sample)
```{r}

climate_df %>% count(Q29, sort = TRUE)
climate_df %>% count(major, sort = TRUE)
cutoff <- 30

climate_df <- climate_df %>% add_count(Q29, name = "major_count") %>% filter(major_count > cutoff)

```


Drop majors with NA as major


```{r}

climate_df <- climate_df %>% filter(!is.na(major))
climate_df %>% count(major, sort = TRUE)

```



# Clustering Process (two-step process using UMAP + HDBSCAN)

```{r}


climate_df <- climate_df %>% 
  mutate(Q27a_tri_num = case_when(Q27a == 1 | Q27a == 2 ~ 0,
                                  Q27a == 3 | Q27a == 4 ~1, 
                                  Q27a == 5 ~ 2),
         Q27b_tri_num = case_when(Q27b == 1 | Q27b == 2 ~ 0,
                                  Q27b == 3 | Q27b == 4 ~1,
                                  Q27b == 5 ~ 2),
         Q27c_tri_num = case_when(Q27c == 1 | Q27c == 2 ~ 0,
                                  Q27c == 3 | Q27c == 4 ~ 1,
                                  Q27c == 5 ~ 2),
         Q27d_tri_num = case_when(Q27d == 1 | Q27d == 2 ~ 0,
                                  Q27d == 3 | Q27d == 4 ~ 1,
                                  Q27d == 5 ~ 2),
         Q27e_tri_num = case_when(Q27e == 1 | Q27e == 2 ~ 0,
                                  Q27e == 3 | Q27e == 4 ~ 1,
                                  Q27e == 5 ~ 2),
         Q27f_tri_num = case_when(Q27f == 1 | Q27f == 2 ~ 0,
                                  Q27f == 3 | Q27f == 4 ~ 1,
                                  Q27f == 5 ~ 2),
         Q27g_tri_num = case_when(Q27g == 1 | Q27g == 2 ~ 0,
                                  Q27g == 3 | Q27g == 4 ~ 1,
                                  Q27g == 5 ~ 2),
         Q27h_tri_num = case_when(Q27h == 1 | Q27h == 2 ~ 0,
                                  Q27h == 3 | Q27h == 4 ~ 1,
                                  Q27h == 5 ~ 2),
         Q27i_tri_num = case_when(Q27i == 1 | Q27i == 2 ~ 0,
                                  Q27i == 3 | Q27i == 4 ~ 1,
                                  Q27i == 5 ~ 2))




Q27_tri_num_vars <- paste0("Q27", letters[1:9], "_tri_num")

climate_df <- climate_df %>% 
  rowid_to_column(var = "student_id")

climate_27_tri_df <- climate_df %>% 
  select(student_id, Q5a, Q5b, Q5c, Q5d, Q5e, Q5f, Q5g, Q5h, Q5i, Q5j, Q27_tri_num_vars)

```


First perform dimension reduction using UMAP
```{r}
climate_27_tri_df <- drop_na(climate_27_tri_df)

last_letter <- 9
Q27_tri_num_vars <- paste0("Q27", letters[1:last_letter], "_tri_num")


#Q27_tri_num_vars <- c("Q27a_tri_num", "Q27b_tri_num", "Q27c_tri_num")

# create custom settings for umap
custom.settings = umap.defaults
#custom.settings$n_neighbors = 30
custom.settings$n_components = 2
custom.settings$n_neighbors = 55 # next time, try dropping this from 55 to 30
custom.settings$min_dist = 0.00001 # experimental, dropping down from 0.1 to 0.0
custom.settings$metric = 'euclidean'

## 30 neighbors seems to work well


climate_27_tri_umap <- climate_27_tri_df %>% 
  select(Q27_tri_num_vars) %>% 
  umap(random_state = 123, config = custom.settings)





# climate_27_tri_umap <- climate_27_tri_df %>% select(Q27_tri_num_vars) %>% umap(random_state = 123)
climate_27_tri_umap
names(climate_27_tri_umap$layout)
names(climate_27_tri_umap$layout) <- c("dim1", "dim2")

head(climate_27_tri_umap$layout, 3)
head(climate_27_tri_umap$layout[,1])
head(climate_27_tri_umap$layout[,2])

# visualize the reduction 
plot(climate_27_tri_umap$layout[,1], climate_27_tri_umap$layout[,2])

plot_df <- climate_27_tri_umap$layout
plot_df <- as_tibble(plot_df)
names(plot_df) <- c("dim1", "dim2")
ggplot(data = plot_df, aes(x = dim1, y = dim2)) +
  geom_point()
```


Next, perform clustering with HDBSCAN

```{r}
# perform clustering using HDBSCAN on the dim-reduced data
# clustering with min 60 pts leaves 131 unclustered
#clustering with 40 creates 13 groups and 29 unclustered
### Best combination: n_components=2, n_neighbords=80, min_dist=0.001, minPts=90 (or 50)
### also good: n_comp=2, n_neigh=20 or 30, min_dist=0.0001, minPts=50
hdbscan_umap_cl <- hdbscan(plot_df, minPts = 120) 
# groups stay pretty similar from minPts 70 up to 150, when it drops from 9 to 6 clusters

hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
plot_df$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of simplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


# add the cluster labels back to the original data set
climate_27_tri_df$cluster <- hdbscan_umap_cl$cluster

climate_27_tri_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for Question 27 ternary split") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



```


Join the dataframes back together again

```{r}
# Add the cluster assignments back to the original climate_df dataframe
climate_df <- climate_27_tri_df %>% select(student_id, cluster) %>% inner_join(climate_df, by = "student_id")
```


```{r}
climate_df %>% count(cluster, sort = TRUE)


```




## Views of when climate change will affect different groups broken down by cluster assignments


## Looking for patterns in the clusters


```{r}
q27_item_list <- list(
  'Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment"
)

q27_labs <- c("Me personally", 
              "My family",
              "People in my comm.",
              "People in US",
              "Other indust. countr.",
              "Developing countries",
              "Plant + animal species",
              "World's poor",
              "Natural environment")

names(q27_labs) <- c("Q27a_tri_num",
                     "Q27b_tri_num",
                     "Q27c_tri_num",
                     "Q27d_tri_num",
                     "Q27e_tri_num",
                     "Q27f_tri_num",
                     "Q27g_tri_num",
                     "Q27h_tri_num",
                     "Q27i_tri_num")
```



# Understanding cluster compositions more


#### First create a dataframe with the rankings for each cluster, where a lower ranking means students in the cluster think climate change will affect more categories sooner. 



```{r}

## create dataframe with rankings for cluster by how soon each cluster believes climate change will affect groups
cluster_ranking_df <- climate_df %>% 
  mutate(Q27_tri_total = Q27a_tri_num + Q27b_tri_num + Q27c_tri_num + Q27d_tri_num + Q27e_tri_num +
           Q27f_tri_num + Q27g_tri_num + Q27h_tri_num + Q27i_tri_num) %>% 
  group_by(cluster) %>% 
  summarize(cluster_avg = mean(Q27_tri_total)) %>% 
  arrange(cluster_avg) %>% 
  rowid_to_column(var = "cluster_time_rank")

cluster_ranking_df

climate_df <- climate_df %>% 
  inner_join(cluster_ranking_df, by = "cluster")

#climate_27_tri_df %>% inner_join(cluster_ranking_df, by = "cluster")


```


Set clustering colors for all plots
```{r}
#Old method of randomly assigning colors
# cluster_num <- length(unique(climate_df$cluster))
# 
# cluster_colors <- colorRampPalette(brewer.pal(9, "Set1"))(cluster_num)

# new method of assigning cluster colors along a gradient
cluster_num <- length(unique(climate_df$cluster_time_rank))

cluster_colors <- colorRampPalette(c("#ec3434", "#f7c035", "#007030"))(cluster_num)
```



### Look at distribution of cluster for how when they think each community may be affected by global warming

```{r}
climate_df %>%
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>% 
  ggplot(aes(x = as_factor(response))) +
  geom_bar(aes(fill = as_factor(cluster_time_rank))) +
  facet_wrap(.~ survey_item, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "Converted Ternary Response (0 = Now, 1 = Later, 2 = Never)",
       y = "Count",
       title = "Histogram of when will global warming affect different groups?",
       fill = "Cluster") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = cluster_colors)

```

Same information but faceted with clusters

** This is a good plot for seeing that a cluster's beliefs about effects of global warming on different populations at different times vary in a clear pattern
```{r}

climate_df %>%
  #filter(cluster != 0) %>% 
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>%
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = survey_item)) +
  geom_bar(aes(fill = as_factor(response))) +
  facet_wrap(.~ cluster_time_rank, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "When will global warming affect this population?",
       y = "Count",
       title = "Cluster patterns of when will global warming affect various populations",
       fill = "Response") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = c("#ec3434", "#f7c035", "#007030"), 
                    name = "Response", 
                    labels = c("0" = "0-10 yrs", "1" = "25-50y yrs", "2" = "Never")) +
  scale_x_discrete(labels = c('Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment")) + 
  coord_flip()

```


#### Overall count for clusters


```{r}
climate_df %>% 
  filter(cluster != 0) %>% 
  group_by(cluster_time_rank) %>% 
  summarize(n = n()) %>% 
  mutate(perc = round(n / sum(n) * 100, 2)) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = fct_reorder(cluster_time_rank, perc), 
             y = perc, fill = as_factor(cluster_time_rank))) +
  geom_col() +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 8)) +
  labs(x = "Cluster", 
       y = "Percentage of students in cluster",
       title = "Distribution of temporal belief clusters in engineering students") +
  scale_fill_manual(values = cluster_colors)


```

Broken plot

```{r}

climate_df %>% 
  group_by(cluster_time_rank) %>% 
  summarize(n = n()) %>% 
#  add_count(major, name = "major_total") %>% 
#  mutate(proportion = n / major_total) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = fct_reorder(cluster_time_rank, n), 
             y = n, fill = as_factor(cluster_time_rank))) +
  geom_col() +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 8)) +
  labs(x = "Cluster", 
       y = "Count",
       title = "Distribution of temporal belief clusters in engineering majors") +
  scale_fill_manual(values = cluster_colors)
```










# Career goals analysis




# Chi square tests of whether different clusters (students with different temporal discounting patterns of when climate change will affect various groups) want to address climate-related outcomes in their careers -->

<!-- ## Q5a - energy (supply or demand) -->
<!-- ```{r} -->

<!-- # cont_table <- table(climate_df$cluster_time_rank, climate_df$Q5a) -->
<!-- # cont_table -->
<!-- # chisq.test(cont_table) -->
<!-- #  -->
<!-- #  -->
<!-- # mosaicplot(cont_table, shade = TRUE, main = "Q27 Cluster vs Q5a (energy)") -->


<!-- ``` -->


<!-- ## Q5d - climate change -->
<!-- ```{r} -->

<!-- # cont_table <- table(climate_df$cluster_time_rank, climate_df$Q5d) -->
<!-- # cont_table -->
<!-- # chisq.test(cont_table) -->
<!-- #  -->
<!-- #  -->
<!-- # mosaicplot(cont_table, shade = TRUE, main = "Q27 Cluster vs Q5d (climate change)") -->

<!-- ``` -->


<!-- ### alternative Q5d visualization for proportions of each cluster interested in addressing climate change -->

<!-- ```{r} -->

<!-- # climate_df %>%  -->
<!-- #   ggplot(aes(x = as_factor(cluster_time_rank), fill = as_factor(Q5d))) + -->
<!-- #   geom_bar(position = "fill") + -->
<!-- #   labs(title = "Question 5d responses by cluster", -->
<!-- #        x = "Cluster assignment", -->
<!-- #        y = "Proportion", -->
<!-- #        fill = "No (0) or Yes (1)") + -->
<!-- #   theme(plot.title = element_text(hjust = 0.5)) -->

<!-- ``` -->


<!-- ## Q5f - water supply -->
<!-- ```{r} -->
<!-- # Q5f -->

<!-- # cont_table <- table(climate_df$cluster_time_rank, climate_df$Q5f) -->
<!-- # cont_table -->
<!-- # chisq.test(cont_table) -->
<!-- #  -->
<!-- # mosaicplot(cont_table, shade = TRUE, main = "Q27 Cluster vs Q5f (water supply)") -->

<!-- ``` -->


<!-- ## Q5j - environmental degradation -->
<!-- ```{r} -->

<!-- # Q5j -->

<!-- # cont_table <- table(climate_df$cluster_time_rank, climate_df$Q5j) -->
<!-- # cont_table -->
<!-- # chisq.test(cont_table) -->
<!-- #  -->
<!-- # mosaicplot(cont_table, shade = TRUE, main = "Q27 Cluster vs Q5j (environmental degradation)") -->

<!-- ``` -->



<!-- ```{r} -->
<!-- #Q29 (major) -->

<!-- #cont_table_Q29 <- table(climate_df$cluster, climate_df$Q29) -->
<!-- #cont_table_Q29 -->
<!-- #chisq.test(cont_table_Q29) -->

<!-- #mosaicplot(cont_table_Q29, shade = TRUE, main = "Q27 Cluster vs Q29 (environmental degradation)") -->


<!-- ``` -->














### *MUTED



## Question 2 items (Working in various sectors) and climate change impacts cluster



```{r}

career_sector_df <- climate_df %>% 
  drop_na(Q2_vars) %>% 
  select(student_id, Q2a:Q2g, major, cluster_time_rank) %>% 
  pivot_longer(cols = Q2a:Q2g, names_to = "Q2_item", values_to = "Q2_resp")

career_sector_df

```



```{r}

career_sector_df %>%  
  mutate(Q2_item_name = case_when(Q2_item == "Q2a" ~ "Private/Corporate", 
              Q2_item == "Q2b" ~ "Non-profit/NGO",
              Q2_item == "Q2c" ~ "Gov./Public Policy",
              Q2_item == "Q2d" ~ "Education",
              Q2_item == "Q2e" ~ "Entrepreneurship/Start-up",
              Q2_item == "Q2f" ~ "Healthcare",
              Q2_item == "Q2g" ~ "Other")) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = Q2_item_name, fill = factor(Q2_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("0", "1", "2", "3", "4")) +
  facet_wrap(. ~ cluster_time_rank, 
             scales = "free") +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q2 sector by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


```


#### Using kruskal-wallis instead of chi square since outcome is Likert-scale item (i.e., ordinal variable)


```{r}


# nested <- career_sector_df %>% 
#   group_by(Q2_item) %>% 
#   nest(-Q2_item) %>% 
#   mutate(
#     Q2_item_name = case_when(Q2_item == "Q2a" ~ "Private/Corporate", 
#               Q2_item == "Q2b" ~ "Non-profit/NGO",
#               Q2_item == "Q2c" ~ "Gov./Public Policy",
#               Q2_item == "Q2d" ~ "Education",
#               Q2_item == "Q2e" ~ "Entrepreneurship/Start-up",
#               Q2_item == "Q2f" ~ "Healthcare",
#               Q2_item == "Q2g" ~ "Other"),
#     cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q2_resp)),
#     test = purrr::map(data, ~kruskal.test(.$cluster_time_rank, .$Q2_resp)),
#     tidied = purrr::map(test, tidy),
#     m_plot = mosaicplot(cont_tab[[1]], shade = TRUE, 
#                         main = paste0("How likely to enter sector: ", Q2_item_name))
#     )
# 


```


visualize with either mosaic plots or boxplots 

```{r}

nested <- career_sector_df %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  group_by(Q2_item) %>% 
  nest(-Q2_item) %>% 
  mutate(
    Q2_item_name = case_when(Q2_item == "Q2a" ~ "Private/Corporate", 
              Q2_item == "Q2b" ~ "Non-profit/NGO",
              Q2_item == "Q2c" ~ "Gov./Public Policy",
              Q2_item == "Q2d" ~ "Education",
              Q2_item == "Q2e" ~ "Entrepreneurship/Start-up",
              Q2_item == "Q2f" ~ "Healthcare",
              Q2_item == "Q2g" ~ "Other"),
    cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q2_resp)),
    test = purrr::map(data, ~kruskal.test(.$cluster_time_rank, .$Q2_resp)),
    tidied = purrr::map(test, tidy),
    m_plot = mosaicplot(cont_tab[[1]], shade = TRUE, 
                        main = paste0("How likely to enter sector: ", Q2_item_name)),
    box_plot = purrr::map(data, ~ ggplot(.x, aes(x = .$cluster_time_rank, 
                                            y = .$Q2_resp)) +
                            geom_boxplot(alpha = 0.5) +
                            geom_jitter(aes(color = .$cluster_time_rank),
                                        alpha = 0.3,
                                        height = 0.15,
                                        width = 0.4) +
                            labs(x = "Cluster",
                                 y = Q2_item_name,
                                 title = "How likely to enter sector by cluster (0 = Not at all likely, 4 = Very likely)") +
                            scale_color_manual(values = cluster_colors) +
                            theme_light() +
                            theme(legend.position = "none", 
                                  plot.title = element_text(hjust = 0.5, 
                                                            size = 9))
                          ))


for (i in 1:length(nested$box_plot)) {
  print(nested$box_plot[[i]])
  }


```




#### Table of kruskal wallis test results

```{r}

nested %>% 
  select(Q2_item, Q2_item_name, tidied) %>% 
  unnest(tidied) %>% kable()

```




## Clusters and Question 3 items (Pursuing various degree options)


### Chi square tests of whether different clusters (students with different temporal discounting patterns of when climate change will affect various groups) want to pursue various degree options


```{r}

career_degree_df <- climate_df %>% 
  select(student_id, Q3a:Q3g, major, cluster_time_rank) %>% 
  pivot_longer(cols = Q3a:Q3g, names_to = "Q3_item", values_to = "Q3_resp")

career_degree_df


```




```{r}
q3_labs <- c("MA/MS (non-engineering)",
             "ME/MS (engineering)",
             "PhD (engineering)",
             "MBA",
             "JD (law)",
             "MD",
             "Other")

names(q3_labs) <- c("Q3a",
                     "Q3b",
                     "Q3c",
                     "Q3d",
                     "Q3e",
                     "Q3f",
                     "Q3g")
```


#### Interest of each topic


```{r}
career_degree_df %>%   
  ggplot(aes(x = as_factor(cluster_time_rank), fill = factor(Q3_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("No", "Yes")) +
  facet_wrap(. ~ Q3_item, 
             scales = "free",
             labeller = labeller(Q3_item = q3_labs)) +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q3 degree by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



```


#### Interest within each cluster


```{r}

career_degree_df %>%  
  mutate(Q3_item_name = case_when(Q3_item == "Q3a" ~ "MA/MS (non-eng)", 
              Q3_item == "Q3b" ~ "ME/MS (eng)",
              Q3_item == "Q3c" ~ "PhD (eng)",
              Q3_item == "Q3d" ~ "MBA",
              Q3_item == "Q3e" ~ "JD (law)",
              Q3_item == "Q3f" ~ "MD",
              Q3_item == "Q3g" ~ "Other")) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = Q3_item_name, 
             fill = factor(Q3_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("No", "Yes")) +
  facet_wrap(. ~ cluster_time_rank, 
             scales = "free") +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q3 degree by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


```


## Chi square tests of degree interests by cluster -- not expecting any differences across clusters

```{r}


nested <- career_degree_df %>% 
  group_by(Q3_item) %>% 
  nest(-Q3_item) %>% 
  mutate(
    Q3_item_name = case_when(Q3_item == "Q3a" ~ "MA/MS (non-eng)", 
              Q3_item == "Q3b" ~ "ME/MS (eng)",
              Q3_item == "Q3c" ~ "PhD (eng)",
              Q3_item == "Q3d" ~ "MBA",
              Q3_item == "Q3e" ~ "JD (law)",
              Q3_item == "Q3f" ~ "MD",
              Q3_item == "Q3g" ~ "Other"),
    cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q3_resp)),
    test = purrr::map(data, ~chisq.test(.$cluster_time_rank, .$Q3_resp)),
    tidied = purrr::map(test, tidy),
    m_plot = mosaicplot(cont_tab[[1]], 
                        shade = TRUE, 
                        main = paste0("Likely to pursue in next 5 yrs: ",Q3_item_name))
    )



```



```{r}

nested %>% 
  select(Q3_item, Q3_item_name, tidied) %>% 
  unnest(tidied) %>% kable()

```





# Kruskal wallis tests of whether different clusters (students with different temporal discounting patterns of when climate change will affect various groups) consider various career satisfaction factors important


## Career satisfaction items (Q4 items)

```{r}

career_sat_df <- climate_df  %>% 
  select(student_id, Q4a:Q4p, major, cluster_time_rank) %>% 
  pivot_longer(cols = Q4a:Q4p, names_to = "Q4_item", values_to = "Q4_resp")

career_sat_df

```



```{r}

career_sat_df %>%  
  mutate(Q4_item_name = case_when(Q4_item == "Q4a" ~ "Make money", 
              Q4_item == "Q4b" ~ "Fame",
              Q4_item == "Q4c" ~ "Help others",
              Q4_item == "Q4d" ~ "Supervise others",
              Q4_item == "Q4e" ~ "Job sec. and opp.",
              Q4_item == "Q4f" ~ "Work w/ people",
              Q4_item == "Q4g" ~ "Invent/design",
              Q4_item == "Q4h" ~ "Develop knowledge/skill",
              Q4_item == "Q4i" ~ "Personal/fam. time",
              Q4_item == "Q4j" ~ "Easy job",
              Q4_item == "Q4k" ~ "Exciting env.",
              Q4_item == "Q4l" ~ "Solve societal prob.",
              Q4_item == "Q4m" ~ "Use talent/abilities",
              Q4_item == "Q4n" ~ "Do hands-on work",
              Q4_item == "Q4o" ~ "Apply math/sci.",
              Q4_item == "Q4p" ~ "Volunteer w/ charity")) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = Q4_item_name, fill = factor(Q4_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("0", "1", "2", "3", "4")) +
  facet_wrap(. ~ cluster_time_rank, 
             scales = "free") +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q4 topic by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


```




```{r}
Q4_labs <- c("Make money", 
             "Fame",
             "Help others",
             "Supervise others",
             "Job sec. and opp.",
             "Work w/ people",
             "Invent/design",
             "Develop knowledge/skill",
             "Personal/fam. time",
             "Easy job",
             "Exciting env.",
             "Solve societal prob.",
             "Use talent/abilities",
             "Do hands-on work",
             "Apply math/sci.",
             "Volunteer w/ charity")

nested <- career_sat_df %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  group_by(Q4_item) %>% 
  nest(-Q4_item) %>% 
  mutate(
    Q4_item_name = case_when(Q4_item == "Q4a" ~ "Make money", 
              Q4_item == "Q4b" ~ "Fame",
              Q4_item == "Q4c" ~ "Help others",
              Q4_item == "Q4d" ~ "Supervise others",
              Q4_item == "Q4e" ~ "Job sec. and opp.",
              Q4_item == "Q4f" ~ "Work w/ people",
              Q4_item == "Q4g" ~ "Invent/design",
              Q4_item == "Q4h" ~ "Develop knowledge/skill",
              Q4_item == "Q4i" ~ "Personal/fam. time",
              Q4_item == "Q4j" ~ "Easy job",
              Q4_item == "Q4k" ~ "Exciting env.",
              Q4_item == "Q4l" ~ "Solve societal prob.",
              Q4_item == "Q4m" ~ "Use talent/abilities",
              Q4_item == "Q4n" ~ "Do hands-on work",
              Q4_item == "Q4o" ~ "Apply math/sci.",
              Q4_item == "Q4p" ~ "Volunteer w/ charity"),
    cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q4_resp)),
    test = purrr::map(data, ~chisq.test(.$cluster_time_rank, .$Q4_resp)),
    tidied = purrr::map(test, tidy),
    m_plot = mosaicplot(cont_tab[[1]], 
                        shade = TRUE, 
                        main = paste0("Importance of factor to career satisfaction - ", Q4_item_name)),
    box_plot = purrr::map(data, ~ ggplot(.x, aes(x = .$cluster_time_rank, 
                                            y = .$Q4_resp)) +
                            geom_boxplot(alpha = 0.5) +
                            geom_jitter(aes(color = .$cluster_time_rank),
                                        alpha = 0.3,
                                        height = 0.15,
                                        width = 0.4) +
                            labs(x = "Cluster",
                                 y = Q4_item_name,
                                 title = "Importance of factor to career satisfaction by cluster (0 = Not at all important, 4 = Very important)") +
                            scale_color_manual(values = cluster_colors) +
                            theme_light() +
                            theme(legend.position = "none", 
                                  plot.title = element_text(hjust = 0.5, 
                                                            size = 9))
                          ))


for (i in 1:length(nested$box_plot)) {
  print(nested$box_plot[[i]])
  }




```




```{r}

# nested <- career_sat_df %>% 
#   mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
#   group_by(Q4_item) %>% 
#   nest(-Q4_item) %>% 
#   mutate(
#     Q4_item_name = case_when(Q4_item == "Q4a" ~ "Make money", 
#               Q4_item == "Q4b" ~ "Fame",
#               Q4_item == "Q4c" ~ "Help others",
#               Q4_item == "Q4d" ~ "Supervise others",
#               Q4_item == "Q4e" ~ "Job sec. and opp.",
#               Q4_item == "Q4f" ~ "Work w/ people",
#               Q4_item == "Q4g" ~ "Invent/design",
#               Q4_item == "Q4h" ~ "Develop knowledge/skill",
#               Q4_item == "Q4i" ~ "Personal/fam. time",
#               Q4_item == "Q4j" ~ "Easy job",
#               Q4_item == "Q4k" ~ "Exciting env.",
#               Q4_item == "Q4l" ~ "Solve societal prob.",
#               Q4_item == "Q4m" ~ "Use talent/abilities",
#               Q4_item == "Q4n" ~ "Do hands-on work",
#               Q4_item == "Q4o" ~ "Apply math/sci.",
#               Q4_item == "Q4p" ~ "Volunteer w/ charity"),
#     cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q4_resp)),
#     test = purrr::map(data, ~chisq.test(.$cluster_time_rank, .$Q4_resp)),
#     tidied = purrr::map(test, tidy),
#     

```




#### Table of chi square test results

```{r}

nested %>% 
  select(Q4_item, Q4_item_name, tidied) %>% 
  unnest(tidied) %>% kable()

```


#### Using kruskal-wallis instead of chi square since outcome is Likert-scale item (i.e., ordinal variable)

```{r}

#kruskal.test(Q4c ~ cluster_time_rank, data = climate_df)


nested <- career_sat_df %>% 
  group_by(Q4_item) %>% 
  nest(-Q4_item) %>% 
  mutate(
    Q4_item_name = case_when(Q4_item == "Q4a" ~ "Make money", 
              Q4_item == "Q4b" ~ "Fame",
              Q4_item == "Q4c" ~ "Help others",
              Q4_item == "Q4d" ~ "Supervise others",
              Q4_item == "Q4e" ~ "Job sec. and opp.",
              Q4_item == "Q4f" ~ "Work w/ people",
              Q4_item == "Q4g" ~ "Invent/design",
              Q4_item == "Q4h" ~ "Develop knowledge/skill",
              Q4_item == "Q4i" ~ "Personal/fam. time",
              Q4_item == "Q4j" ~ "Easy job",
              Q4_item == "Q4k" ~ "Exciting env.",
              Q4_item == "Q4l" ~ "Solve societal prob.",
              Q4_item == "Q4m" ~ "Use talent/abilities",
              Q4_item == "Q4n" ~ "Do hands-on work",
              Q4_item == "Q4o" ~ "Apply math/sci.",
              Q4_item == "Q4p" ~ "Volunteer w/ charity"),
    cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q4_resp)),
    test = purrr::map(data, ~kruskal.test(.$cluster_time_rank, .$Q4_resp)),
    tidied = purrr::map(test, tidy)
    )



```


```{r}

nested %>% 
  select(Q4_item, Q4_item_name, tidied) %>% 
  unnest(tidied) %>% kable()

```





## Q5 career topic interests for all ten topics in Q5 by cluster (instead of major)



```{r}

# Add new variables related to career interest (or a new, long dataframe for plotting)

career_interest_df <- climate_df  %>% 
  select(student_id, Q5a:Q5j, major, cluster_time_rank) %>% 
  pivot_longer(cols = Q5a:Q5j, names_to = "Q5_item", values_to = "Q5_resp")


climate_df <- climate_df %>% 
  mutate(Q5_total = Q5a + Q5b + Q5c + Q5d + Q5e + Q5f + Q5g + Q5h + Q5i + Q5j)



## Prepare labels for facet plots of career interest proportions broken down by topic and cluster (or major)

q5_labs <- c("Energy (supply/demand)", 
              "Disease",
              "Poverty and wealth dist.",
              "Climate change",
              "Terrorism and war",
              "Water supply",
              "Food availability",
              "Opp. for future gen",
              "Opp. for women and/or min.",
             "Environmental degradation")

names(q5_labs) <- c("Q5a",
                     "Q5b",
                     "Q5c",
                     "Q5d",
                     "Q5e",
                     "Q5f",
                     "Q5g",
                     "Q5h",
                     "Q5i",
                    "Q5j")

```


### Table of average number of topics that students in each cluster identified

```{r}

climate_df %>% 
  select(Q5a:Q5j, Q5_total, cluster_time_rank) %>% 
  group_by(cluster_time_rank) %>% 
  summarize(n = n(),
            avg_Q5_total = mean(Q5_total)) %>% 
  arrange(desc(avg_Q5_total))




```


### Number of Q5 topics identified in each cluster

```{r}


climate_df %>% 
  ggplot(aes(x = Q5_total)) +
  geom_histogram() +
  facet_wrap(. ~ cluster_time_rank) +
  labs(x = "Total Number of Q5 topics",
       y = "Count",
       title = "Number of Q5 topics identified by cluster") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))

```



### Proportions of each cluster interested in Q5 topics

```{r}


career_interest_df %>%   
  ggplot(aes(x = as_factor(cluster_time_rank), fill = factor(Q5_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("No", "Yes")) +
  facet_wrap(. ~ Q5_item, 
             scales = "free",
             labeller = labeller(Q5_item = q5_labs)) +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q5 topic by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


```


#### Interests within each cluster


```{r}


career_interest_df %>%  
  mutate(Q5_item_name = case_when(Q5_item == "Q5a" ~ "Energy (supply/demand)", 
              Q5_item == "Q5b" ~ "Disease",
              Q5_item == "Q5c" ~ "Poverty and wealth dist.",
              Q5_item == "Q5d" ~ "Climate change",
              Q5_item == "Q5e" ~ "Terrorism and war",
              Q5_item == "Q5f" ~ "Water supply",
              Q5_item == "Q5g" ~ "Food availability",
              Q5_item == "Q5h" ~ "Opp. for future gen",
              Q5_item == "Q5i" ~ "Opp. for women and/or min.",
              Q5_item == "Q5j" ~ "Environmental degradation")) %>% 
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = Q5_item_name, 
             fill = factor(Q5_resp))) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Set1", labels = c("No", "Yes")) +
  facet_wrap(. ~ cluster_time_rank, 
             scales = "free") +
  labs(x = "Cluster", y = "Proportion", fill = "", title = "Proportions of Q5 topic by cluster") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


```




```{r}

climate_df %>% 
  group_by(cluster_time_rank) %>% 
  summarize(n = n(),
            Q5a_total = sum(Q5a),
            Q5a_prop = Q5a_total / n,
            Q5b_total = sum(Q5b),
            Q5b_prop = Q5b_total / n,
            Q5c_total = sum(Q5c),
            Q5c_prop = Q5c_total / n,
            Q5d_total = sum(Q5d),
            Q5d_prop = Q5d_total / n,
            Q5e_total = sum(Q5e),
            Q5e_prop = Q5e_total / n,
            Q5f_total = sum(Q5f),
            Q5f_prop = Q5f_total / n,
            Q5g_total = sum(Q5g),
            Q5g_prop = Q5g_total / n,
            Q5h_total = sum(Q5h),
            Q5h_prop = Q5h_total / n,
            Q5i_total = sum(Q5i),
            Q5i_prop = Q5i_total / n,
            Q5j_total = sum(Q5j),
            Q5j_prop = Q5j_total / n) %>% 
  pivot_longer(cols = ends_with("prop"), 
               names_to = "Q5_item", 
               values_to = "Q5_item_prop") %>%
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = reorder_within(Q5_item, Q5_item_prop, cluster_time_rank), 
             y = Q5_item_prop, 
             fill = Q5_item)) +
  geom_col() +
  facet_wrap(. ~ cluster_time_rank, scales = "free") +
  scale_x_reordered() +
  coord_flip() +
  theme_light() +
  theme(legend.position = "none", plot.title = element_text(hjust=0.5)) +
  labs(x = "Career topic",
       y = "Proportion",
       title = "Proportion of cluster interested in various career topics") 

```



```{r}

### using nest, map, and broom to run all chi square tests at once

nested <- career_interest_df %>% 
  group_by(Q5_item) %>% 
  nest(-Q5_item) %>% 
  mutate(
    Q5_item_name = case_when(Q5_item == "Q5a" ~ "Energy (supply/demand)", 
              Q5_item == "Q5b" ~ "Disease",
              Q5_item == "Q5c" ~ "Poverty and wealth dist.",
              Q5_item == "Q5d" ~ "Climate change",
              Q5_item == "Q5e" ~ "Terrorism and war",
              Q5_item == "Q5f" ~ "Water supply",
              Q5_item == "Q5g" ~ "Food availability",
              Q5_item == "Q5h" ~ "Opp. for future gen",
              Q5_item == "Q5i" ~ "Opp. for women and/or min.",
              Q5_item == "Q5j" ~ "Environmental degradation"),
    cont_tab = purrr::map(data, ~table(.$cluster_time_rank, .$Q5_resp)),
    test = purrr::map(data, ~chisq.test(.$cluster_time_rank, .$Q5_resp)),
    tidied = purrr::map(test, tidy),
    m_plot = mosaicplot(cont_tab[[1]], shade = TRUE, 
                        main = paste0("Want to address in career - topic: ", Q5_item_name))
    )



```



```{r}

nested %>% 
  select(Q5_item, Q5_item_name, tidied) %>% 
  unnest(tidied) %>% kable()

```





## End of career interest section










# End cluster analysis




```{r}

## Career topic interests (Q5) by major

# climate_df %>% 
#   select(Q5a:Q5j, Q5_total, major) %>% 
#   group_by(major) %>% 
#   summarize(n = n(),
#             avg_Q5_total = mean(Q5_total)) %>% 
#   arrange(desc(avg_Q5_total))

```


```{r}

# climate_df %>% 
#   ggplot(aes(x = Q5_total)) +
#   geom_histogram() +
#   facet_wrap(. ~ major) +
#   labs(x = "Total Number of Q5 topics",
#        y = "Count",
#        title = "Number of Q5 topics identified by major") +
#   theme_bw() +
#   theme(plot.title = element_text(hjust = 0.5))


```


```{r}

# career_interest_df %>%   
#   ggplot(aes(x = major, fill = factor(Q5_resp))) +
#   geom_bar(position = "fill") +
#   scale_fill_brewer(palette = "Set2", labels = c("No", "Yes")) +
#   facet_wrap(. ~ Q5_item, 
#              scales = "free",
#              labeller = labeller(Q5_item = q5_labs)) +
#   labs(x = "Major", y = "Proportion", fill = "", title = "Proportions of Q5 topic by major") +
#   coord_flip() +
#   theme(plot.title = element_text(hjust = 0.5))



```


