---
title: "Q27 Imputation and UMAP"
author: "Katz et al."
date: "5/16/2021"
output: html_document
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}

library(RColorBrewer)
library(tidyverse)
library(dbscan)
library(umap)
library(psych)
library(gmodels)
library(graphics)
library(knitr)
library(purrr)
library(tidytext)
library(ggmosaic)
library(brms)
library(lme4)
library(parallel)
library(ggridges)
library(tidybayes)
library(ggridges)

library(ggmcmc)
library(maps)
library(ggmap)

library(cluster)
library(factoextra)
library(mice)

library(uwot)

library(rstatix)

library(sjPlot)

set.seed(123)

```




```{r}

#climate_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/updated_climate_df_2.csv")
data_folder <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/"
data_file <- "updated_climate_df_2.csv"

climate_df <- read_csv(paste0(data_folder, data_file))


## Drop duplicates
climate_df <- climate_df %>% distinct(Litho, .keep_all = TRUE)
# check for possible duplicates
#climate_df %>% group_by(Litho) %>% filter(n() > 1) %>% arrange(Litho) %>% ungroup()


## Add in major as string instead of number

climate_df <- climate_df %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))



climate_df <- climate_df %>% 
  rowid_to_column(var = "student_id")

```


```{r}
# create variable vectors

#test_df <- climate_df %>% select(Q7_vars, Q7tally_vars, Q7wt_sum_vars, Q7other_vars, Q7disc_vars,Q7eng_ele_vars, Q7non_eng_vars)

Q1_vars <- paste0("Q1", letters[1:20])
Q2_vars <- paste0("Q2", letters[1:7])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])
Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")
Q7wt_sum_vars <- paste0("Q7", letters[1:22], "_wt_sum")
Q7other_vars <- paste0("Q7", letters[1:22], "_other")
Q7disc_vars <- paste0("Q7", letters[1:22], "_disc_spec")
Q7eng_ele_vars <- paste0("Q7", letters[1:22], "_eng_ele")
Q7non_eng_vars <- paste0("Q7", letters[1:22], "_non_eng_ele")


Q16_vars <- paste0("Q16", letters[1:13])



Q27_vars <- paste0("Q27", letters[1:9])
last_letter <- 9
Q27_tri_num_vars <- paste0("Q27", letters[1:last_letter], "_tri_num")

Q28_vars <- paste0("Q28", letters[1:12])

Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])



```




Looking at counts by demographic variables, especially NAs

```{r}
# [OLD] Looking at counts by 
# climate_df %>% count(Q29, sort = TRUE) # 735 NAs
# 
# climate_df %>% count(Q32) # 597 NAs
# 
# climate_df %>% filter(!is.na(Q29)) %>% count(Q32) #156 NAs
# 
# 
# climate_df %>% count(Q33)
# 
# climate_df %>% filter(!is.na(Q29)) %>% count(Q33, sort = TRUE)
# 
# climate_df %>% count(Q37)


```



Drop NAs for specific questions and filter out disciplines with fewer than 30 (the cutoff) students in sample

```{r}




# climate_df <- climate_df %>% 
#   drop_na(Q29, Q18k, Q20a, Q20b, Q20d, Q18k, Q22) %>%
#   drop_na(Q23a, Q23b, Q23c, Q23d, Q23e, Q23f, Q23g, Q23h, Q23i, Q23j) %>%
#   drop_na(Q24a, Q24b, Q24c, Q24d, Q24e, Q24f, Q24g, Q24h, Q24i, Q24j, Q24k) %>%
#   drop_na(Q25a, Q25b, Q25c) %>%
#   drop_na(Q26a, Q26b, Q26c, Q26d, Q26e, Q26f, Q26g, Q26h) %>%
#   drop_na(Q27_vars) %>%
#   drop_na(Q28_vars)

# climate_df <- climate_df %>% 
#   drop_na(Q29, Q27_vars, Q32, Q37, Q40)

# climate_df %>% count(Q29, sort = TRUE)

#cutoff <- 30


# climate_df <- climate_df %>% 
#   add_count(Q29, name = "major_count") %>% 
#   filter(major_count > 30)


#climate_df %>% count(Q29, sort = TRUE)

#count_tbl <- climate_df %>% count(Q29, major, sort = TRUE)

```


Major counts and percentages
```{r}
# [OLD]
# count_tbl %>% 
#   mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
#   mutate(cumulat_pct = round(cumsum(n)/sum(n)*100, 2)) %>% 
#   kable()
```

Gender counts overall
```{r}

# [OLD]
# climate_df %>% count(Q37) %>% 
#   mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
#   kable()
```



fill in 0s for NAs for specific items (Q1, Q3, Q5)
```{r}


### Fill in NAs for specific items ---- 




#climate_df[, Q1_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q1_vars), ~replace_na(., 0))
#climate_df[, Q1_vars]

#climate_df[, Q3_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q3_vars), ~ replace_na(.,0))
#climate_df[, Q3_vars]

#climate_df[,Q5_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q5_vars), ~ replace_na(.,0))
#climate_df[, Q5_vars]

#climate_df[, Q7_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q7_vars), ~ replace_na(., 0))
#climate_df[,Q7_vars]

#climate_df[, Q35_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q35_vars), ~ replace_na(., 0))
#climate_df[,Q35_vars]

#climate_df[, Q39_vars]
climate_df <- climate_df %>% mutate_at(all_of(Q39_vars), ~ replace_na(., 0))
#climate_df[,Q39_vars]


#climate_df[, Q28_vars]
#climate_df <- climate_df %>% drop_na(Q28_vars)
#climate_df[, Q28_vars]
#climate_df <- climate_df %>% drop_na(Q16_vars)





```


Inspect missing data patterns

```{r}
# include Q7 individual indicator columns
# climate_df_sel <- climate_df %>% select(Q1a:Q39i, Q7a_eng_ele:Q7v_other) %>% 
#   select(-c(Q33_writein, Q37_writein, Q38_writein))

# exclude Q7items
climate_df_sel <- climate_df %>% select(student_id:Q40)



#md.pattern(climate_df_sel)


```

Impute missing values

```{r imp-setup}

# get general imputation model without actually imputing (by setting maxit = 0)
climate_imp <- mice(climate_df_sel, m = 1, maxit = 0)

# if wanting to look at which methods are being used for imputation
#climate_imp_2$method


## When setting variables not to impute, be careful to also remove them
# as predictors from the predictor matrix

# identify variables not to be imputed
do_not_impute <- c("student_id", "Litho", "School", 
                   "Q29", "Q30", "Q31", "Q32", "Q33", "Q34", "Q35a", "Q35b",
                   "Q35c", "Q35d", "Q35e", "Q35f", "Q35g", "Q35h", "Q35i",
                   "Q36a", "Q36b", "Q37", "Q38", "Q39a",
                   "Q33_writein", "Q37_writein", "Q38_writein",
                   "Q39b", "Q39c", "Q39d", "Q39e", "Q39f", "Q39g", "Q39h","Q39i",
                   "Q39_writein", "Q40", Q7_vars)
                   
                   
#, Q7tally_vars, Q7wt_sum_vars, Q7other_vars, Q7disc_vars, Q7eng_ele_vars, Q7non_eng_vars)


do_not_use_to_predict <- c(do_not_impute, "Q6a", "Q6d", "Q6e", "Q6i", "Q6j", "Q8j", "Q8n")



# first attempt to exclude variables from imputation
# get predictor matrix to identify demographic variables not to be imputed
pred <- climate_imp$predictorMatrix


# tried by specifying predictor matrix
pred[,do_not_use_to_predict] <- 0 # this did not seem to work

# second attempt: try specifying method = ""
meth <- climate_imp$method
meth[do_not_impute] <- ""

# sanity check
#meth # check passed


```


```{r imp-run}
# take a subsection of the original data to figure out how to avoid imputing some variables
#short_df <- climate_df_sel %>% head(100)


m_dataset <- 40


# estimate imputation model
# climate_imp <- mice(climate_df_sel, m = m_dataset, maxit = 10, predictorMatrix = pred, method = meth)


# climate_imp <- parlmice(climate_df_sel, m = m_dataset,
#                         maxit = 10, predictorMatrix = pred, method = meth,
#                         cluster.seed = 123, n.core = parallel::detectCores())


```

```{r}


# saveRDS(climate_imp, file = "climate_imp_40_2021-05-01.rds")

#use the readRDS version - seems to work
climate_imp_read <- readRDS(file = "climate_imp_40_2021-05-01.rds")

# miceadds::write.mice.imputation(climate_imp, name = "climate_imp_40_2021_05_01")
```


```{r imp-long}
#climate_imp$loggedEvents




# climate_imp_long <- complete(climate_imp, action = "long", include = TRUE)

```


```{r imp-add-q7}

# make df of Q7 items and their recodings to join to the imputed datasets 
# the original way of carrying these variables through the imputation seemed to 
# 

# climate_q7_df <- climate_df %>%
#   select(student_id, Q7tally_vars, Q7wt_sum_vars, Q7other_vars, Q7disc_vars, Q7eng_ele_vars, Q7non_eng_vars)
# # 
# climate_imp_long <- climate_imp_long %>% inner_join(climate_q7_df, by = "student_id")

```



```{r imp-write}

# write the imputed dataset to csv
# climate_imp_long %>% write_csv(paste0("climate_imputed_", m_dataset,
#                                       "_", Sys.Date(), ".csv"))

# 2021-04-17 contains 5 imputed datasets with 10 iterations each
# 2021-04-18 contains 5 imputed datasets with 10 iterations each
# 2021-04-21 contains 20 imputed datasets with 10 iterations each
# 2021-04-22 contains 20 imputed datasets with 10 iterations each and q7 extra vars
# 2021-05-01 contains 40 imputed datasets with 10 iterations each and q7 extra vars
```





```{r imp-read}
# read in most recent version of imputed dataset
data_folder <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering/"
data_file <- "climate_imputed_40_2021-05-01.csv"

climate_imp_long <- read_csv(paste0(data_folder, data_file))




nested_imp <- climate_imp_long %>% group_by(.imp) %>% nest() %>% ungroup()



###
# Try dropping .imp == 0 (the original dataset) for all of the analysis and then adding it back in at the end

nested_imp <- nested_imp %>% 
  filter(.imp != 0)

nested_imp$data[[3]]

```

Explore imputed datasets
```{r}
# just check to see what the distributions look like
climate_imp_long %>% 
  ggplot(aes(x = Q27a)) +
  geom_histogram() +
  facet_grid(.imp ~ .)


```


```{r}
# [OLD]
# climate_df <- climate_df %>% drop_na(all_of(Q28_vars))
# climate_df <- climate_df %>% drop_na(all_of(Q27_vars)) #should have 3313 observations

nested_imp <- nested_imp %>% 
  mutate(data = purrr::map(.x = data, 
                           ~mutate(.x, 
                                   Q28_social = Q28c + Q28d + Q28e+Q28j+ Q28l,
                                   Q28_tech = Q28a+Q28f+Q28g+Q28h+Q28i+ Q28k,
                                   Q28_social_norm = Q28_social / 5,
                                   Q28_tech_norm = Q28_tech / 6)))


# [OLD]
# climate_df <- climate_df %>% 
#   mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
#          Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
#          Q28_social_norm = Q28_social / 5,
#          Q28_tech_norm = Q28_tech / 6)


```


```{r}
# [OLD]
# Drop majors with low counts (below 30 students in sample)

# climate_df %>% count(Q29, sort = TRUE)
# climate_df %>% count(major, sort = TRUE)
# cutoff <- 30
# 
# climate_df <- climate_df %>% add_count(Q29, name = "major_count") %>% filter(major_count > cutoff)

```




```{r}
# UMAP functions with uwot

uwot_umap <- function(df, umap_min_dist, umap_spread, umap_n_comp, umap_n_nei, metric) {
  df %>% 
    select(all_of(Q27_vars)) %>%
    uwot::umap(min_dist = umap_min_dist, 
               spread = umap_spread, 
               n_components = umap_n_comp,
               n_neighbors = umap_n_nei,
               metric = metric) %>% 
    as_data_frame()
}

uwot_umap_ab <- uwot_umap <- function(df, a, b) {
  df %>% 
    select(-student_id) %>%
    uwot::umap(a = a, b = b) %>% 
    as_data_frame()
}


uwot_plot <- function(df, min_dist = "", spread = "", n_nei = "", metric = ""){
  p <- df %>% 
    ggplot(aes(x = V1, y = V2)) +
    geom_point() +
    labs(title = paste0("min_dist=", min_dist, 
                        ", spread=", spread, ", n_nei=", n_nei, ", metric=", metric)) +
    theme(strip.text.x = element_text(size = 7)) +
    theme_light()
  
  return(p)
}

uwot_plot_ab <- function(df, a = "", b = ""){
  p <- df %>% 
    ggplot(aes(x = V1, y = V2)) +
    geom_point() +
    labs(title = paste0("a = ", a, 
                        ", b = ", b)) +
    theme(strip.text.x = element_text(size = 7)) +
    theme_light()
  
  return(p)
}

```




# Clustering Process (two-step process using UMAP + HDBSCAN)

```{r}


nested_imp <- nested_imp %>%
  mutate(data = purrr::map(data,
                    ~ mutate(.x, 
                             Q27a_tri_num = case_when(Q27a == 1 | Q27a == 2 ~ 0,
                                  Q27a == 3 | Q27a == 4 ~1, 
                                  Q27a == 5 ~ 2),
                             Q27b_tri_num = case_when(Q27b == 1 | Q27b == 2 ~ 0,
                                  Q27b == 3 | Q27b == 4 ~1,
                                  Q27b == 5 ~ 2),
                             Q27c_tri_num = case_when(Q27c == 1 | Q27c == 2 ~ 0,
                                  Q27c == 3 | Q27c == 4 ~ 1,
                                  Q27c == 5 ~ 2),
                             Q27d_tri_num = case_when(Q27d == 1 | Q27d == 2 ~ 0,
                                  Q27d == 3 | Q27d == 4 ~ 1,
                                  Q27d == 5 ~ 2),
                             Q27e_tri_num = case_when(Q27e == 1 | Q27e == 2 ~ 0,
                                  Q27e == 3 | Q27e == 4 ~ 1,
                                  Q27e == 5 ~ 2),
                             Q27f_tri_num = case_when(Q27f == 1 | Q27f == 2 ~ 0,
                                  Q27f == 3 | Q27f == 4 ~ 1,
                                  Q27f == 5 ~ 2),
                             Q27g_tri_num = case_when(Q27g == 1 | Q27g == 2 ~ 0,
                                  Q27g == 3 | Q27g == 4 ~ 1,
                                  Q27g == 5 ~ 2),
                             Q27h_tri_num = case_when(Q27h == 1 | Q27h == 2 ~ 0,
                                  Q27h == 3 | Q27h == 4 ~ 1,
                                  Q27h == 5 ~ 2),
                             Q27i_tri_num = case_when(Q27i == 1 | Q27i == 2 ~ 0,
                                  Q27i == 3 | Q27i == 4 ~ 1,
                                  Q27i == 5 ~ 2))))





# [OLD]
# climate_27_tri_df <- climate_df %>% 
#   select(student_id, Q5a, Q5b, Q5c, Q5d, Q5e, Q5f, Q5g, Q5h, Q5i, Q5j, Q27_tri_num_vars)

nested_imp <- nested_imp %>% 
  mutate(climate_27_tri_df = purrr::map(data,
                    ~ select(.x, c(.id, all_of(Q27_tri_num_vars)))))

nested_imp$climate_27_tri_df[[1]]
```


```{r}

## attempt to use UMAP on original Q27 items (not the recoded ternary versions)

nested_imp <- nested_imp %>% 
  mutate(climate_27_df = purrr::map(data, 
                                    ~select(.x, c(.id, all_of(Q27_vars)))))
  
nested_imp$climate_27_df[[1]]
```



```{r}

#dim red and clustering with uwot::umap instead of umap::umap

# cl_df <- nested_imp$data[[4]]
# 
# cl_df <- cl_df %>% 
#   select(student_id, Q27_tri_num_vars)

```







First perform dimension reduction using UMAP
```{r}


#Q27_tri_num_vars <- c("Q27a_tri_num", "Q27b_tri_num", "Q27c_tri_num")

# create custom settings for umap
custom.settings = umap.defaults
#custom.settings$n_neighbors = 30
custom.settings$n_components = 2
custom.settings$n_neighbors = 30 # next time, try dropping this from 55 to 30
custom.settings$min_dist = 0.00001 # experimental, dropping down from 0.1 to 0.0
custom.settings$metric = 'euclidean'

## 30 neighbors seems to work well

nested_imp <- nested_imp %>% 
  mutate(climate_27_tri_umap = purrr::map(.x = climate_27_tri_df, 
                                          ~ select(.x, all_of(Q27_tri_num_vars)) %>%
                                                     umap::umap(random_state = 123, 
                                                          config = custom.settings)))


# testing umap on one of the five imputed datasets
#nested_imp$climate_27_tri_df[[1]]


# nested_imp$climate_27_tri_df[[3]]


nested_imp <- nested_imp %>% 
  mutate(plot_df = purrr::map(.x = climate_27_tri_umap,
                       ~ as_tibble(.x$layout)))

             

nested_imp <- nested_imp %>% 
  mutate(plot_df = purrr::map(.x = plot_df,
                              ~ rename(.x, 
                                       dim1 = V1,
                                       dim2 = V2)))

nested_imp <- nested_imp %>% 
  mutate(data = purrr::map2(.x = data, .y = plot_df,
                            ~ bind_cols(.x, .y)))

#nested_imp$climate_27_tri_umap
nested_imp$data[[2]]

# check one example of the five imputed datasets to see what the UMAP projection looks like


ggplot(data = nested_imp$plot_df[[1]], aes(x = dim1, y = dim2)) +
  geom_point()
```





```{r}
# try clustering with agglomerative clustering

# need to use plot_df because that has the two-dimension reduction from UMAP

agg_df <- nested_imp$plot_df[[1]]
  
  
```



```{r}

hc2 <- agnes(agg_df, method = "ward")

```


```{r}
pltree(hc2, cex = 0.6, hang = -1)
```

```{r}

sub_grp <- cutree(hc2, k = 8)
table(sub_grp)

agg_df$cl <- sub_grp
```

```{r}
cl_tri_df <- nested_imp$climate_27_tri_df[[1]]

```

```{r}
cl_tri_df$cluster <- agg_df$cl

cl_tri_df
```

```{r}
fviz_nbclust(agg_df, FUNcluster = hcut, method = "wss")
```




# Next, perform clustering using either HDBSCAN or agglomerative clustering



# Option 1: using HDBSCAN

```{r}
# perform clustering using HDBSCAN on the dim-reduced data
# clustering with min 60 pts leaves 131 unclustered
#clustering with 40 creates 13 groups and 29 unclustered
### Best combination: n_components=2, n_neighbords=80, min_dist=0.001, minPts=90 (or 50)
### also good: n_comp=2, n_neigh=20 or 30, min_dist=0.0001, minPts=50
nested_imp <- nested_imp %>% 
  mutate(hdbscan_umap_cl = purrr::map(.x = plot_df, 
                               ~ hdbscan(.x, minPts = 150))) 
# groups stay pretty similar from minPts 70 up to 150, when it drops from 9 to 6 clusters





# check one example of the clustering
nested_imp$hdbscan_umap_cl[[4]] # check passed


# [OLD] add the cluster labels to the plotting dataframe
#plot_df$cluster <- hdbscan_umap_cl$cluster

nested_imp <- nested_imp %>% 
  mutate(plot_df = purrr::map2(.x = plot_df, .y = hdbscan_umap_cl,
                              ~ mutate(.x, cluster = .y$cluster)))

# sensibility check
#nested_imp$plot_df[[1]]$cluster #check passed

# plot the reduction with the clusters
nested_imp$plot_df[[1]] %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of simplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


# add the cluster labels back to the original data set
nested_imp <- nested_imp %>% 
  mutate(climate_27_tri_df = purrr::map2(.x = climate_27_tri_df, .y = hdbscan_umap_cl,
                              ~ mutate(.x, cluster = .y$cluster)))


# sanity check of clusters being stored for plotting -- check passed
# nested_imp$climate_27_tri_df[[2]] %>% 
#   ggplot(aes(x = cluster)) +
#   geom_histogram() +
#   labs(x = "Cluster",
#        y = "Count",
#        title = "Histogram of clusters for Question 27 ternary split") +
#   theme_bw() +
#   theme(plot.title = element_text(hjust = 0.5, size = 8))


# create cluster distribution plots for each of the imputed datasets
nested_imp <- nested_imp %>% 
  mutate(cluster_hist = purrr::map(.x = climate_27_tri_df,
                                   ~ ggplot(.x, aes(x = cluster)) +
                                     geom_histogram() +
                                     labs(x = "Cluster",
                                          y = "Count",
                                          title = "Histogram of clusters for Q27 ternary split") +
                                     theme_light() +
                                     theme(plot.title = element_text(hjust=0.5, size = 8))))



```


## For using agglomerative clustering instead of HDBSCAN (choose one or the other, not both)

```{r}
# add option for agglomerative clustering instead of hdbscan
nested_imp <- nested_imp %>% 
  mutate(agg_umap_cl = purrr::map(.x = plot_df, 
                               ~ cluster::agnes(.x, method = "ward")))
```


```{r}
# write_rds(nested_imp, file = paste0("nested_imp_umap_cl_", Sys.Date(), ".rds"))

# wrote to rds to save umap projects and agglomerative clusters since the clustering took so long
```

```{r}
# reading in the RDS saved in the prior block -- need to save agg and hdb clusters in separate columns
nested_imp <- read_rds("nested_imp_umap_cl_2021-05-04.rds")
```


```{r}

```





```{r}

# hard coding number of clusters
k <- 8

nested_imp <- nested_imp %>% 
  mutate(agg_clusters = purrr::map(.x = agg_umap_cl, 
                              ~cutree(.x, k = k)))

```





## Original clustering implementation (implemented in each of the imputation scripts)



```{r}
# perform clustering using HDBSCAN on the dim-reduced data
# clustering with min 60 pts leaves 131 unclustered
#clustering with 40 creates 13 groups and 29 unclustered
### Best combination: n_components=2, n_neighbords=80, min_dist=0.001, minPts=90 (or 50)
### also good: n_comp=2, n_neigh=20 or 30, min_dist=0.0001, minPts=50
hdbscan_umap_cl <- hdbscan(plot_df, minPts = 120) 
# groups stay pretty similar from minPts 70 up to 150, when it drops from 9 to 6 clusters

hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
plot_df$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of simplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


# add the cluster labels back to the original data set
climate_27_df$cluster <- hdbscan_umap_cl$cluster

climate_27_tri_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for Question 27 ternary split") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



```




Join the dataframes back together again

```{r}
# Add the cluster assignments back to the original climate_df dataframe
climate_df <- climate_27_tri_df %>% select(student_id, cluster) %>% inner_join(climate_df, by = "student_id")
```


```{r}
#climate_df <- climate_df %>% rename(cluster = cluster.y)

climate_df %>% count(cluster, sort = TRUE)


```




## Views of when climate change will affect different groups broken down by cluster assignments


## Looking for patterns in the clusters


```{r}
q27_item_list <- list(
  'Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment"
)

q27_labs <- c("Me personally", 
              "My family",
              "People in my comm.",
              "People in US",
              "Other indust. countr.",
              "Developing countries",
              "Plant + animal species",
              "World's poor",
              "Natural environment")

names(q27_labs) <- c("Q27a_tri_num",
                     "Q27b_tri_num",
                     "Q27c_tri_num",
                     "Q27d_tri_num",
                     "Q27e_tri_num",
                     "Q27f_tri_num",
                     "Q27g_tri_num",
                     "Q27h_tri_num",
                     "Q27i_tri_num")
```



# Understanding cluster compositions more


#### First create a dataframe with the rankings for each cluster, where a lower ranking means students in the cluster think climate change will affect more categories sooner. 



```{r}

## create dataframe with rankings for cluster by how soon each cluster believes climate change will affect groups
cluster_ranking_df <- climate_df %>% 
  mutate(Q27_tri_total = Q27a_tri_num + Q27b_tri_num + Q27c_tri_num + Q27d_tri_num + Q27e_tri_num +
           Q27f_tri_num + Q27g_tri_num + Q27h_tri_num + Q27i_tri_num) %>% 
  group_by(cluster) %>% 
  summarize(cluster_avg = mean(Q27_tri_total)) %>% 
  arrange(cluster_avg) %>% 
  rowid_to_column(var = "cluster_time_rank")

cluster_ranking_df

climate_df <- climate_df %>% 
  inner_join(cluster_ranking_df, by = "cluster")

#climate_27_tri_df %>% inner_join(cluster_ranking_df, by = "cluster")


```


Set clustering colors for all plots
```{r}
#Old method of randomly assigning colors
# cluster_num <- length(unique(climate_df$cluster))
# 
# cluster_colors <- colorRampPalette(brewer.pal(9, "Set1"))(cluster_num)

# new method of assigning cluster colors along a gradient
cluster_num <- length(unique(climate_df$cluster_time_rank))

# cluster colors with red, yellow, green
#cluster_colors <- colorRampPalette(c("#ec3434", "#f7c035", "#007030"))(cluster_num)

# cluster colors with grayscale
cluster_colors <- colorRampPalette(c("#000000", "#a8adb5", "#dedede"))(cluster_num)


```



### Look at distribution of cluster for how when they think each community may be affected by global warming

```{r}
climate_df %>%
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>% 
  ggplot(aes(x = as_factor(response))) +
  geom_bar(aes(fill = as_factor(cluster_time_rank))) +
  facet_wrap(.~ survey_item, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "Converted Ternary Response (0 = Now, 1 = Later, 2 = Never)",
       y = "Count",
       title = "Histogram of when will global warming affect different groups?",
       fill = "Cluster") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = cluster_colors)

```

Same information but faceted with clusters

** This is a good plot for seeing that a cluster's beliefs about effects of global warming on different populations at different times vary in a clear pattern
```{r}
## for the ternary options


climate_df %>%
  #filter(cluster != 0) %>% 
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>%
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = survey_item)) +
  geom_bar(aes(fill = as_factor(response))) +
  facet_wrap(.~ cluster_time_rank, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "When will global warming affect this population?",
       y = "Count",
       title = "Cluster patterns of when will global warming affect various populations",
       fill = "Response") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = c("#000000", "#a8adb5", "#dedede"), 
                    name = "Response", 
                    labels = c("0" = "0-10 yrs", "1" = "25-50y yrs", "2" = "Never")) +
  scale_x_discrete(labels = c('Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment")) + 
  coord_flip()

```














## Investigating alternatives to the ternary UMAP implementation

```{r}
## Create the test dataset (just pick one of the 40 imputed datasets)


climate_df <- nested_imp$data[[3]]
climate_27_df <- climate_df %>% select(student_id, all_of(Q27_vars))
climate_27_tri_df <- climate_df %>% select(student_id, all_of(Q27_tri_num_vars))

```


# option 1: using umap implementation


## grid search on number of neigbors


```{r}

n_nei_seq <- seq(from = 15, to = 125, by = 5)

for (i in 1:length(n_nei_seq)){
  custom.settings = umap.defaults
  #custom.settings$n_neighbors = 30
  custom.settings$n_components = 2
  custom.settings$n_neighbors = n_nei_seq[i] # next time, try dropping this from 55 to 30
  custom.settings$min_dist = 0.00001 # experimental, dropping down from 0.1 to 0.0
  custom.settings$metric = 'euclidean'
  
  
  test_umap <- climate_27_tri_df %>% 
    select(-student_id) %>% 
    umap::umap(random_state = 357,
               config = custom.settings)
  
  
  plot_df <- as_tibble(test_umap$layout)
  
  plot_df <- plot_df %>% 
  rename(dim1 = V1,
         dim2 = V2)
  
  p <- ggplot(data = plot_df, aes(x = dim1, y = dim2)) +
    geom_point() +
    labs(title = paste0("n_nei = ", n_nei_seq[i]))
  
  print(p)

}

```


```{r}
# create custom settings for umap
custom.settings = umap.defaults
#custom.settings$n_neighbors = 30
custom.settings$n_components = 2
custom.settings$n_neighbors = 45 # next time, try dropping this from 55 to 30
custom.settings$min_dist = 0.00001 # experimental, dropping down from 0.1 to 0.0
custom.settings$metric = 'euclidean'

n_nei_seq <- seq(from = 15, to = 100, by = 5)

test_umap <- climate_27_tri_df %>% 
  select(-student_id) %>% 
  umap::umap(random_state = 357,
             config = custom.settings)


plot_df <- as_tibble(test_umap$layout)
```


# option 2: using uwot instead of umap implementation

## try grid search for a and b parameters

```{r}

a_rep <- seq(from = 0.1, to = 3, by = 0.2)
b_rep <- seq(from = 0.05, to = 1.2, by = 0.1)

for (i in 1:length(b_rep)){
  for (j in 1:length(a_rep)){
  b <- b_rep[i]
  a <- a_rep[j]
  uwot_res <- uwot_umap_ab(climate_27_tri_df, a = a, b = b)
  
  print(uwot_plot_ab(uwot_res, a = a, b = b))
  }
}


```


## final implementation
```{r}
a <- 3
b <- 1.15

uwot_res <- uwot_umap_ab(climate_27_tri_df, a = a, b = b)
uwot_plot_ab(uwot_res, a = a, b = b)


plot_df <- uwot_res
```





```{r}
plot_df <- plot_df %>% 
  rename(dim1 = V1,
         dim2 = V2)
ggplot(data = plot_df, aes(x = dim1, y = dim2)) +
  geom_point()



```





```{r}
# perform clustering using HDBSCAN on the dim-reduced data
# clustering with min 60 pts leaves 131 unclustered
#clustering with 40 creates 13 groups and 29 unclustered
### Best combination: n_components=2, n_neighbords=80, min_dist=0.001, minPts=90 (or 50)
### also good: n_comp=2, n_neigh=20 or 30, min_dist=0.0001, minPts=50
hdbscan_umap_cl <- hdbscan(plot_df, minPts = 120) 
# groups stay pretty similar from minPts 70 up to 150, when it drops from 9 to 6 clusters

hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
plot_df$new_cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(new_cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of simplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


# add the cluster labels back to the original data set
climate_27_df$new_cluster <- hdbscan_umap_cl$cluster

climate_27_df %>% 
  ggplot(aes(x = new_cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for Question 27 ternary split") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



```



```{r}
# try clustering with agglomerative clustering

# need to use plot_df because that has the two-dimension reduction from UMAP

agg_df <- nested_imp$plot_df[[1]]
  
  
```



```{r}

hc2 <- agnes(agg_df, method = "ward")

```


```{r}
pltree(hc2, cex = 0.6, hang = -1)
```

```{r}

sub_grp <- cutree(hc2, k = 8)
table(sub_grp)

agg_df$cl <- sub_grp
```

```{r}
cl_tri_df <- nested_imp$climate_27_tri_df[[1]]

```

```{r}
cl_tri_df$cluster <- agg_df$cl

cl_tri_df
```

```{r}
fviz_nbclust(agg_df, FUNcluster = hcut, method = "wss")
```




Join the dataframes back together again

```{r}
# Add the cluster assignments back to the original climate_df dataframe
climate_df <- climate_27_df %>% select(student_id, new_cluster) %>% inner_join(climate_df, by = "student_id")
```


```{r}
#climate_df <- climate_df %>% rename(cluster = cluster.y)

climate_df %>% count(new_cluster, sort = TRUE)


```




## Views of when climate change will affect different groups broken down by cluster assignments


## Looking for patterns in the clusters


```{r}
q27_item_list <- list(
  'Q27a' = "Me personally",
  "Q27b" = "My family",
  "Q27c" = "People in my comm.",
  "Q27d" = "People in US",
  "Q27e" = "Other indust. countr.",
  "Q27f" = "Developing countries",
  "Q27g" = "Plant + animal species",
  "Q27h" = "World's poor",
  "Q27i" = "Natural environment"
)

q27_labs <- c("Me personally", 
              "My family",
              "People in my comm.",
              "People in US",
              "Other indust. countr.",
              "Developing countries",
              "Plant + animal species",
              "World's poor",
              "Natural environment")

names(q27_labs) <- c("Q27a",
                     "Q27b",
                     "Q27c",
                     "Q27d",
                     "Q27e",
                     "Q27f",
                     "Q27g",
                     "Q27h",
                     "Q27i")
```



# Understanding cluster compositions more


#### First create a dataframe with the rankings for each cluster, where a lower ranking means students in the cluster think climate change will affect more categories sooner. 



```{r}

## create dataframe with rankings for cluster by how soon each cluster believes climate change will affect groups
cluster_ranking_df <- climate_df %>% 
  mutate(Q27_total = Q27a + Q27b + Q27c + Q27d + Q27e +
           Q27f + Q27g + Q27h + Q27i) %>% 
  group_by(new_cluster) %>% 
  summarize(cluster_avg = mean(Q27_total)) %>% 
  arrange(cluster_avg) %>% 
  rowid_to_column(var = "new_cluster_time_rank")

cluster_ranking_df

climate_df <- climate_df %>% 
  inner_join(cluster_ranking_df, by = "new_cluster")

#climate_27_tri_df %>% inner_join(cluster_ranking_df, by = "cluster")


```


Set clustering colors for all plots
```{r}
#Old method of randomly assigning colors
# cluster_num <- length(unique(climate_df$cluster))
# 
# cluster_colors <- colorRampPalette(brewer.pal(9, "Set1"))(cluster_num)

# new method of assigning cluster colors along a gradient
cluster_num <- length(unique(climate_df$new_cluster_time_rank))

# cluster colors with red, yellow, green
#cluster_colors <- colorRampPalette(c("#ec3434", "#f7c035", "#007030"))(cluster_num)

# cluster colors with grayscale
cluster_colors <- colorRampPalette(c("#000000", "#a8adb5", "#dedede"))(cluster_num)


```



### Look at distribution of cluster for how when they think each community may be affected by global warming

```{r}
climate_df %>%
  pivot_longer(cols = Q27a:Q27i, names_to = "survey_item", values_to = "response") %>% 
  ggplot(aes(x = as_factor(response))) +
  geom_bar(aes(fill = as_factor(new_cluster_time_rank))) +
  facet_wrap(.~ survey_item, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "Converted Ternary Response (0 = Now, 1 = Later, 2 = Never)",
       y = "Count",
       title = "Histogram of when will global warming affect different groups?",
       fill = "Cluster") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = cluster_colors)

```

Same information but faceted with clusters

```{r}

scale_num <- length(unique(climate_df$Q27a_tri_num))

# cluster colors with red, yellow, green
scale_colors <- colorRampPalette(c("#ec3434", "#f7c035", "#007030"))(scale_num)

# cluster colors with grayscale
# scale_colors <- colorRampPalette(c("#000000", "#a8adb5", "#dedede"))(scale_num)

```


** This is a good plot for seeing that a cluster's beliefs about effects of global warming on different populations at different times vary in a clear pattern
```{r}
## for the ternary options


climate_df %>%
  #filter(cluster != 0) %>% 
  pivot_longer(cols = Q27a:Q27i, names_to = "survey_item", values_to = "response") %>%
  mutate(cluster_time_rank = as_factor(new_cluster_time_rank)) %>% 
  ggplot(aes(x = survey_item)) +
  geom_bar(aes(fill = as_factor(response))) +
  facet_wrap(.~ cluster_time_rank, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "When will global warming affect this population?",
       y = "Count",
       title = "Cluster patterns of when will global warming affect various populations",
       fill = "Response") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = scale_colors, 
                    name = "Response", 
                    labels = c("1" = "Now", "2" = "10 yrs", "3" = "25 yrs",
                               "4" = "50 yrs", "5" = "Never")) +
  scale_x_discrete(labels = c('Q27a' = "Me personally",
  "Q27b" = "My family",
  "Q27c" = "People in my comm.",
  "Q27d" = "People in US",
  "Q27e" = "Other indust. countr.",
  "Q27f" = "Developing countries",
  "Q27g" = "Plant + animal species",
  "Q27h" = "World's poor",
  "Q27i" = "Natural environment")) + 
  coord_flip()

```




```{r}

```{r}
## for the ternary options


climate_df %>%
  #filter(cluster != 0) %>% 
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>%
  mutate(cluster_time_rank = as_factor(new_cluster_time_rank)) %>% 
  ggplot(aes(x = survey_item)) +
  geom_bar(aes(fill = as_factor(response))) +
  facet_wrap(.~ cluster_time_rank, 
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "When will global warming affect this population?",
       y = "Count",
       title = "Cluster patterns of when will global warming affect various populations",
       fill = "Response") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = c("#000000", "#a8adb5", "#dedede"), 
                    name = "Response", 
                    labels = c("0" = "0-10 yrs", "1" = "25-50y yrs", "2" = "Never")) +
  scale_x_discrete(labels = c('Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment")) + 
  coord_flip()

```

```

