---
title: "Q27 Ternary Items Random Forest and Modeling"
author: "Katz et al."
date: "6/12/2021"
output: html_document
---








```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
library(psych)
library(tidyverse)
library(tidymodels)
library(ranger)
library(purrrlyr)
library(purrr)
library(randomForest)
library(pander)
library(kableExtra)
library(knitr)

library(ordinalForest)

library(brms)
library(tidybayes)

```



Script for creating random forests for Q5 and Q16

```{r}
setwd("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering")

# climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/updated_climate_df_2.csv")


#original data set
#climate_data <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/climate_data.csv")

# read in the imputed dataset
climate_imp_long_full <- read_csv("climate_imp_long_hc_cl_full_40_2021-05-05.csv")

```


```{r}
pub_ds_ver <- 1
climate_data <- climate_imp_long_full %>% filter(.imp == pub_ds_ver)

rm(climate_imp_long_full)

```


```{r}

# just to get ipeds_vars
data_path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/"
file_name <- "ipeds_inst_char_2018.csv"

school_info <- read_csv(paste0(data_path, file_name))

ipeds_vars <- names(school_info)
rm(school_info)


```


```{r}

climate_data <- climate_data %>% 
  select(-one_of(ipeds_vars))

```



```{r}
# not sure if want to remove these or not

Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")
Q7wt_sum_vars <- paste0("Q7", letters[1:22], "_wt_sum")
Q7other_vars <- paste0("Q7", letters[1:22], "_other")
Q7disc_vars <- paste0("Q7", letters[1:22], "_disc_spec")
Q7eng_ele_vars <- paste0("Q7", letters[1:22], "_eng_ele")
Q7non_eng_vars <- paste0("Q7", letters[1:22], "_non_eng_ele")


```


```{r}

Q27_vars <- paste0("Q27", letters[1:9])

```





# Create a new dataframe for the random forest work

Perform EFA for Q28

```{r}



Q28_vars <- paste0("Q28", letters[1:12])


Q28_df <- climate_data %>% drop_na(Q28_vars) %>% select(Q28_vars)

Q28_fa <- fa(Q28_df, nfactors = 2, fm = "ml", rotate = "oblimin")
print(Q28_fa, cut = 0.3, digits = 3)
# use `print(fa, digits = 3)` to view FLs < .3

```

Calculate Cronbach's alpha for internal consistency reliability

```{r}


FA1 <- c("Q28a", "Q28f", "Q28g", "Q28h", "Q28i", "Q28k")
FA2 <- c("Q28c", "Q28d", "Q28e", "Q28j", "Q28l")

alpha.fa1 <- psych::alpha(Q28_df[FA1])
print(alpha.fa1, digits = 3) #0.91

alpha.fa2 <- psych::alpha(Q28_df[FA2])
print(alpha.fa2, digits = 3) #0.80


```



Add variables for Q28_tech_norm ((Q28a + Q28f + Q28g + Q28h + Q28i + Q28k) / 6) and Q28_social_norm ((Q28c + Q28d + Q28e + Q28j + Q28l) / 5)
```{r}

climate_data <- climate_data %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

```


Perform EFA for Q12

```{r}
Q12_vars <- paste0("Q12", letters[1:9])

Q12_df <- climate_data %>% drop_na(Q12_vars) %>% select(Q12_vars)

Q12_fa <- fa(Q12_df, nfactors = 2, fm = "ml", rotate = "oblimin")
print(Q12_fa, cut = 0.3, digits = 3)

```


```{r}

FA1 <- c("Q12a", "Q12b", "Q12c")
FA2 <- c("Q12d", "Q12e", "Q12f", "Q12g", "Q12h", "Q12i")

alpha.fa1 <- psych::alpha(Q12_df[FA1])
print(alpha.fa1, digits = 3) #0.83

alpha.fa2 <- psych::alpha(Q12_df[FA2])
print(alpha.fa2, digits = 3) #0.90

```



Add variables for Q12 factors (Q12abc_norm (a+b+c)/3 and Q12_defghi_norm = (d+e+f+g+h+i)/6)

```{r}

climate_data <- climate_data %>% 
  mutate(Q12abc = Q12a + Q12b + Q12c,
         Q12defghi = Q12d + Q12e + Q12f + Q12g + Q12h + Q12i,
         Q12abc_norm = Q12abc / 3,
         Q12defghi_norm = Q12defghi / 6)

```

Recode variables
```{r}

climate_data <- climate_data %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))

```



Remove majors with fewer than 30 students and students with NA for major


```{r}


climate_data %>% count(Q29, sort = TRUE)
climate_data %>% count(major, sort = TRUE)
cutoff <- 30

climate_data <- climate_data %>% 
  add_count(Q29, name = "major_count") %>% 
  filter(major_count > cutoff) %>% 
  filter(!is.na(Q29))

climate_data %>% count(Q29, sort = TRUE)

```


Fill in Q1, Q3, Q5, Q7, Q39 NAs with 0's (the way they were coded, it's ambiguous if an NA is there intentionally by the participant, so this is a conservative assumption to make that an NA actually corresponds to an intentional omission rather than an accidental omission)


```{r}
# prepraing the data
# start with the climate_data dataframe


Q1_vars <- paste0("Q1", letters[1:20])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])

Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])

Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")


#str(climate_data)

### old way to remove disciplines with 
# rf_df <- climate_data %>% 
#   filter(!is.na(Q29)) %>% 
#   filter(Q29 != 15) %>% 
#   filter(Q29 != 14) %>% 
#   filter(Q29 != 9) %>% 
#   filter(Q29 != 2)

rf_df <- climate_data

rf_df %>% group_by(Q29) %>% count()

#rf_df[, Q1_vars]
rf_df <- rf_df %>% mutate_at(vars(Q1_vars), ~replace_na(., 0))
#rf_df[, Q1_vars]

#rf_df[, Q3_vars]
rf_df <- rf_df %>% mutate_at(vars(Q3_vars), ~ replace_na(.,0))
#rf_df[, Q3_vars]

#rf_df[,Q5_vars]

#rf_df[, Q7_vars]
rf_df <- rf_df %>% mutate_at(vars(Q7_vars), ~ replace_na(., 0))
#rf_df[,Q7_vars]

#rf_df[, Q35_vars]
rf_df <- rf_df %>% mutate_at(vars(Q35_vars), ~ replace_na(., 0))
#rf_df[,Q35_vars]

#rf_df[, Q39_vars]
rf_df <- rf_df %>% mutate_at(vars(Q39_vars), ~ replace_na(., 0))
#rf_df[,Q39_vars]
```


Drop individual Q12, Q16, and Q28 items. Q16 items were too similar to Q5 items and Q28 items were factored

```{r}
Q12_vars <- paste0("Q12", letters[1:9])
Q16_vars <- paste0("Q16", letters[1:13])
Q28_vars <- paste0("Q28", letters[1:12])


rf_df <- rf_df %>% drop_na(Q12_vars)
rf_df <- rf_df %>% drop_na(Q16_vars)
rf_df <- rf_df %>% drop_na(Q28_vars)

climate_data %>% count(major, sort = T)

```

Turn the variables into factors

```{r}
# turning variables into factors


#rf_df <- dmap(rf_df, as.factor)
```


Remove additional columns that will not feed into the random forest algorithm

```{r}
# remove columns with majority na (noticed from visual inspection)
removal_vars <- c("School", "Litho", "major", "Q33_", 
                  "Q37_", "Q38_", "Q39_", "Q40", "abe", "Q16abc", "lm", "dfg", "hijk",
                  "spec", "other", "tally", "ele", "Q16_bin", "_ind")

# Q13, Q14 were originally on the removal list - not sure why - need to add back in

# consider removing "sum" from the above

removal_vars_start <- paste0("^(", paste(removal_vars, collapse="|"), ")")
removal_vars_end <- paste0("(", paste(removal_vars, collapse="|"), ")$")


# create a dataframe called train_df that we'll use for training the random forests
train_df <- rf_df %>% dplyr::select(-matches(removal_vars_start))
train_df <- train_df %>% dplyr::select(-matches(removal_vars_end))

train_df <- train_df %>% 
  dplyr::select(-Q28_tech, -Q28_social, -Q12abc, -Q12defghi)
train_df <- train_df %>% dplyr::select(-Q28_vars)
train_df <- train_df %>% dplyr::select(-Q1_vars)



# remove the original Q7 vars because they were too messy - use tallies instead

# remove other Q5 variables aside from 5e
## probably want to change this to Q16 removals

# forest_outcome_var <- "Q16c"


# Q16_removals <- c("Q5a","Q5b", "Q5c", "Q5d", "Q5e", "Q5f", "Q5g", "Q5i", "Q5j")

train_df <- train_df %>% dplyr::select(-Q7_vars)
train_df <- train_df %>% dplyr::select(-Q27_vars)
#train_df <- train_df %>% dplyr::select(-Q16_energy)
```


```{r}
factor_vars <- c("Q29", "Q32", "Q33", "Q37", Q39_vars)

train_df <- train_df %>% 
  mutate_at(factor_vars, as.factor)
  
  # mutate(Q29 = as.factor(Q29),
  #        Q37 = as.factor(Q37))

train_df %>% count(cluster_time_rank)

```





```{r}
extra_removal_vars <- c(".id", ".imp", "student_id", "full_hdb_cluster", "full_agg_cluster",
                        "cluster_time_rank_hdb", "cluster_avg_hdb", "cluster_avg_agg",
                        "dim1", "dim2")

train_df <- train_df %>% 
  select(-one_of(extra_removal_vars))
```


```{r}

# rf_mod <- randomForest(formula = Q5h ~ ., 
#                        data = q5h_train,
#                        ntree = 1000,
#                        proximity = TRUE,
#                        na.action = na.roughfix,
#                        importance = TRUE)

set.seed(42)


rf_mod <- randomForest(formula = cluster_time_rank ~ ., 
                       data = train_df,
                       ntree = 1000,
                       proximity = TRUE,
                       na.action = na.roughfix,
                       importance = TRUE)



```


```{r}

# rf_mod %>% write_rds(file = "rf_mod_agg_cl_20210520.rds")

```



```{r}

imp <- importance(rf_mod, type = 1, scale = F) # permutation importances 
#(specifying "type = 1" pulls MeanDecreaseAccuracy instead of MeanDecreaseGini)

```

Manual way of collecting variable importance data

```{r}

#row.names(imp)
featureImportance <- data.frame(Feature = row.names(imp), Importance = imp[,1])

p <- featureImportance %>% 
  top_n(30, Importance) %>% 
  ggplot(aes(x = reorder(Feature, -Importance), y = Importance)) +
  geom_bar(stat = "identity", fill = "#53cfff", width = 0.65) +
  coord_flip() + 
  theme_light(base_size = 20) +
  theme(axis.title.x = element_text(size = 10, color = "black"),
        axis.title.y = element_blank(),
        axis.text.x  = element_text(size = 10, color = "black"),
        axis.text.y  = element_text(size = 10, color = "black"),
        plot.title = element_text(size = 10, hjust = 0.5)) +
  ggtitle("Random Forest Variable Importance for Spatiotemporal Belief Patterns About Global Warming")

p



```




Calculate variable importance and plot using permutation

```{r}
# library(vip)

code_break


```







## Option 2: Ordinal forest instead of regression forest for Q16b




### Ordinal Forest instead of Regression Random Forest


```{r}
train_df <- train_df %>%
  mutate(cluster_time_rank = as.ordered(cluster_time_rank)) 
#   select(-c(cluster_time_rank_hdb, cluster_avg_hdb, cluster_avg_agg, full_agg_cluster,
#             full_hdb_cluster, dim1, dim2))
# 
# train_df <- train_df %>% 
#   select(-c(full_agg_cluster, full_hdb_cluster, dim1, dim2))
```


```{r}


# train_df %>% drop_na(Q32, Q33, Q37)

# Q27 vars were the variables used to form the clusters to begin with
Q27_tri_vars <- paste0("Q27", letters[1:9], "_tri_num")

# drop Q20a and Q20c since those are asking about uncertainty of climate change
# the other Q20 vars are okay to keep in since they are about human contributions and changing opinion
Q20_vars <- c("Q20a", "Q20c")

extra_drop_vars <- c("race_eth", "gpa", "STABBR_student", "latitude", "longitude", "state_name", "region_name", "region_code", "division_name", "division_code", "cluster_avg", "cluster_time_rank_rev", "cluster", Q27_tri_vars, Q20_vars)

ord_rf_df <- train_df %>% 
  select(-one_of("Q30", "Q31", "Q34", "Q35", "Q36a", "Q36b", "Q38", Q39_vars, "Q40",
                 extra_drop_vars)) %>% 
  drop_na(Q32, Q33, Q37)
```


```{r}

set.seed(42)

ord_rf_df %>% select(cluster_time_rank)

ord_rf_df <- as.data.frame(ord_rf_df)
# default mtry
rf_mod_ord <- ordfor(depvar = "cluster_time_rank", 
                     data = ord_rf_df, 
                     perffunction = "proportional")


```



#### Identify top 30 most important variables for ordinal prediction

```{r}
# sort(rf_mod_ord$varimp, decreasing=TRUE)

var_imp <- rf_mod_ord$varimp
# var_imp
# names(var_imp)

var_imp_df <- tibble(variable = names(var_imp),
                     var_importance = var_imp)

```

For ordinal forest variable importance measures

```{r}

p <- var_imp_df %>% 
  top_n(30, var_importance) %>% 
  ggplot(aes(x = reorder(variable, -var_importance), y = var_importance)) +
  geom_bar(stat = "identity", fill = "#53cfff", width = 0.65) +
  coord_flip() + 
  theme_light() +
  labs(x = "Variable",
       y = "Variable Importance") +
  theme(axis.title.x = element_text(size = 10, color = "black"),
        # axis.title.y = element_blank(),
        axis.text.x  = element_text(size = 10, color = "black"),
        axis.text.y  = element_text(size = 10, color = "black"),
        plot.title = element_text(size = 10, hjust = 0.5)) +
  ggtitle("Ordinal Forest Variable Importance for Career Interest in Energy Efficiency")

p

```




```{r}
code_break
```









# Bayesian modeling of outcome (spatiotemporal belief pattern cluster) as a function of top predictors identified from random forest

Top predictors from random forest:



Top predictors from ordinal forest:
Q28_tech_norm
Q20d
Q28_social_norm
Q20b
Q26b
Q19h
Q26h
Q18k


Need to change the following to ordinal:
Q20d
Q20a
Q26b
Q19h
Q20b
Q20c



## First, import the imputed dataset

```{r}

climate_imp_long_full <- read_csv("climate_imp_long_hc_cl_full_40_2021-05-05.csv")

```


```{r}
pub_ds_ver <- 1

climate_df <- climate_imp_long_full %>% filter(.imp == pub_ds_ver)

rm(climate_imp_long_full)

```



## Method using Bayesian ordinal regression


Add major column back to replace Q29 in regression models


```{r}

climate_df <- climate_df %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))

```



```{r}


str(climate_df$major)

# set reference discipline

climate_df$major <- fct_relevel(climate_df$major, "Mec") 

str(climate_df$major)

```

Q28_tech_norm
Q20d
Q28_social_norm
Q20b
Q26b
Q19h
Q26h
Q18k

Q28_tech_norm
Q20d -- strongly disagree to strongly agree
Q28_social_norm
Q20b -- strongly disagree to strongly agree
Q26b -- strongly disagree to strongly agree
Q19h -- strongly disagree to strongly agree
Q26h -- strongly disagree to strongly agree
Q18k -- strongly disagree to strongly agree


```{r}

climate_df <- climate_df %>% 
  mutate(Q18k_center = Q18k - mean(Q18k),
         Q28_tech_norm_center = Q28_tech_norm - mean(Q28_tech_norm),
         Q20d_center = Q20d - mean(Q20d),
         Q26b_center = Q20a - mean(Q26b),
         Q28_social_norm_center = Q28_social_norm - mean(Q28_social_norm),
         Q26h_center = Q26h - mean(Q26h),
         Q19h_center = Q19h - mean(Q19h),
         Q20b_center = Q20b - mean(Q20b))

# climate_df %>% select(Q18k, Q18k_center)

```





## Need to reorder items
```{r}
# Do not do this! Probably does not make sense to make Q28_tech and Q28_social ordinal variables

# train_df$Q28_social_norm_center <- as.ordered(train_df$Q28_social_norm_center)
# climate_df <- climate_df %>% mutate(Q28_tech_norm_ord = as.ordered(Q28_tech_norm),
                    # Q28_social_norm_ord = as.ordered(Q28_social_norm))

# climate_df %>% select(Q28_social_norm, Q28_social_norm_center, Q28_social_norm_ord)

```


# Recode ordinal predictors as ordinal
Q28_tech_norm * don't recode
Q20d -- strongly disagree to strongly agree
Q28_social_norm * don't recode
Q20b -- strongly disagree to strongly agree
Q26b -- strongly disagree to strongly agree
Q19h -- strongly disagree to strongly agree
Q26h -- strongly disagree to strongly agree
Q18k -- strongly disagree to strongly agree

```{r}

climate_df %>% count(Q14a)

climate_df <- climate_df %>% 
  mutate(Q20d_ord = case_when(Q20d == 0 ~ "Strongly disagree",
                              Q20d == 1 ~ "Disagree",
                              Q20d == 2 ~ "Neutral",
                              Q20d == 3 ~ "Agree",
                              Q20d == 4 ~ "Strongly agree"),
         Q26b_ord = case_when(Q26b == 0 ~ "Strongly disagree",
                              Q26b == 1 ~ "Disagree",
                              Q26b == 2 ~ "Neutral",
                              Q26b == 3 ~ "Agree",
                              Q26b == 4 ~ "Strongly agree"),
         Q26h_ord = case_when(Q26h == 0 ~ "Strongly disagree",
                              Q26h == 1 ~ "Disagree",
                              Q26h == 2 ~ "Neutral",
                              Q26h == 3 ~ "Agree",
                              Q26h == 4 ~ "Strongly agree"),
         Q19h_ord = case_when(Q19h == 0 ~ "Strongly disagree",
                              Q19h == 1 ~ "Disagree",
                              Q19h == 2 ~ "Neutral",
                              Q19h == 3 ~ "Agree",
                              Q19h == 4 ~ "Strongly agree"),
         Q20b_ord = case_when(Q20b == 0 ~ "Strongly disagree",
                              Q20b == 1 ~ "Disagree",
                              Q20b == 2 ~ "Neutral",
                              Q20b == 3 ~ "Agree",
                              Q20b == 4 ~ "Strongly agree"),
         Q18k_ord = case_when(Q18k == 0 ~ "Strongly disagree",
                              Q18k == 1 ~ "Disagree",
                              Q18k == 2 ~ "Neutral",
                              Q18k == 3 ~ "Agree",
                              Q18k == 4 ~ "Strongly agree"))


```




```{r}

climate_df %>% count(Q20d)
climate_df %>% count(Q20d_ord)

```



```{r}
str(climate_df$Q20d_ord)
rf_ord_vars <- c("Q20d_ord", "Q26b_ord", "Q26h_ord", "Q19h_ord", "Q20b_ord", "Q18k_ord")
rf_ord_levels <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")



climate_df <- climate_df %>% 
  mutate_at(rf_ord_vars, ~factor(., ordered = TRUE, levels = rf_ord_levels)) 


```

```{r}

climate_df %>% count(Q20d)
climate_df %>% count(Q20d_ord)

```










## Start creating models


### Model 1: Ordinal outcome with continuous predictors

```{r}
# no priors
mod1_ord_cl_tri_inf <- brm(formula = ordered(cluster_time_rank) ~ Q28_tech_norm + Q20d + Q26b + Q28_social_norm + Q26h + Q19h + Q20b + Q18k,
                     data = climate_df,
                     family = cumulative("logit"),
                     cores = parallel::detectCores())




```


```{r}


file_name <- "mod1_ord_rf_cl_tri_inf.rds"

mod1_ord_cl_tri_inf %>% write_rds(file = file_name)

```




```{r}
# no priors
mod1_lin_rf_cl_tri_inf <- brm(formula = cluster_time_rank ~ Q28_tech_norm + Q20d + Q26b + Q28_social_norm + Q26h + Q19h + Q20b + Q18k,
                     data = climate_df,
                     family = gaussian(),
                     cores = parallel::detectCores())




```


```{r}


file_name <- "mod1_lin_rf_cl_tri_inf.rds"

mod1_lin_rf_cl_tri_inf %>% write_rds(file = file_name)

```


```{r}

#centered variables
mod1_lin_center_cl_tri_inf <- brm(formula = cluster_time_rank ~ Q28_tech_norm_center + Q20d_center + 
                            Q26b_center + Q28_social_norm_center + Q26h_center + 
                            Q19h_center + Q20b_center + Q18k_center,
                     data = climate_df,
                     family = gaussian(),
                     cores = parallel::detectCores())



```






```{r}


file_name <- "mod1_lin_cent_rf_cl_tri_inf.rds"

mod1_lin_center_cl_tri_inf %>% write_rds(file = file_name)

```

```{r}

mod1_lin_cl_tri_inf <- read_rds(file = file_name)

```

```{r}
tab_model(mod1_lin_center_cl_tri_inf)
```


```{r}

summary(mod1_lin_cl_tri_inf)

# coef(mod1_ord_Q16c)
# fixef(mod1_lin_cl)

```

```{r}
get_variables(mod1_lin_cl_tri_inf)
```


```{r}
stanplot(mod1_lin_cl_tri_inf, pars = c("^r_", "^b_", "^sd_")) +
  theme_light() +
  theme(axis.text.y = element_text(hjust = 0))
```


```{r}

# broken
mod1_lin_cl_tri_inf %>%
  spread_draws(`b_.*`, regex = TRUE) %>%
  ggplot(aes(y = factor(i), x = b_Intercept)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Intercept Estimates for Orginal Regression with Environmental Topics",
       x = "Parameter Estimate",
       y = "Cluster cutoff point") +
  theme(plot.title = element_text(hjust=0.5))

```


```{r}

param_plot <- mod1_lin_center_cl_tri_inf %>%
  spread_draws(`b_.*`, regex = TRUE) %>%
  pivot_longer(cols = b_Intercept:b_Q18k_center, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Intercept Estimates for Linear Regression with Spatiotemporal Beliefs Patterns",
       x = "Parameter Estimate",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot

```




```{r}

mod1_lin_center_cl_tri_inf %>%
  spread_draws(r_major[major,i]) %>%
  ggplot(aes(y = factor(major), x = r_major)) +
  stat_halfeye(.width = c(.9, .5)) +
  facet_grid(major ~ i, scales = "free") +
  labs(title = "Intercept Estimates for Ordinal Regression with Environmental Topics",
       x = "Parameter Estimate",
       y = "Cluster cutoff point") +
  theme(plot.title = element_text(hjust=0.5))


```





### Model 2: Linear outcome with monotonic effects of categorical predictors

```{r}

mod2_lin_mono_cl_tri_inf <- brm(formula = cluster_time_rank ~ Q28_tech_norm + mo(Q20d_ord) + 
                            mo(Q26b_ord) + Q28_social_norm + mo(Q26h_ord) + 
                            mo(Q19h_ord) + mo(Q20b_ord) + mo(Q18k_ord),
                     data = climate_df,
                     family = gaussian(),
                     cores = parallel::detectCores())

```




```{r}


file_name <- "mod2_lin_mono_rf_cl_tri_inf.rds"

mod2_lin_mono_cl_tri_inf %>% write_rds(file = file_name)

```


```{r}

mod2_lin_mono_cl_tri_inf <- read_rds(file = file_name)

```

```{r}

get_variables(mod2_lin_mono_cl_tri_inf)

```



```{r}

mod2_lin_mono_cl_tri_inf %>% 
  spread_draws(`b.*`, regex = TRUE)

```




```{r}

plot(conditional_effects(mod2_lin_mono_cl_tri_inf))



```



```{r}

mod2_param_plot <- mod2_lin_mono_cl_tri_inf %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q28_tech_norm = b_Q28_tech_norm,
         Q28_social_norm = b_Q28_social_norm,
         Q26h = bsp_moQ26h_ord,
         Q20d = bsp_moQ20d_ord,
         Q26b = bsp_moQ26b_ord,
         Q20b = bsp_moQ20b_ord,
         Q19h = bsp_moQ19h_ord,
         Q18k = bsp_moQ18k_ord) %>% 
  pivot_longer(cols = Q28_tech_norm:Q18k, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Linear Regression with Spatiotemporal Beliefs Patterns",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

mod2_param_plot

```


```{r}

ggsave(filename = paste0("fig_q27_rf_cl_mod2_param_plot_", Sys.Date(),".png"),
       plot = mod2_param_plot,
       dpi = 450,
       width = 8,
       height = 6)

```





```{r}

mod3_ord_mono_rf_cl_tri_inf <- brm(formula = ordered(cluster_time_rank) ~ Q28_tech_norm + mo(Q20d_ord) + 
                            mo(Q26b_ord) + Q28_social_norm + mo(Q26h_ord) + 
                            mo(Q19h_ord) + mo(Q20b_ord) + mo(Q18k_ord),
                     data = climate_df,
                     family = cumulative("logit"),
                     cores = parallel::detectCores())

```




```{r}


file_name <- "mod3_ord_mono_rf_cl_tri_inf.rds"

mod3_ord_mono_rf_cl_tri_inf %>% write_rds(file = file_name)

```


```{r}


param_plot <- mod3_ord_mono_rf_cl_tri_inf %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(Q28_tech_norm = b_Q28_tech_norm,
         Q28_social_norm = b_Q28_social_norm,
         Q26h = bsp_moQ26h_ord,
         Q20d = bsp_moQ20d_ord,
         Q20b = bsp_moQ20b_ord,
         Q26b = bsp_moQ26b_ord,
         Q19h = bsp_moQ19h_ord,
         Q18k = bsp_moQ18k_ord) %>% 
  pivot_longer(cols = Q28_tech_norm:Q18k, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Spatiotemporal Beliefs Patterns",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot


```


```{r}


ggsave(filename = paste0("fig_q27_rf_cl_mod3_param_plot", Sys.Date(),".png"),
       plot = param_plot,
       dpi = 450,
       width = 8,
       height = 6)


```




