---
title: "Class clustering"
author: "Katz et al."
date: "4/26/2021"
output: html_document
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}

library(RColorBrewer)
library(tidyverse)
library(dbscan)
library(umap)
library(psych)
library(gmodels)
library(graphics)
library(knitr)
library(purrr)
library(tidytext)
library(ggmosaic)
library(brms)
library(lme4)
library(parallel)
library(ggridges)
library(tidybayes)
library(ggridges)

library(ggmcmc)
library(maps)
library(ggmap)

library(mice)

library(uwot)

library(rstatix)

set.seed(123)

```




```{r}

#climate_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/updated_climate_df_2.csv")
data_folder <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/data/"
data_file <- "updated_climate_df_2.csv"

climate_df <- read_csv(paste0(data_folder, data_file))


## Drop duplicates
climate_df <- climate_df %>% distinct(Litho, .keep_all = TRUE)
# check for possible duplicates
#climate_df %>% group_by(Litho) %>% filter(n() > 1) %>% arrange(Litho) %>% ungroup()


## Add in major as string instead of number

climate_df <- climate_df %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))



climate_df <- climate_df %>% 
  rowid_to_column(var = "student_id")

```


```{r}
# create variable vectors

#test_df <- climate_df %>% select(Q7_vars, Q7tally_vars, Q7wt_sum_vars, Q7other_vars, Q7disc_vars,Q7eng_ele_vars, Q7non_eng_vars)

Q1_vars <- paste0("Q1", letters[1:20])
Q2_vars <- paste0("Q2", letters[1:7])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])
Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")
Q7wt_sum_vars <- paste0("Q7", letters[1:22], "_wt_sum")
Q7other_vars <- paste0("Q7", letters[1:22], "_other")
Q7disc_vars <- paste0("Q7", letters[1:22], "_disc_spec")
Q7eng_ele_vars <- paste0("Q7", letters[1:22], "_eng_ele")
Q7non_eng_vars <- paste0("Q7", letters[1:22], "_non_eng_ele")

Q6_vars <- paste0("Q6", letters[1:11])
Q8_vars <- paste0("Q8", letters[1:14])

Q16_vars <- paste0("Q16", letters[1:13])



Q27_vars <- paste0("Q27", letters[1:9])
last_letter <- 9
Q27_tri_num_vars <- paste0("Q27", letters[1:last_letter], "_tri_num")

Q28_vars <- paste0("Q28", letters[1:12])

Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])



```

```{r}
climate_df <- climate_df %>% 
  mutate(Q27a_tri_num = case_when(Q27a == 1 | Q27a == 2 ~ 0,
                                  Q27a == 3 | Q27a == 4 ~1, 
                                  Q27a == 5 ~ 2),
         Q27b_tri_num = case_when(Q27b == 1 | Q27b == 2 ~ 0,
                                  Q27b == 3 | Q27b == 4 ~1,
                                  Q27b == 5 ~ 2),
         Q27c_tri_num = case_when(Q27c == 1 | Q27c == 2 ~ 0,
                                  Q27c == 3 | Q27c == 4 ~ 1,
                                  Q27c == 5 ~ 2),
         Q27d_tri_num = case_when(Q27d == 1 | Q27d == 2 ~ 0,
                                  Q27d == 3 | Q27d == 4 ~ 1,
                                  Q27d == 5 ~ 2),
         Q27e_tri_num = case_when(Q27e == 1 | Q27e == 2 ~ 0,
                                  Q27e == 3 | Q27e == 4 ~ 1,
                                  Q27e == 5 ~ 2),
         Q27f_tri_num = case_when(Q27f == 1 | Q27f == 2 ~ 0,
                                  Q27f == 3 | Q27f == 4 ~ 1,
                                  Q27f == 5 ~ 2),
         Q27g_tri_num = case_when(Q27g == 1 | Q27g == 2 ~ 0,
                                  Q27g == 3 | Q27g == 4 ~ 1,
                                  Q27g == 5 ~ 2),
         Q27h_tri_num = case_when(Q27h == 1 | Q27h == 2 ~ 0,
                                  Q27h == 3 | Q27h == 4 ~ 1,
                                  Q27h == 5 ~ 2),
         Q27i_tri_num = case_when(Q27i == 1 | Q27i == 2 ~ 0,
                                  Q27i == 3 | Q27i == 4 ~ 1,
                                  Q27i == 5 ~ 2))


```



## Clustering based on Q7

```{r}
# create clustering matrix

course_cl_t_df <- climate_df %>% 
  filter(!is.na(Q40)) %>% 
  select(student_id, Q7tally_vars)

q27_df <- climate_df %>% 
  select(student_id, Q27_tri_num_vars)

```





```{r}
# attempt using umap from uwot instead of from umap package

umap_min_dist <- 1
umap_spread <- 1
umap_n_comp <- 2
umap_n_nei <- 5
u_metric <- "euclidean"

uwot_umap <- function(df, umap_min_dist, umap_spread, umap_n_comp, umap_n_nei, metric) {
  df %>% 
    select(Q7a_tally:Q7v_tally) %>%
    uwot::umap(min_dist = umap_min_dist, 
               spread = umap_spread, 
               n_components = umap_n_comp,
               n_neighbors = umap_n_nei,
               metric = metric) %>% 
    as_data_frame()
}

uwot_umap_ab <- uwot_umap <- function(df, a, b) {
  df %>% 
    select(-student_id) %>%
    uwot::umap(a = a, b = b) %>% 
    as_data_frame()
}


uwot_plot <- function(df, min_dist = "", spread = "", n_nei = "", metric = ""){
  p <- df %>% 
    ggplot(aes(x = V1, y = V2)) +
    geom_point() +
    labs(title = paste0("min_dist=", min_dist, 
                        ", spread=", spread, ", n_nei=", n_nei, ", metric=", metric)) +
    theme(strip.text.x = element_text(size = 7)) +
    theme_light()
  
  return(p)
}

uwot_plot_ab <- function(df, a = "", b = ""){
  p <- df %>% 
    ggplot(aes(x = V1, y = V2)) +
    geom_point() +
    labs(title = paste0("a = ", a, 
                        ", b = ", b)) +
    theme(strip.text.x = element_text(size = 7)) +
    theme_light()
  
  return(p)
}
```






```{r}

# final umap selection
# optimal params: 
# n_comp <- 2
# min_dist <- 0.05
# u_spread <- 1
# n_nei <- 5
# metric <- "euclidean"




n_comp <- 2
min_dist <- 0.00005
u_spread <- 1
n_nei <- 5
metric <- "cosine"

uwot_res <- uwot_umap(course_cl_t_df, umap_min_dist = min_dist, umap_spread = u_spread, umap_n_comp = n_comp, umap_n_nei = n_nei, metric = metric)


uwot_plot(uwot_res, min_dist = min_dist, spread = u_spread, n_nei = n_nei, metric = metric)

```



```{r}
# attempt with a, b parameter

a <- 1
b <- seq(from = 0.1, to = 2, by = 0.1)

uwot_res <- uwot_umap_ab(course_cl_t_df, a = a, b =b)


uwot_plot_ab(uwot_res, a = a, b = b)

for (b in b){
  uwot_res <- uwot_umap_ab(course_cl_t_df, a = a, b =b)
  
  
  print(uwot_plot_ab(uwot_res, a = a, b = b))
  
}


```



```{r}


a <- 1
b <- 0.6

uwot_res <- uwot_umap_ab(course_cl_t_df, a = a, b = b)


uwot_plot_ab(uwot_res, a = a, b = b)



```



```{r}
#cluster umap from uwot implementation

hdbscan_umap_cl <- hdbscan(uwot_res, minPts = 120) 


hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
uwot_res$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
uwot_res %>% 
  ggplot(aes(x = V1, y = V2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of STEPS ratings using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))




```



```{r}

# cluster compositions from uwot + hdbscan implementation

# add the cluster labels back to the original data set
course_cl_t_df$cluster <- hdbscan_umap_cl$cluster

course_cl_t_df <- course_cl_t_df %>% inner_join(climate_df %>% select(student_id, Q29), by = "student_id")


course_cl_t_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for STEPS ratings") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



course_cl_t_df %>% 
  filter(cluster != 0) %>% 
  filter(!is.na(Q29)) %>% 
  pivot_longer(cols = Q7a_tally:Q7v_tally, names_to = "course_tally", values_to = "course_amount") %>% 
  ggplot(aes(x = course_amount, fill = as_factor(Q29))) +
  geom_histogram() +
  facet_grid(course_tally ~ cluster) +
  labs(x = "Item Rating (0 = Low, 3 = High)",
       title = "Histogram of Course Topic Tallies by Cluster") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_light()


```





# Course weights instead of tallies



```{r}
course_cl_ws_df <- climate_df %>% 
  filter(!is.na(Q40)) %>% 
  select(student_id, Q7a_wt_sum:Q7v_wt_sum)


```





```{r}

# final umap selection
# optimal params: 
# n_comp <- 2
# min_dist <- 0.05
# u_spread <- 1
# n_nei <- 5
# metric <- "euclidean"




n_comp <- 2
min_dist <- 0.05
u_spread <- 1
n_nei <- 5
metric <- "euclidean"

uwot_res <- uwot_umap(course_cl_ws_df, umap_min_dist = min_dist, umap_spread = u_spread, umap_n_comp = n_comp, umap_n_nei = n_nei, metric = metric)


uwot_plot(uwot_res, min_dist = min_dist, spread = u_spread, n_nei = n_nei, metric = metric)

```



```{r}
# attempt with a, b parameter

a <- 1
b <- seq(from = 0.1, to = 1, by = 0.05)

uwot_res <- uwot_umap_ab(course_cl_ws_df, a = a, b =b)


uwot_plot_ab(uwot_res, a = a, b = b)



for (b in b){
  uwot_res <- uwot_umap_ab(course_cl_ws_df, a = a, b =b)
  
  
  print(uwot_plot_ab(uwot_res, a = a, b = b))
  
}


```

```{r}

# attempt with a, b parameter

a <- seq(from = 0.1, to = 2, by = 0.1)
b <- 1

uwot_res <- uwot_umap_ab(course_cl_ws_df, a = a, b =b)


uwot_plot_ab(uwot_res, a = a, b = b)



for (a in a){
  uwot_res <- uwot_umap_ab(course_cl_ws_df, a = a, b =b)
  
  
  print(uwot_plot_ab(uwot_res, a = a, b = b))
  
}

```







```{r}


a <- 1
b <- 0.45

uwot_res <- uwot_umap_ab(course_cl_ws_df, a = a, b =b)


uwot_plot_ab(uwot_res, a = a, b = b)



```



```{r}
#cluster umap from uwot implementation

hdbscan_umap_cl <- hdbscan(uwot_res, minPts = 80) 


hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
uwot_res$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
uwot_res %>% 
  ggplot(aes(x = V1, y = V2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of STEPS ratings using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))




```



```{r}

# cluster compositions from uwot + hdbscan implementation

# add the cluster labels back to the original data set
course_cl_ws_df$cluster <- hdbscan_umap_cl$cluster

course_cl_ws_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for STEPS ratings") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



course_cl_ws_df %>% 
  filter(cluster != 0) %>% 
  pivot_longer(cols = Q7a_wt_sum:Q7v_wt_sum, names_to = "course_tally", values_to = "course_amount") %>% 
  ggplot(aes(x = course_amount)) +
  geom_histogram() +
  facet_grid(course_tally ~ cluster) +
  labs(x = "Item Rating (0 = Low, 3 = High)",
       title = "Histogram of Course Topic Tallies by Cluster") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_light()


```

















```{r}

# original hdbscan implementation

hdbscan_umap_cl <- hdbscan(plot_df, minPts = 10) 
# groups stay pretty similar from minPts 70 up to 150, when it drops from 9 to 6 clusters

hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
plot_df$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of STEPS ratings using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))


# add the cluster labels back to the original data set
sys_think_df$cluster <- hdbscan_umap_cl$cluster

sys_think_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for STEPS ratings") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))



```








## Q 27 Clustering with a and b parameters instead of min_dist, n_nei

```{r}

data_folder <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change/analysis/q27 clustering/"
data_file <- "climate_imputed_2021-04-22.csv"

climate_imp_long <- read_csv(paste0(data_folder, data_file))

```



```{r}

climate_imp_long <- climate_imp_long %>% 
  mutate(Q27a_tri_num = case_when(Q27a == 1 | Q27a == 2 ~ 0,
                                  Q27a == 3 | Q27a == 4 ~1, 
                                  Q27a == 5 ~ 2),
         Q27b_tri_num = case_when(Q27b == 1 | Q27b == 2 ~ 0,
                                  Q27b == 3 | Q27b == 4 ~1,
                                  Q27b == 5 ~ 2),
         Q27c_tri_num = case_when(Q27c == 1 | Q27c == 2 ~ 0,
                                  Q27c == 3 | Q27c == 4 ~ 1,
                                  Q27c == 5 ~ 2),
         Q27d_tri_num = case_when(Q27d == 1 | Q27d == 2 ~ 0,
                                  Q27d == 3 | Q27d == 4 ~ 1,
                                  Q27d == 5 ~ 2),
         Q27e_tri_num = case_when(Q27e == 1 | Q27e == 2 ~ 0,
                                  Q27e == 3 | Q27e == 4 ~ 1,
                                  Q27e == 5 ~ 2),
         Q27f_tri_num = case_when(Q27f == 1 | Q27f == 2 ~ 0,
                                  Q27f == 3 | Q27f == 4 ~ 1,
                                  Q27f == 5 ~ 2),
         Q27g_tri_num = case_when(Q27g == 1 | Q27g == 2 ~ 0,
                                  Q27g == 3 | Q27g == 4 ~ 1,
                                  Q27g == 5 ~ 2),
         Q27h_tri_num = case_when(Q27h == 1 | Q27h == 2 ~ 0,
                                  Q27h == 3 | Q27h == 4 ~ 1,
                                  Q27h == 5 ~ 2),
         Q27i_tri_num = case_when(Q27i == 1 | Q27i == 2 ~ 0,
                                  Q27i == 3 | Q27i == 4 ~ 1,
                                  Q27i == 5 ~ 2))


climate_imp_4 <- climate_imp_long %>% 
  filter(.imp == 5)

```


```{r}
q27_df <- climate_imp_4 %>% 
  select(student_id, Q27_tri_num_vars)
```


```{r}
a <- 0.5
b <- 1
uwot_res <- uwot_umap_ab(q27_df, a = a, b = b)

```

```{r}
uwot_plot_ab(uwot_res, a = a, b = b)
```







```{r}
#cluster umap from uwot implementation

hdbscan_umap_cl <- hdbscan(uwot_res, minPts = 80) 


hdbscan_umap_cl


# add the cluster labels to the plotting dataframe
uwot_res$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
uwot_res %>% 
  ggplot(aes(x = V1, y = V2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of STEPS ratings using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 8))
```







```{r}
q27_item_list <- list(
  'Q27a_tri_num' = "Me personally",
  "Q27b_tri_num" = "My family",
  "Q27c_tri_num" = "People in my comm.",
  "Q27d_tri_num" = "People in US",
  "Q27e_tri_num" = "Other indust. countr.",
  "Q27f_tri_num" = "Developing countries",
  "Q27g_tri_num" = "Plant + animal species",
  "Q27h_tri_num" = "World's poor",
  "Q27i_tri_num" = "Natural environment"
)

q27_labs <- c("Me personally", 
              "My family",
              "People in my comm.",
              "People in US",
              "Other indust. countr.",
              "Developing countries",
              "Plant + animal species",
              "World's poor",
              "Natural environment")

names(q27_labs) <- c("Q27a_tri_num",
                     "Q27b_tri_num",
                     "Q27c_tri_num",
                     "Q27d_tri_num",
                     "Q27e_tri_num",
                     "Q27f_tri_num",
                     "Q27g_tri_num",
                     "Q27h_tri_num",
                     "Q27i_tri_num")
```



# Understanding cluster compositions more


#### First create a dataframe with the rankings for each cluster, where a lower ranking means students in the cluster think climate change will affect more categories sooner. 



```{r}

## create dataframe with rankings for cluster by how soon each cluster believes climate change will affect groups

# [OLD]
# cluster_ranking_df <- climate_df %>% 
#   mutate(Q27_tri_total = Q27a_tri_num + Q27b_tri_num + Q27c_tri_num + Q27d_tri_num + Q27e_tri_num +
#            Q27f_tri_num + Q27g_tri_num + Q27h_tri_num + Q27i_tri_num) %>% 
#   group_by(cluster) %>% 
#   summarize(cluster_avg = mean(Q27_tri_total)) %>% 
#   arrange(cluster_avg) %>% 
#   rowid_to_column(var = "cluster_time_rank")

#climate_27_tri_df %>% inner_join(cluster_ranking_df, by = "cluster")

q27_df$cluster <- uwot_res$cluster

cluster_ranking_df <- q27_df %>% 
  mutate(Q27_tri_total = Q27a_tri_num +
           Q27b_tri_num + Q27c_tri_num +
           Q27d_tri_num + Q27e_tri_num +
           Q27f_tri_num + Q27g_tri_num +
           Q27h_tri_num + Q27i_tri_num) %>% 
  group_by(cluster) %>% 
  summarize(cluster_avg = mean(Q27_tri_total)) %>% 
  arrange(cluster_avg) %>% 
  rowid_to_column(var = "cluster_time_rank")

# spot check -- passed
#nested_imp$cluster_ranking_df[[1]]


q27_df <- q27_df %>% inner_join(cluster_ranking_df, by = "cluster")

# spot check for whether distributions looks reasonable (e.g., most students believe everything affected now) -- check passed
#nested_imp$data[[5]] %>% count(cluster_time_rank) %>% summarize(n = sum(n))


q27_df %>% count(cluster_time_rank)
```


Set clustering colors for all plots
```{r}

cluster_num = length(unique(q27_df$cluster_time_rank))


# spot check: make sure five values stores -- passed
#test_df$cluster_num

cluster_colors = colorRampPalette(c("#000000", "#a8adb5", "#dedede"))(cluster_num)

# spot check: make sure colors stored -- passed
#test_df$cluster_colors[[5]]



# [OLD]
# new method of assigning cluster colors along a gradient
#cluster_num <- length(unique(climate_df$cluster_time_rank))

# cluster colors with red, yellow, green
#cluster_colors <- colorRampPalette(c("#ec3434", "#f7c035", "#007030"))(cluster_num)

# cluster colors with grayscale
#cluster_colors <- colorRampPalette(c("#000000", "#a8adb5", "#dedede"))(cluster_num)


```



### Look at distribution of cluster for how when they think each community may be affected by global warming

Same information but faceted with clusters

** This is a good plot for seeing that a cluster's beliefs about effects of global warming on different populations at different times vary in a clear pattern
```{r}


q27_df %>% 
  pivot_longer(cols = Q27a_tri_num:Q27i_tri_num, names_to = "survey_item", values_to = "response") %>%
  mutate(cluster_time_rank = as_factor(cluster_time_rank)) %>% 
  ggplot(aes(x = survey_item)) +
  geom_bar(aes(fill = as_factor(response))) +
  facet_wrap(.~ cluster_time_rank,
             scales = "free",
             labeller = labeller(survey_item = q27_labs)) +
  theme_bw() +
  labs(x = "When will global warming affect this population?",
       y = "Count",
       title = "Cluster patterns of when will global warming affect various populations",
       fill = "Response") +
  theme(plot.title = element_text(hjust = 0.5, size = 8)) +
  scale_fill_manual(values = c("#000000", "#a8adb5", "#dedede"), 
                    name = "Response",
                    labels = c("0" = "0-10 yrs", "1" = "25-50y yrs", "2" = "Never")) +
  scale_x_discrete(labels = c('Q27a_tri_num' = "Me personally", "Q27b_tri_num" = "My family", "Q27c_tri_num" = "People in my comm.", "Q27d_tri_num" = "People in US", "Q27e_tri_num" = "Other indust. countr.", "Q27f_tri_num" = "Developing countries", "Q27g_tri_num" = "Plant + animal species", "Q27h_tri_num" = "World's poor", "Q27i_tri_num" = "Natural environment")) + 
  coord_flip()

```















