---
title: "Kase Analysis"
author: "Katz et al."
date: "7/7/2021"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(psych)
library(tidyverse)
library(tidymodels)
library(ranger)
library(purrrlyr)
library(purrr)
library(randomForest)
library(pander)
library(kableExtra)
library(knitr)

library(mice)

library(brms)
library(tidybayes)
library(sjPlot)

library(MASS)
library(Hmisc)

```


Import data

```{r}
data_folder <- "G:/My Drive/AK Faculty/Service/Graduate student committees/Kase Poling/"
data_file <- "duplicates_removed.csv"

df <- read_csv(paste0(data_folder, data_file))

```

```{r}
df <- df %>% 
  rename(value_at_risk = `Value at Risk`)
```


## Data exploration

```{r}
df %>% 
  count(value_at_risk)


df %>% 
  ggplot(aes(x = value_at_risk)) +
  geom_histogram()

```



I want to use ‘Value at Risk’, ‘frequency’, and ‘datevalue’ as the inputs and ‘Q20b’ as one dependent variable and in another model ‘Q27c_group’ as the dependent variable

Create model 1

```{r}
mod_formula <- "ordered(Q20b) ~ value_at_risk + frequency + datevalue"

# don't use this because the variables are so messed up

# mod1 <- brm(formula = mod_formula,
#             family = cumulative("logit"),
#             data = df,
#             cores = parallel::detectCores())

```


```{r}

# data_folder <- "G:/My Drive/AK Faculty/Service/Graduate student committees/Kase Poling/"
# file_name <- "kase_mod1.rds"

# mod1 %>% write_rds(file = paste0(data_folder, file_name))


```



```{r}

# summary(mod1)

```

Re-try model by standardizing predictors

```{r}
max(df$value_at_risk)
var_mean <- mean(df$value_at_risk)
var_sd <- sd(df$value_at_risk)

date_mean <- mean(df$datevalue)
date_sd <- sd(df$datevalue)

freq_mean <- mean(df$frequency)
freq_sd <- sd(df$frequency)


df <- df %>% 
  mutate(var_norm = (value_at_risk - var_mean)/var_sd,
         date_norm = (datevalue - date_mean)/date_sd,
         freq_norm = (frequency - freq_mean)/freq_sd)

df %>% 
  ggplot(aes(x= freq_norm)) +
  geom_histogram(color = "white")

```



#### Data exploration
```{r}
df %>% 
  ggplot(aes(x = var_norm)) +
  geom_histogram(color = "white")


```

Too many var_norm values at 0

```{r}

df %>% 
  filter(var_norm > 0) %>% 
  count(Q27c_group)
# there are only 69 students with var_norm above 0
```


```{r}
df %>% 
  filter(var_norm > 0) %>% 
  ggplot(aes(x = var_norm)) +
  geom_histogram(color = "white")


```





```{r}

df %>% 
  dplyr::select(Q27c_group, freq_norm, var_norm, date_norm) %>% 
  pivot_longer(cols = freq_norm:date_norm, names_to = "variable_name", values_to = "variable_value") %>% 
  ggplot(aes(x = variable_value)) +
  geom_histogram(color = "white") +
  facet_grid(Q27c_group ~ variable_name, scales = "free")

```







```{r}

mod1_norm <- brm(ordered(Q20b) ~ var_norm + date_norm + freq_norm,
                 data = df,
                 family = cumulative("logit"),
                 cores = parallel::detectCores())

```


```{r}

summary(mod1_norm)

```



```{r}



param_plot_mod1 <- mod1_norm %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(var_norm = b_var_norm,
         datevalue_norm = b_date_norm,
         frequency_norm = b_freq_norm) %>% 
  pivot_longer(cols = var_norm:frequency_norm, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), 
             x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Standardized Predictors for Q20b",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot_mod1

```


```{r}
ggsave(filename = paste0("fig_q20b_param_plot_", Sys.Date(),".png"),
       plot = param_plot_mod1,
       dpi = 450,
       width = 8,
       height = 6)
```





```{r}

df %>% 
  ggplot(aes(x = Q27c_group)) +
  geom_histogram(color = "white")

```


Create model 2

```{r}

mod2_norm <- brm(ordered(Q27c_group) ~ var_norm + date_norm + freq_norm,
                 data = df,
                 family = cumulative("logit"),
                 cores = parallel::detectCores())

```



```{r}

summary(mod2_norm)

```


```{r}


param_plot_mod2 <- mod2_norm %>%
  spread_draws(`b.*`, regex = TRUE) %>% 
  rename(var_norm = b_var_norm,
         datevalue_norm = b_date_norm,
         frequency_norm = b_freq_norm) %>% 
  pivot_longer(cols = var_norm:frequency_norm, names_to = "parameter", values_to = "parameter_estimate") %>% 
  ggplot(aes(y = factor(parameter), 
             x = parameter_estimate)) +
  stat_halfeye(.width = c(.9, .5)) +
  labs(title = "Parameter Estimates for Ordinal Regression with Standardized Predictors for Q27c_group",
       x = "Estimated Value of Parameter Probability Density",
       y = "Survey Item") +
  theme_light() +
  theme(plot.title = element_text(hjust=0.5, size = 10)) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")

param_plot_mod2

```



```{r}


ggsave(filename = paste0("fig_q27c_param_plot_", Sys.Date(),".png"),
       plot = param_plot_mod2,
       dpi = 450,
       width = 8,
       height = 6)

```





#### Model using polr from MASS package

https://stats.idre.ucla.edu/r/dae/ordinal-logistic-regression/

```{r}

df <- df %>% 
  mutate(Q27c_group = as_factor(Q27c_group))

mod2_polr <- polr(Q27c_group ~ var_norm + date_norm + freq_norm,
                  data = df, Hess = TRUE)

```


```{r}
summary(mod2_polr)
```


```{r}

(ctable <- coef(summary(mod2_polr)))

```

```{r}

## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = p))

```

```{r}


(ci <- confint(mod2_polr)) # default method gives profiled CIs
```

```{r}

## odds ratios
exp(coef(mod2_polr))

```

```{r}

exp(cbind(OR = coef(mod2_polr), ci))

```



Test proportional odds assumption

```{r}
df %>% 
  count(Q27c_group)

```


```{r}
df %>% 
  count(Q20b)

```


```{r}
sf <- function(y) {
  c('Y>=0' = qlogis(mean(y >= 0)),
    'Y>=1' = qlogis(mean(y >= 1)),
    'Y>=2' = qlogis(mean(y >= 2)))
}
```


```{r}

(s <- with(df, summary(as.numeric(Q27c_group) ~ var_norm + freq_norm + date_norm, fun=sf)))


```

```{r}

glm(I(as.numeric(Q27c_group) >= 1) ~ var_norm, family="binomial", data = df)

```











