---
title: "ASEE 2020 - Civil engineering students and impacts of climate change"
author: "Shealy and Katz"
date: "1/22/2020"
output: word_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(broom)
library(knitr)
library(randomForest)
library(purrr)
library(purrrlyr)
library(RColorBrewer)
library(gmodels)
library(umap)
library(dbscan)

library(sjPlot)
library(sjlabelled)
library(sjmisc)

knitr::opts_chunk$set(echo = TRUE)


```

## Analysis for 2020 ASEE paper on civil engineering student beliefs about the geographical impacts across time 


```{r data processing, echo=FALSE, message=FALSE}

project_path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change"
setwd(project_path)

climate_data <- read_csv("updated_climate_df_5.csv")

table(climate_data$Q29)

Q1_vars <- paste0("Q1", letters[1:20])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])
Q16_vars <- paste0("Q16", letters[1:13])
Q27_vars <- paste0("Q27", letters[1:9])
Q28_vars <- paste0("Q28", letters[1:12])
Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])

Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")


# create a new dataframe for doing all the calculations
#rf_df <- climate_data

# rf_df <- rf_df %>% mutate_at(vars(Q1_vars), ~replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q3_vars), ~ replace_na(.,0))
# 
# #rf_df <- rf_df %>% mutate_at(vars(Q5_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q7_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q35_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q39_vars), ~ replace_na(., 0))
# 
# 
# rf_df <- rf_df %>% drop_na(Q28_vars)
# 
# rf_df <- rf_df %>% drop_na(Q16_vars)


#data read-in 
#climate_df <- read_csv("filtered_climate_survey_20200122.csv")

#climate_df <- climate_df %>% drop_na(Q28_vars)
#climate_df <- climate_df %>% drop_na(Q27_vars) #should have 
dim(climate_data)


```


#### Summary statistics


Frequency tables for Question 28


```{r echo=FALSE, message=FALSE}


 # climate_df %>% 
 #   filter(Q29 == 4) %>% 
 #   select(Q28_vars) %>% 
 #   gather(key = "item", value = "response") %>% 
 #   group_by(item, response) %>% 
 #   tally() %>% 
 #   spread(response, n) %>% 
 #  mutate(total = )

count_df <- climate_df %>% 
   filter(Q29 == 4) %>% 
   select(Q28_vars) %>% 
   gather(key = "item", value = "response") %>% 
   group_by(item) %>% 
   tally()


q28_df <-  climate_df %>% 
   filter(Q29 == 4) %>% 
   select(Q28_vars) %>% 
   gather(key = "item", value = "response") %>% 
   group_by(item, response) %>% 
   tally() %>% 
   spread(response, n)


q28_df <- inner_join(count_df, q28_df)

q28_df %>% 
  kable()

response_values <- colnames(q28_df)[-(1:2)]

q28_df %>% 
  mutate_at(response_values, funs(./n * 100)) %>% 
  mutate_at(response_values, funs(round(., 1))) %>% 
  kable()
  



```



Summary statistics for Q28 factor


```{r echo=FALSE}

climate_df <- climate_df %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q28_social, Q28_tech, Q28_social_norm, Q28_tech_norm) %>% 
  gather(key = "item", value = "response_values") %>%
  group_by(item) %>% 
  summarize(mean = mean(response_values), sd = sd(response_values), n = n()) %>% 
  kable(digits = 2)

climate_df %>% 
  filter(Q29 == 4) %>% 
  ggplot(aes(x = Q28_tech_norm)) +
  geom_histogram() +
  theme_bw() +
  labs(x = "Global warming is a 'technical' issue normalized score",
       y = "Number of students")

climate_df %>% 
  filter(Q29 == 4) %>% 
  ggplot(aes(x = Q28_social_norm)) +
  geom_histogram() +
  theme_bw() +
  labs(x = "Global warming is a 'social' issue normalized score",
       y = "Number of students") +
  ylim(0, 150)


```



Frequency tables for Question 27


```{r echo=FALSE, message=FALSE}


count_df <- climate_df %>% 
   filter(Q29 == 4) %>% 
   select(Q27_vars) %>% 
   gather(key = "item", value = "response") %>% 
   group_by(item) %>% 
   tally()


q27_df <-  climate_df %>% 
   filter(Q29 == 4) %>% 
   select(Q27_vars) %>% 
   gather(key = "item", value = "response") %>% 
   group_by(item, response) %>% 
   tally() %>% 
   spread(response, n)


q27_df <- inner_join(count_df, q27_df)

q27_df %>% 
  kable()

response_values <- colnames(q27_df)[-(1:2)]

q27_df %>% 
  mutate_at(response_values, funs(./n *100)) %>% 
  mutate_at(response_values, funs(round(., 1))) %>% 
  kable()
  



```




### Chi square tests for Question 27

```{r echo=FALSE, message=FALSE}

test_df <- climate_df %>% 
  filter(Q29 == 4) %>% 
  mutate(Q27a_bin = case_when(Q27a == 1 | Q27a == 2 ~ "Sooner",
                              Q27a == 3 | Q27a == 4 | Q27a == 5 ~ "Later"),
         Q27b_bin = case_when(Q27b == 1 | Q27b == 2 ~ "Sooner",
                              Q27b == 3 | Q27b == 4 | Q27b == 5 ~ "Later"),
         Q27c_bin = case_when(Q27c == 1 | Q27c == 2 ~ "Sooner",
                              Q27c == 3 | Q27c == 4 | Q27c == 5 ~ "Later"),
         Q27d_bin = case_when(Q27d == 1 | Q27d == 2 ~ "Sooner",
                              Q27d == 3 | Q27d == 4 | Q27d == 5 ~ "Later"),
         Q27e_bin = case_when(Q27e == 1 | Q27e == 2 ~ "Sooner",
                              Q27e == 3 | Q27e == 4 | Q27e == 5 ~ "Later"),
         Q27f_bin = case_when(Q27f == 1 | Q27f == 2 ~ "Sooner",
                              Q27f == 3 | Q27f == 4 | Q27f == 5 ~ "Later"),
         Q27g_bin = case_when(Q27g == 1 | Q27g == 2 ~ "Sooner",
                              Q27g == 3 | Q27g == 4 | Q27g == 5 ~ "Later"),
         Q27h_bin = case_when(Q27h == 1 | Q27h == 2 ~ "Sooner",
                              Q27h == 3 | Q27h == 4 | Q27h == 5 ~ "Later"),
         Q27i_bin = case_when(Q27i == 1 | Q27i == 2 ~ "Sooner",
                              Q27i == 3 | Q27i == 4 | Q27i == 5 ~ "Later"))


```

chi-square for Q27 natural environment (27i) vs me personally (27a)

```{r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs me personally (27a)
CrossTable(test_df$Q27a_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27a_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27a_bin, test_df$Q27i_bin)
```

chi-square for Q27 natural environment (27i) vs my family (27b)

```{r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs my family (27b)
CrossTable(test_df$Q27b_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27b_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27b_bin, test_df$Q27i_bin)
```

chi-square for Q27 natural environment (27i) vs people in my community (27c)

``` {r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs people in my community (27c)
CrossTable(test_df$Q27c_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27c_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27c_bin, test_df$Q27i_bin)
```


chi-square for Q27 natural environment (27i) vs people in the United States (27d)

```{r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs people in the United States (27d)
CrossTable(test_df$Q27d_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27d_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27d_bin, test_df$Q27i_bin)


```


chi-square for Q27 natural environment (27i) vs people in other industrialized countries (27e)


``` {r echo= FALSE}

# using chi-square for Q27 natural environment (27i) vs people in other industrialized countries (27e)

CrossTable(test_df$Q27e_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27e_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27e_bin, test_df$Q27i_bin)
```


chi-square for Q27 natural environment (27i) vs people in developing countries (27f)

```{r echo=FALSE}
# using chi-square for Q27 natural environment (27i) vs people in developing countries (27f)
CrossTable(test_df$Q27f_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27f_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27f_bin, test_df$Q27i_bin)

```


chi-square for Q27 natural environment (27i) vs plant and animal species (27g)

```{r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs plant and animal species (27g)
CrossTable(test_df$Q27g_bin, test_df$Q27i_bin, chisq = TRUE)
xtabs(~ Q27g_bin + Q27i_bin, data=test_df)
chisq.test(test_df$Q27g_bin, test_df$Q27i_bin)

```


chi-square for Q27 natural environment (27i) vs the world's poor (27h)
```{r echo= FALSE}
# using chi-square for Q27 natural environment (27i) vs the world's poor (27h)
CrossTable(test_df$Q27h_bin, test_df$Q27i_bin, chisq = TRUE)
kable(xtabs(~ Q27h_bin + Q27i_bin, data=test_df))
chisq.test(test_df$Q27h_bin, test_df$Q27i_bin)



```


### Question 27 clustering


```{r echo=FALSE, message=FALSE}



civil_df <- climate_df %>% 
  filter(Q29 == 4) %>% 
  mutate(Q27a_bin = case_when(Q27a == 1 | Q27a == 2 ~ "Sooner",
                              Q27a == 3 | Q27a == 4 | Q27a == 5 ~ "Later"),
         Q27b_bin = case_when(Q27b == 1 | Q27b == 2 ~ "Sooner",
                              Q27b == 3 | Q27b == 4 | Q27b == 5 ~ "Later"),
         Q27c_bin = case_when(Q27c == 1 | Q27c == 2 ~ "Sooner",
                              Q27c == 3 | Q27c == 4 | Q27c == 5 ~ "Later"),
         Q27d_bin = case_when(Q27d == 1 | Q27d == 2 ~ "Sooner",
                              Q27d == 3 | Q27d == 4 | Q27d == 5 ~ "Later"),
         Q27e_bin = case_when(Q27e == 1 | Q27e == 2 ~ "Sooner",
                              Q27e == 3 | Q27e == 4 | Q27e == 5 ~ "Later"),
         Q27f_bin = case_when(Q27f == 1 | Q27f == 2 ~ "Sooner",
                              Q27f == 3 | Q27f == 4 | Q27f == 5 ~ "Later"),
         Q27g_bin = case_when(Q27g == 1 | Q27g == 2 ~ "Sooner",
                              Q27g == 3 | Q27g == 4 | Q27g == 5 ~ "Later"),
         Q27h_bin = case_when(Q27h == 1 | Q27h == 2 ~ "Sooner",
                              Q27h == 3 | Q27h == 4 | Q27h == 5 ~ "Later"),
         Q27i_bin = case_when(Q27i == 1 | Q27i == 2 ~ "Sooner",
                              Q27i == 3 | Q27i == 4 | Q27i == 5 ~ "Later"))


# making binary variable values rather than character variable values

Q27_bin_num_vars <- paste0("Q27", letters[1:9], "_bin_num")
Q27_bin_num_vars

civil_df <- civil_df %>% 
  mutate(Q27a_bin_num = case_when(Q27a == 1 | Q27a == 2 ~ 0,
                              Q27a == 3 | Q27a == 4 | Q27a == 5 ~ 1),
         Q27b_bin_num = case_when(Q27b == 1 | Q27b == 2 ~ 0,
                              Q27b == 3 | Q27b == 4 | Q27b == 5 ~ 1),
         Q27c_bin_num = case_when(Q27c == 1 | Q27c == 2 ~ 0,
                              Q27c == 3 | Q27c == 4 | Q27c == 5 ~ 1),
         Q27d_bin_num = case_when(Q27d == 1 | Q27d == 2 ~ 0,
                              Q27d == 3 | Q27d == 4 | Q27d == 5 ~ 1),
         Q27e_bin_num = case_when(Q27e == 1 | Q27e == 2 ~ 0,
                              Q27e == 3 | Q27e == 4 | Q27e == 5 ~ 1),
         Q27f_bin_num = case_when(Q27f == 1 | Q27f == 2 ~ 0,
                              Q27f == 3 | Q27f == 4 | Q27f == 5 ~ 1),
         Q27g_bin_num = case_when(Q27g == 1 | Q27g == 2 ~ 0,
                              Q27g == 3 | Q27g == 4 | Q27g == 5 ~ 1),
         Q27h_bin_num = case_when(Q27h == 1 | Q27h == 2 ~ 0,
                              Q27h == 3 | Q27h == 4 | Q27h == 5 ~ 1),
         Q27i_bin_num = case_when(Q27i == 1 | Q27i == 2 ~ 0,
                              Q27i == 3 | Q27i == 4 | Q27i == 5 ~ 1))





civil_27_bin_df <- civil_df %>% 
  select(Q27_bin_num_vars)


#hdbscan without dim reduction

hdbscan_cl <- hdbscan(civil_27_bin_df, minPts = 15)
hdbscan_cl



# hdbscan with dim reduction using UMAP

# Step 1: dim reduction with UMAP from nine dimensions to two dimensions

civil_umap <- umap(civil_27_bin_df)
civil_umap
names(civil_umap$layout)
names(civil_umap$layout) <- c("dim1", "dim2")

head(civil_umap$layout, 3)
head(civil_umap$layout[,1])
head(civil_umap$layout[,2])

# visualize the reduction 
plot(civil_umap$layout[,1], civil_umap$layout[,2])

plot_df <- civil_umap$layout
plot_df <- as_tibble(plot_df)
names(plot_df) <- c("dim1", "dim2")
ggplot(data = plot_df, aes(x = dim1, y = dim2)) +
  geom_point()


# perform clustering using HDBSCAN on the dim-reduced data

hdbscan_umap_cl <- hdbscan(plot_df, minPts = 15)
hdbscan_umap_cl
#hdbscan_umap_cl$cluster

# add the cluster labels to the plotting dataframe
plot_df$cluster <- hdbscan_umap_cl$cluster

# plot the reduction with the clusters
plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of simplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))


# add the cluster labels back to the original data set
civil_27_bin_df$cluster <- hdbscan_umap_cl$cluster

civil_27_bin_df %>% 
  ggplot(aes(x = cluster)) +
  geom_histogram() +
  labs(x = "Cluster",
       y = "Count",
       title = "Histogram of clusters for simplified Question 27") +
  theme_bw()




######
#
# Clustering using unsimplified question 27 (values 1-5) rather than simplified question 27 (binary values - sooner (0) or later (1))
#
######


civil_27_df <- civil_df %>% 
  select(Q27_vars)

# clustering on the unreduced data (pretty noisy)
hdbscan_cl <- hdbscan(civil_27_df, minPts = 15)
hdbscan_cl


# perform dimension reduction and then try clustering

# Step 1: dimension reduction from 9 dimensions to 2 dimensions using umap

civil_umap <- umap(civil_27_df)
civil_umap
#names(civil_umap$layout)
names(civil_umap$layout) <- c("dim1", "dim2")

head(civil_umap$layout, 3)
head(civil_umap$layout[,1])
head(civil_umap$layout[,2])

# visualized the reduction
plot(civil_umap$layout[,1], civil_umap$layout[,2])

plot_df <- civil_umap$layout
plot_df <- as_tibble(plot_df)
names(plot_df) <- c("dim1", "dim2")
ggplot(data = plot_df, aes(x = dim1, y = dim2)) +
  geom_point()


hdbscan_umap_cl <- hdbscan(plot_df, minPts = 30)
hdbscan_umap_cl
#hdbscan_umap_cl$cluster


plot_df$cluster <- hdbscan_umap_cl$cluster

plot_df %>% 
  ggplot(aes(x = dim1, y = dim2, color = as.factor(cluster))) +
  geom_point() +
  labs(x = "UMAP projection dimension 1", 
       y = "UMAP projection dimension 2",
       color = "Cluster",
       title = "Two-dimensional projection of unsimplified Q27 using UMAP") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) 
  


civil_27_df$cluster <- hdbscan_umap_cl$cluster






```





##### Question 27 
Global warming will start to have serious impact on...

(a) me personally
(b) my family
(c) people in my community
(d) people in the United States
(e) people in other modern industrialized countries
(f) people in developing countries
(g) plant and animal species
(h) the world's poor
(i) the natural environment

1 = now, 2 = 10 yrs, 3 = 25 yrs, 4 = 50 yrs, 5 = Never


```{r Q27 summary, echo = FALSE, message = FALSE}

# climate_df %>% 
#   filter(Q29 == 4) %>% 
#   select(Q27_vars) %>% 
#   summarize_all(list(~min(.), 
#                      ~max(.),
#                      ~mean(.), 
#                      ~sd(.), 
#                      ~median(.))) %>% 
#   kable()

stat_vars <- c("n", "mean", "sd", "median", "min", "max")

climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q27_vars) %>% 
  summarize_all(funs(min(.), 
                     max(.),
                     mean(.), 
                     sd(.), 
                     median(.),
                     n(),
                     mode(.))) %>% 
  gather(stat, val) %>% 
  separate(stat, into = c("item", "stat"), sep = "_") %>% 
  spread(stat, val) %>% 
  select(item, n, mean, sd, median, min, max) %>% 
  mutate_at(stat_vars, as.numeric) %>% 
  kable(digits = 2)



```



##### Question 28
I believe that global warming is a(n)...

(a) environmental issue)
(b) moral issue
(c) religious issue
(d) social justice (fairness issue)
(e) political issue
(f) scientific issue
(g) engineering issue
(h) health issue
(i) economic issue
(j) national security issue
(k) agricultural (farming, food) issue
(l) poverty issue

0 = strongly disagree, 1, 2, 3, 4 = strongly agree


```{r Q28 summary, echo=FALSE, message=FALSE, warning = FALSE}


climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q28_vars) %>% 
  summarize_all(funs(min(.), 
                     max(.),
                     mean(.), 
                     sd(.), 
                     median(.),
                     n(),
                     mode(.))) %>% 
  gather(stat, val) %>% 
  separate(stat, into = c("item", "stat"), sep = "_") %>% 
  spread(stat, val) %>% 
  select(item, n, mean, sd, median, min, max) %>% 
  mutate_at(stat_vars, as.numeric) %>% 
  kable(digits = 2)


```

## Plots

### Question 27 histograms

```{r echo=FALSE, warning=FALSE, message=FALSE}

# Question 27 histograms
# climate_df %>% 
#   filter(Q29 == 4) %>% 
#   select(Q27_vars) %>% 
#   gather(key = "item", value = "response", Q27_vars) %>% 
#   ggplot(aes(x = response)) +
#   geom_histogram() + 
#   facet_grid(item ~ .) +
#   ggtitle("Distribution of Question 27 responses for civil engineering") +
#   ylab("Count") +
#   xlab("Item Response") +
#   theme_bw() +
#   theme(plot.title = element_text(size = 10))



Q27_var_names <- c(
  Q27a = "me",
  Q27b = "my family",
  Q27c = "my comm.",
  Q27d = "US people",
  Q27e = "ind. countr",
  Q27f = "dev. countr",
  Q27g = "plant/anim",
  Q27h = "the poor",
  Q27i = "nat. env."
)

climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q27_vars) %>% 
  gather(key = "item", value = "response", Q27_vars) %>% 
  ggplot(aes(x = response)) +
  geom_histogram() + 
  facet_grid(item ~ ., labeller = labeller(item = Q27_var_names)) +
  ggtitle("Distribution of Question 27 responses for civil engineering") +
  ylab("Count") +
  xlab("Item Response") +
  theme_bw() +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        strip.text.y = element_text(size = 7))




```



### Question 28 histograms

```{r echo=FALSE, warning=FALSE, message=FALSE}

# Question 28 histograms
# climate_df %>% 
#   filter(Q29 == 4) %>% 
#   select(Q28_vars) %>% 
#   gather(key = "item", value = "response", Q28_vars) %>% 
#   ggplot(aes(x = response)) +
#   geom_histogram() + 
#   facet_grid(item ~ .) +
#   ggtitle("Distribution of Question 28 responses for civil engineering") +
#   ylab("Count") +
#   xlab("Item Response") +
#   theme_bw() +
#   theme(plot.title = element_text(size = 10))




Q28_var_names <- c(
  Q28a = "environ",
  Q28b = "moral",
  Q28c = "religious",
  Q28d = "soc. just.",
  Q28e = "politic",
  Q28f = "sci",
  Q28g = "eng",
  Q28h = "health",
  Q28i = "economic",
  Q28j = "security",
  Q28k = "agricul",
  Q28l = "poverty"
)

climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q28_vars) %>% 
  gather(key = "item", value = "response", Q28_vars) %>% 
  ggplot(aes(x = response)) +
  geom_histogram() + 
  facet_grid(item ~ ., labeller = labeller(item = Q28_var_names)) +
  ggtitle("Distribution of Question 28 responses for civil engineering") +
  ylab("Count") +
  xlab("Item Response") +
  theme_bw() +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        strip.text.y = element_text(size = 7))



```


Making list of plots instead

```{r echo=FALSE}

Q28_hist <- map2(.x = Q28_vars, 
                 .y = Q28_var_names, 
                 .f = ~ climate_df %>% 
  filter(Q29 == 4) %>% 
  select(.x) %>% 
  gather(key = "item", value = "response", .x) %>% 
  ggplot(aes(x = response)) +
  geom_histogram() + 
  facet_grid(item ~ .) +
  ggtitle("Distribution of Question 28 responses for civil engineering") +
  ylab("Count") +
  xlab("Item Response") +
  theme_bw() +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        strip.text.y = element_text(size = 7)))

for (i in seq_along(Q28_hist)) {
  Q28_hist[[i]]
}


```
