---
title: "IJSHE_students_coursework_climate_change"
author: "Shealy and Katz"
date: "2/13/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(broom)
library(knitr)
library(randomForest)
library(purrr)
library(purrrlyr)
library(RColorBrewer)
library(gmodels)
library(umap)
library(dbscan)
library(pixiedust)
library(jtools)
library(kableExtra)

library(sjPlot)
library(sjlabelled)
library(sjmisc)


knitr::opts_chunk$set(echo = TRUE)


```

## Analysis for 2020 IJSHE paper on engineering student curricular and co-curricular experiences and career interests 


```{r data processing, echo=FALSE, message=FALSE}

project_path <- "G:/My Drive/AK Faculty/Research/Projects/project students and climate change"
setwd(project_path)

climate_df <- read_csv("updated_climate_df_5.csv")


Q1_vars <- paste0("Q1", letters[1:20])
Q3_vars <- paste0("Q3", letters[1:7])
Q5_vars <- paste0("Q5", letters[1:10])
Q16_vars <- paste0("Q16", letters[1:13])
Q27_vars <- paste0("Q27", letters[1:9])
Q28_vars <- paste0("Q28", letters[1:12])
Q35_vars <- paste0("Q35", letters[1:9])
Q39_vars <- paste0("Q39", letters[1:9])

Q7_vars <- paste0("Q7", letters[1:22])
Q7tally_vars <- paste0("Q7", letters[1:22], "_tally")


# create a new dataframe for doing all the calculations
#rf_df <- climate_data

# rf_df <- rf_df %>% mutate_at(vars(Q1_vars), ~replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q3_vars), ~ replace_na(.,0))
# 
# #rf_df <- rf_df %>% mutate_at(vars(Q5_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q7_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q35_vars), ~ replace_na(., 0))
# 
# rf_df <- rf_df %>% mutate_at(vars(Q39_vars), ~ replace_na(., 0))
# 
# 
# rf_df <- rf_df %>% drop_na(Q28_vars)
# 
# rf_df <- rf_df %>% drop_na(Q16_vars)


#data read-in 
#climate_df <- read_csv("filtered_climate_survey_20200122.csv")


# drop the Q28 and Q27 items that had any NAs

#climate_df <- climate_df %>% drop_na(Q28_vars)
#climate_df <- climate_df %>% drop_na(Q27_vars) #should have 
dim(climate_df)


```



### Linear models



#### Research Question 1 
"What is the relationship between course topics and students’ interest to address the topic in their careers?"

``` {r echo=FALSE}


q16_abe_model <- lm(Q16_abe ~ Q7a_wt_sum + Q7b_wt_sum + Q7c_wt_sum + 
                      Q7d_wt_sum + Q7e_wt_sum + Q7f_wt_sum + Q7g_wt_sum +
                      Q7h_wt_sum + Q7i_wt_sum + Q7j_wt_sum + 
                      Q7k_wt_sum + Q7l_wt_sum + Q7m_wt_sum +
                      Q7n_wt_sum + Q7o_wt_sum + Q7p_wt_sum +
                      Q7q_wt_sum + Q7r_wt_sum + Q7s_wt_sum +
                      Q7t_wt_sum + Q7u_wt_sum + Q7v_wt_sum, data=climate_df)


#dust(q16_abe_model)

summary(q16_abe_model)

tab_model(q16_abe_model)


```





``` {r echo=FALSE}


q16_hijk_model <- lm(Q16_hijk ~ Q7a_wt_sum + Q7b_wt_sum + Q7c_wt_sum + 
                      Q7d_wt_sum + Q7e_wt_sum + Q7f_wt_sum + Q7g_wt_sum +
                      Q7h_wt_sum + Q7i_wt_sum + Q7j_wt_sum + 
                      Q7k_wt_sum + Q7l_wt_sum + Q7m_wt_sum +
                      Q7n_wt_sum + Q7o_wt_sum + Q7p_wt_sum +
                      Q7q_wt_sum + Q7r_wt_sum + Q7s_wt_sum +
                      Q7t_wt_sum + Q7u_wt_sum + Q7v_wt_sum, data=climate_df)
summary(q16_hijk_model)

#dust(q16_hijk_model)

tab_model(q16_hijk_model)

```





``` {r echo=FALSE}


q16_dfg_model <- lm(Q16_dfg ~ Q7a_wt_sum + Q7b_wt_sum + Q7c_wt_sum + 
                      Q7d_wt_sum + Q7e_wt_sum + Q7f_wt_sum + Q7g_wt_sum +
                      Q7h_wt_sum + Q7i_wt_sum + Q7j_wt_sum + 
                      Q7k_wt_sum + Q7l_wt_sum + Q7m_wt_sum +
                      Q7n_wt_sum + Q7o_wt_sum + Q7p_wt_sum +
                      Q7q_wt_sum + Q7r_wt_sum + Q7s_wt_sum +
                      Q7t_wt_sum + Q7u_wt_sum + Q7v_wt_sum, data=climate_df)
summary(q16_dfg_model)
#stargazer(q16_dfg_model)
#tidy(q16_dfg_model)
#glance(q16_dfg_model)

#dust(q16_dfg_model)

tab_model(q16_dfg_model)

tab_model(q16_abe_model, q16_dfg_model, q16_hijk_model)

```




### Research Question 2


"What is the relationship between undergraduate co-curricular experiences and topics engineering students want to address in their careers?"


```{r echo=FALSE}


q16_abe_q6_model <- lm(Q16_abe ~ Q6a_ind + Q6b_ind + Q6c_ind +
                         Q6d_ind + Q6e_ind + Q6f_ind +
                         Q6g_ind + Q6h_ind + Q6i_ind + Q6k_ind, data=climate_df)

summary(q16_abe_q6_model)

tab_model(q16_abe_q6_model)


```


```{r echo=FALSE}


q16_dfg_q6_model <- lm(Q16_dfg ~ Q6a_ind + Q6b_ind + Q6c_ind +
                         Q6d_ind + Q6e_ind + Q6f_ind +
                         Q6g_ind + Q6h_ind + Q6i_ind + Q6k_ind, data=climate_df)

summary(q16_dfg_q6_model)

tab_model(q16_dfg_q6_model)


```



```{r echo=FALSE}


q16_hijk_q6_model <- lm(Q16_hijk ~ Q6a_ind + Q6b_ind + Q6c_ind +
                         Q6d_ind + Q6e_ind + Q6f_ind +
                         Q6g_ind + Q6h_ind + Q6i_ind + Q6k_ind, data=climate_df)

summary(q16_hijk_q6_model)

tab_model(q16_hijk_q6_model)


tab_model(q16_abe_q6_model, q16_dfg_q6_model, q16_hijk_q6_model)

```



