---
title: "r_climate_framing"
author: "Katz and Shealy"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




```{r}

library(RColorBrewer)
library(tidyverse)
library(dbscan)
library(umap)
library(psych)
library(gmodels)
library(graphics)
library(knitr)
library(purrr)
library(tidytext)
library(ggmosaic)

library(quanteda)



```




```{r}

frame_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/proposals/proposal 1 - students and framing/framing/Results/results_w_version_column.csv")

frame_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/proposals/proposal 1 - students and framing/framing/Results/clustered_frame_df.csv")

frame_df <- frame_df %>% 
  mutate(Version = dplyr::case_when(Version == "technical" ~ "Technical",
                             Version == "social" ~ "Social",
                             Version == "control" ~ "Control"))

```



```{r}

# look at counts
frame_df %>% count(Version)

frame_df %>% count(Version, frequency)


```


```{r}
frame_df_long <- frame_df %>%
  add_count(Version, name = "version_total") %>% 
  pivot_longer(cols = Q1.1a:Q2.6b, names_to = "survey_item", values_to = "survey_response") %>% 
  select(Version, frequency, percent_freq, survey_item, survey_response, version_total) %>% 
  #filter(str_detect(survey_item, "a")) %>% 
  mutate(survey_response_num = case_when(survey_response == "Yes" ~ 1, 
                                         survey_response == "No" ~ 0))
  
  
```




```{r}
#display.brewer.all(colorblindFriendly = TRUE)

frame_df %>%
  add_count(Version, name = "version_total") %>% 
  pivot_longer(cols = Q1.1a:Q2.6b, names_to = "survey_item", values_to = "survey_response") %>% 
  select(Version, frequency, percent_freq, survey_item, survey_response, version_total) %>% 
  filter(str_detect(survey_item, "a")) %>% 
  mutate(survey_response_num = case_when(survey_response == "Yes" ~ 1, 
                                         survey_response == "No" ~ 0)) %>% 
  group_by(Version, survey_item) %>% 
  summarize(n = n(),
            perc_yes = round(sum(survey_response_num) / n * 100, 1)) %>% 
  ggplot(aes(x = Version, y = perc_yes, fill = Version)) +
  geom_col() +
  facet_wrap(survey_item ~ .) +
  theme_light() +
  theme(legend.position = "none") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Percent of Students in Each Group Selecting Each Credit",
       x = "Version",
       y = "Percentage of Group Selecting Credit") +
  theme(plot.title = element_text(size = 10, hjust = 0.5))

```

Double checking with mosaic plot

```{r}
# double check with a mosaic plot


cont_table_q11 <- table(frame_df$Version, frame_df$Q1.1a)
cont_table_q11
chisq.test(cont_table_q11)


mosaicplot(cont_table_q11, shade = TRUE, main = "Q1.1 for Framing Groups")


```


```{r}

# double check with a mosaic plot


cont_table_q23 <- table(frame_df$Version, frame_df$Q2.3a)
cont_table_q23
chisq.test(cont_table_q23, )


mosaicplot(cont_table_q23, shade = TRUE, main = "Q2.3 for Framing Groups")


test_df <- frame_df %>% filter(Version != "Social")

cont_table_q23 <- table(test_df$Version, test_df$Q2.3a)
cont_table_q23
chisq.test(cont_table_q23)


mosaicplot(cont_table_q23, shade = TRUE, main = "Q2.3 for Framing Groups")



```


Jittered boxplot of number of credits selected by each group


```{r}

frame_df %>% 
  ggplot(aes(x = Version, y = frequency, color = Version)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.3,
              height = 0.0,
              width = 0.3) +
  scale_y_continuous(limits = c(-0.1, 10),
                     breaks = c(0, 2, 4, 6, 8, 10)) +
  labs(title = "Number of Credits Selected by Framing Group",
       x = "Framing Group",
       y = "Number of Credits Selected") +
  theme_light() +
  scale_color_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0.5, size = 10),
        legend.position = "none")


```



Try logistic regression for effect sizes of treatment on binary outcomes for individual items

Modeling selection of 1.3a

```{r}
frame_df <- frame_df %>% 
  mutate(q13a_num = case_when(Q1.3a == "Yes" ~ 1,
                              Q1.3a == "No" ~ 0))

mod_13a <- glm(q13a_num ~ as.factor(Version), data = frame_df, family = binomial(link = 'logit'))
summary(mod_13a)

```

Logistic regression for Q2.6a binary selection

```{r}
frame_df <- frame_df %>% 
  mutate(q26a_num = case_when(Q2.6a == "Yes" ~ 1,
                              Q2.6a == "No" ~ 0))

mod_26a <- glm(q26a_num ~ as.factor(Version), data = frame_df, family = binomial(link = 'logit'))
summary(mod_26a)

```


Kruskal-Wallis test for non-parametric version of ANOVA

```{r}

freq_kruskal_res <- kruskal.test(frequency ~ Version, data = frame_df)
freq_kruskal_res

```




one-way ANOVA for frequency by treatment group

```{r}

freq_aov_res <- aov(frequency ~ Version, data = frame_df)
summary(freq_aov_res)

```

One-way ANOVA for percent frequency by treatment group

```{r}

perc_freq_aov_res <- aov(percent_freq ~ Version, data = frame_df)
summary(perc_freq_aov_res)

```



Text analysis


```{r}
frame_corpus <- frame_df_long %>% 
  rowid_to_column(var = "docid") %>% 
  filter(str_detect(survey_item, "b")) %>% 
  rename(text = survey_response) %>% 
  corpus()

#summary(frame_corpus)

```


```{r}

survey_items <- frame_df_long %>% 
  filter(str_detect(survey_item, "b"))%>%
  distinct(survey_item) %>% 
  pull()


for (i in survey_items){
  
  dfm_weight_version <- frame_corpus %>%
       corpus_subset(survey_item == i) %>%
       dfm(remove = stopwords("english"), remove_punct = TRUE) %>%
       dfm_weight(scheme = "prop")
  
  
  
  
  # Calculate relative frequency by president
  freq_weight <- textstat_frequency(dfm_weight_version, n = 10, groups = "Version")
  
  plot <- ggplot(data = freq_weight, aes(x = nrow(freq_weight):1, y = frequency)) +
       geom_point() +
       facet_wrap(~ group, scales = "free") +
       coord_flip() +
       scale_x_continuous(breaks = nrow(freq_weight):1,
                          labels = freq_weight$feature) +
       labs(x = NULL, 
            y = "Relative frequency",
            title = paste0("Top 10 Words by Group for Item ", i)) +
    theme(plot.title = element_text(hjust = 0.5))
  
  print(plot)

}




# # single version
# 
# dfm_weight_version <- frame_corpus %>%
#      corpus_subset(survey_item == "Q2.3b") %>%
#      dfm(remove = stopwords("english"), remove_punct = TRUE) %>%
#      dfm_weight(scheme = "prop")
# 
# 
# 
# 
# # Calculate relative frequency by president
# freq_weight <- textstat_frequency(dfm_weight_version, n = 10, groups = "Version")
# 
# ggplot(data = freq_weight, aes(x = nrow(freq_weight):1, y = frequency)) +
#      geom_point() +
#      facet_wrap(~ group, scales = "free") +
#      coord_flip() +
#      scale_x_continuous(breaks = nrow(freq_weight):1,
#                         labels = freq_weight$feature) +
#      labs(x = NULL, 
#           y = "Relative frequency")
# 


```





### Looking at clustered responses

```{r}

frame_df %>% select(Q1.3b, Q1.3b_cluster) %>% arrange(Q1.3b_cluster) %>% view()

```






