---
title: "jcee_analysis"
author: "Shealy and Katz"
date: "7/21/2020"
output:
  word_document: default
  html_document:
    df_print: paged
mainfont: Times New Roman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r loading, include=FALSE}
library(tidyverse)
library(dbscan)
library(umap)
library(psych)
library(gmodels)
library(graphics)
library(RColorBrewer)
library(knitr)
```



```{r include=FALSE}
setwd("G:/My Drive/AK Faculty/Research/Projects/project students and climate change")

#climate_df <- read_csv("filtered_climate_survey_20200122.csv")
#climate_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/updated_climate_df_2.csv")

climate_df <- read_csv("G:/My Drive/AK Faculty/Research/Projects/project students and climate change/climate_data.csv")

## Drop duplicates
climate_df <- climate_df %>% distinct(Litho, .keep_all = TRUE)


## Add in major as string instead of number

climate_df <- climate_df %>% 
  mutate(major = case_when(Q29 == 1 ~ "Aer/Oce",
                           Q29 == 2 ~ "Agr/Biol",
                           Q29 == 3 ~ "Bio",
                           Q29 == 4 ~ "Civ",
                           Q29 == 5 ~ "Che",
                           Q29 == 6 ~ "Con",
                           Q29 == 7 ~ "Comp",
                           Q29 == 8 ~ "Ele",
                           Q29 == 9 ~ "EngPhy",
                           Q29 == 10 ~ "Env/Eco",
                           Q29 == 11 ~ "Ind",
                           Q29 == 12 ~ "Mat",
                           Q29 == 13 ~ "Mec",
                           Q29 == 14 ~ "Min",
                           Q29 == 15 ~ "Nuc",
                           Q29 == 16 ~ "Softw",
                           Q29 == 17 ~ "Str/Arc",
                           Q29 == 18 ~ "Gen"))


```


Drop NAs for specific questions and filter out disciplines with fewer than 30 (the cutoff) students in sample

```{r}
climate_df <- climate_df %>% drop_na(Q29, Q20a, Q20b, Q20d, Q18k, Q22) %>% 
  drop_na(Q23a, Q23b, Q23c, Q23d, Q23e, Q23f, Q23g, Q23h, Q23i, Q23j) %>% 
  drop_na(Q24a, Q24b, Q24c, Q24d, Q24e, Q24f, Q24g, Q24h, Q24i, Q24j, Q24k) %>% 
  drop_na(Q25a, Q25b, Q25c) %>% 
  drop_na(Q26a, Q26b, Q26c, Q26d, Q26e, Q26f, Q26g, Q26h) %>% 
  drop_na(Q28a, Q28b, Q28c, Q28d, Q28e, Q28f, Q28g, Q28h, Q28i, Q28j, Q28k, Q28l) %>% 
  drop_na(Q37)

climate_df %>% count(Q29, sort = TRUE)
cutoff <- 30

climate_df <- climate_df %>% 
  rowid_to_column(var = "student_id")

climate_df <- climate_df %>% add_count(Q29, name = "major_count") %>% filter(major_count > cutoff)

climate_df %>% count(Q29, sort = TRUE)

count_tbl <- climate_df %>% count(Q29, major, sort = TRUE)

```


Major counts and percentages
```{r}
count_tbl %>% 
  mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
  mutate(cumulat_pct = round(cumsum(n)/sum(n)*100, 2)) %>% 
  kable()
```


Gender counts overall
```{r}
climate_df %>% count(Q37) %>% 
  mutate(pct_total = round((n / sum(n))*100, 2)) %>% 
  kable()
```



Gender counts by major
```{r}
climate_df %>% 
  count(Q29, major, Q37, name = "gender_in_major") %>% 
  kable()
  
  
  
```


```{r}
# group all disciplines together?


climate_df <- climate_df %>% mutate(Q29_binned = case_when(Q29 == 4 ~ "civil",
                                             TRUE ~ "other")) 


```


### Distribution of technical vs social for civil engineering students


Summary statistics for Q28 factor


```{r echo=FALSE}

climate_df <- climate_df %>% 
  mutate(Q28_social = Q28c + Q28d + Q28e + Q28j + Q28l,
         Q28_tech = Q28a + Q28f + Q28g + Q28h + Q28i + Q28k,
         Q28_social_norm = Q28_social / 5,
         Q28_tech_norm = Q28_tech / 6)

climate_df %>% 
  filter(Q29 == 4) %>% 
  select(Q28_social, Q28_tech, Q28_social_norm, Q28_tech_norm) %>% 
  gather(key = "item", value = "response_values") %>%
  group_by(item) %>% 
  summarize(mean = mean(response_values), sd = sd(response_values), n = n()) %>% 
  kable(digits = 2)

climate_df %>% count(Q29)

climate_df %>% 
  filter(Q29 == 4) %>% 
  ggplot(aes(x = Q28_tech_norm)) +
  geom_histogram(color = "white") +
  theme_bw() +
  labs(x = "Global warming is a 'technical' issue normalized score",
       y = "Number of civil engineering students") +
  ylim(0, 125)

climate_df %>% 
  filter(Q29 == 4) %>% 
  ggplot(aes(x = Q28_social_norm)) +
  geom_histogram(color = "white") +
  theme_bw() +
  labs(x = "Global warming is a 'social' issue normalized score",
       y = "Number of civil engineering students") +
  ylim(0, 125)


```


# RQ 1 - What do civil engineering students believe about global warming? (Q29d, Q18k, Q20a, Q20b, Q20d)



## Q18k - We should be taking stronger actions to address climate change

```{r}

climate_df <- climate_df %>% mutate(Q18k_bin =  case_when(Q18k == 0 | Q18k == 1 | Q18k == 2 ~ 0,
                                         Q18k == 3 | Q18k == 4 ~ 1))


cont_table_Q18k <- table(climate_df$Q29, climate_df$Q18k_bin)
cont_table_Q18k
chisq.test(cont_table_Q18k)


mosaicplot(cont_table_Q18k, shade = TRUE, main = "Major vs Q18k - We should take stronger action")

```


```{r}

cont_table_Q18k <- table(climate_df$Q29_binned, climate_df$Q18k_bin)
cont_table_Q18k
chisq.test(cont_table_Q18k)


mosaicplot(cont_table_Q18k, shade = TRUE, main = "Major vs Q18k - We should take stronger action")


```





```{r}
#civil_df <- climate_df %>% filter(Q29 == 4) %>% view()



climate_df <- climate_df %>% 
  mutate(Q20a_bin = case_when(Q20a == 0 | Q20a == 1 | Q20a == 2 ~ 0,
                                         Q20a == 3 | Q20a == 4 ~ 1)) %>% 
  mutate(Q20b_bin = case_when(Q20b == 0 | Q20b == 1 | Q20b == 2 ~ 0,
                                         Q20b == 3 | Q20b == 4 ~ 1)) %>% 
  mutate(Q20d_bin = case_when(Q20d == 0 | Q20d == 1 | Q20d == 2 ~ 0,
                                         Q20d == 3 | Q20d == 4 ~ 1)) 



```




## Plot for Major by Q20a
```{r}


#CrossTable(climate_df$Q29, climate_df$Q20a_bin, chisq = TRUE)


cont_table_Q20a <- table(climate_df$Q29, climate_df$Q20a_bin)
cont_table_Q20a
chisq.test(cont_table_Q20a)


mosaicplot(cont_table_Q20a, shade = TRUE, main = "Contingency table: Major vs Q20a - I am sure global warming is happening")

#contingency_tab <- xtabs(~ major + Q5d, data = climate_data, na.action = na.pass)
#contingency_tab



```


```{r}

cont_table_Q20a <- table(climate_df$Q29_binned, climate_df$Q20a_bin)
cont_table_Q20a
chisq.test(cont_table_Q20a)


mosaicplot(cont_table_Q20a, shade = TRUE, main = "Contingency table: Major vs Q20a - I am sure global warming is happening")

```




## Plot for Major by Q20b
```{r}


#CrossTable(climate_df$Q29, climate_df$Q20b_bin, chisq = TRUE)


cont_table_Q20b <- table(climate_df$Q29, climate_df$Q20b_bin)
cont_table_Q20b
chisq.test(cont_table_Q20b)


mosaicplot(cont_table_Q20b, shade = TRUE, main = "Contingency table: Major vs Q20b - Global warming caused by humans")


```


```{r}

cont_table_Q20b <- table(climate_df$Q29_binned, climate_df$Q20b_bin)
cont_table_Q20b
chisq.test(cont_table_Q20b)


mosaicplot(cont_table_Q20b, shade = TRUE, main = "Contingency table: Major vs Q20b - Global warming caused by humans")


```




## Plot for Major by Q20d
```{r}


cont_table_Q20d <- table(climate_df$Q29, climate_df$Q20d_bin)
cont_table_Q20d
chisq.test(cont_table_Q20d)


mosaicplot(cont_table_Q20d, shade = TRUE, main = "Contingency table: Major vs Q20d - Global warming important to me")


```


```{r}


cont_table_Q20d <- table(climate_df$Q29_binned, climate_df$Q20d_bin)
cont_table_Q20d
chisq.test(cont_table_Q20d)


mosaicplot(cont_table_Q20d, shade = TRUE, main = "Contingency table: Major vs Q20d - Global warming important to me")


```





## Q22 - What percentage of climate scientists think that human-caused global warming is happening?

```{r}

climate_df <- climate_df %>% mutate(Q22_bin = case_when(Q22 == 4 ~ 1,
                                          TRUE ~ 0))


cont_table_Q22 <- table(climate_df$Q29, climate_df$Q22_bin)
cont_table_Q22
chisq.test(cont_table_Q22)


mosaicplot(cont_table_Q22, shade = TRUE, main = "Major vs Q22 - Percentage of Scientists")


```


```{r}

cont_table_Q22 <- table(climate_df$Q29_binned, climate_df$Q22_bin)
cont_table_Q22
chisq.test(cont_table_Q22)


mosaicplot(cont_table_Q22, shade = TRUE, main = "Major vs Q22 - Percentage of Scientists")


```


Set colors for majors for all plots
```{r}
major_num <- length(unique(climate_df$Q29))

major_colors <- colorRampPalette(brewer.pal(9, "Set1"))(major_num)
```



## Q23 - I believe that a cause of global climate change is...

```{r}

climate_df <- climate_df %>%
  drop_na(Q23a, Q23b, Q23c, Q23d, Q23e, Q23f, Q23g, Q23h, Q23i, Q23j) %>% 
  mutate(Q23a_bin = case_when(Q23a == 0 | Q23a == 1 | Q23a == 2 ~ 0,
                                         Q23a == 3 | Q23a == 4 ~ 1)) %>% 
  mutate(Q23b_bin = case_when(Q23b == 0 | Q23b == 1 ~ 1,
                                          Q23b == 2| Q23b == 3 | Q23b == 4 ~ 0)) %>% 
  mutate(Q23c_bin = case_when(Q23c == 0 | Q23c == 1 ~ 1,
                                         Q23c == 2 | Q23c == 3 | Q23c == 4 ~ 0)) %>% 
  mutate(Q23d_bin = case_when(Q23d == 0 | Q23d == 1 | Q23d == 2 ~ 0,
                                         Q23d == 3 | Q23d == 4 ~ 1)) %>% 
  mutate(Q23e_bin = case_when(Q23e == 0 | Q23e == 1 ~ 1,
                                         Q23e == 2| Q23e == 3 | Q23e == 4 ~ 0)) %>% 
  mutate(Q23f_bin = case_when(Q23f == 0 | Q23f == 1 | Q23f == 2 ~ 0,
                                         Q23f == 3 | Q23f == 4 ~ 1)) %>% 
  mutate(Q23g_bin = case_when(Q23g == 0 | Q23g == 1 ~ 1,
                                         Q23g == 2 | Q23g == 3 | Q23g == 4 ~ 0)) %>% 
  mutate(Q23h_bin = case_when(Q23h == 0 | Q23h == 1 | Q23h == 2 ~ 0,
                                         Q23h == 3 | Q23h == 4 ~ 1)) %>% 
  mutate(Q23i_bin = case_when(Q23i == 0 | Q23i == 1 ~ 1,
                                         Q23i == 2 | Q23i == 3 | Q23i == 4 ~ 0)) %>% 
  mutate(Q23j_bin = case_when(Q23j == 0 | Q23j == 1 ~ 1,
                                         Q23j == 2 | Q23j == 3 | Q23j == 4 ~ 0)) %>% 
  mutate(Q23_bin_total = Q23a_bin + Q23b_bin + Q23c_bin + Q23d_bin + Q23e_bin + 
           Q23f_bin + Q23g_bin + Q23h_bin + Q23i_bin + Q23j_bin) %>% 
  mutate(Q23_bin_total_pct = (Q23_bin_total/10) * 100)
  



climate_df %>% 
  ggplot(aes(x = major, y = Q23_bin_total_pct, fill = major)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q23 percent correct",
       title = "Q23 Score (Causes of climate change) by major")



```




### ANOVA for Q23 scores by major

```{r}

res.aov <- aov(Q23_bin_total ~ major, data = climate_df)
summary(res.aov)

TukeyHSD(res.aov)



```


### T-test for Q23 scores by civl vs others


```{r}


climate_df %>% 
  ggplot(aes(x = as_factor(Q29_binned), y = Q23_bin_total, fill = Q29_binned)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q23 cumulative score",
       title = "Q23 Score (Causes of climate change) by major")



```

Checking t-test assumptions

```{r}
# test assumptions for t-test
with(climate_df, shapiro.test(Q23_bin_total[Q29_binned == "civil"]))
with(climate_df, shapiro.test(Q23_bin_total[Q29_binned == "other"]))

## failed normality assumption


#equal variance test - passed this test

res.ftest <- var.test(Q23_bin_total ~ Q29_binned, data = climate_df)
res.ftest

res <- t.test(Q23_bin_total ~ Q29_binned, data = climate_df, var.equal = FALSE)
res





```




## Q24 - I believe a way to help reduce or slow down climate change is...

```{r}


climate_df <- climate_df %>%
  drop_na(Q24a, Q24b, Q24c, Q24d, Q24e, Q24f, Q24g, Q24h, Q24i, Q24j, Q24k) %>% 
  mutate(Q24a_bin = case_when(Q24a == 0 | Q24a == 1 | Q24a == 2 ~ 0,
                                         Q24a == 3 | Q24a == 4 ~ 1)) %>% 
  mutate(Q24b_bin = case_when(Q24b == 0 | Q24b == 1 | Q24b == 2 ~ 0,
                                         Q24b == 3 | Q24b == 4 ~ 1)) %>% 
  mutate(Q24c_bin = case_when(Q24c == 0 | Q24c == 1 | Q24c == 2 ~ 0,
                                         Q24c == 3 | Q24c == 4 ~ 1)) %>% 
  mutate(Q24d_bin = case_when(Q24d == 0 | Q24d == 1 ~ 1,
                                          Q24d == 2 | Q24d == 3 | Q24d == 4 ~ 0)) %>% 
  mutate(Q24e_bin = case_when(Q24e == 0 | Q24e == 1 | Q24e == 2 ~ 0,
                                         Q24e == 3 | Q24e == 4 ~ 1)) %>% 
  mutate(Q24f_bin = case_when(Q24f == 0 | Q24f == 1 ~ 1,
                                         Q24f == 2 | Q24f == 3 | Q24f == 4 ~ 0)) %>% 
  mutate(Q24g_bin = case_when(Q24g == 0 | Q24g == 1 | Q24g == 2 ~ 0,
                                         Q24g == 3 | Q24g == 4 ~ 1)) %>% 
  mutate(Q24h_bin = case_when(Q24h == 0 | Q24h == 1 | Q24h == 2 ~ 0,
                                         Q24h == 3 | Q24h == 4 ~ 1)) %>% 
  mutate(Q24i_bin = case_when(Q24i == 0 | Q24i == 1 ~ 1,
                                         Q24i == 2 | Q24i == 3 | Q24i == 4 ~ 0)) %>% 
  mutate(Q24j_bin = case_when(Q24j == 0 | Q24j == 1 | Q24j == 2 ~ 0,
                                         Q24j == 3 | Q24j == 4 ~ 1)) %>%
  mutate(Q24k_bin = case_when(Q24k == 0 | Q24k == 1 | Q24k == 2 ~ 0,
                                         Q24k == 3 | Q24k == 4 ~ 1)) %>% 
  mutate(Q24_bin_total = Q24a_bin + Q24b_bin + Q24c_bin + Q24d_bin + Q24e_bin + 
           Q24f_bin + Q24g_bin + Q24h_bin + Q24i_bin + Q24j_bin + Q24k_bin) %>% 
  mutate(Q24_bin_total_pct = (Q24_bin_total/11) * 100)
  


climate_df %>% 
  ggplot(aes(x = major, y = Q24_bin_total_pct, fill = major)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q24 percent correct",
       title = "Q24 Score (Ways to slow down climate change) by major")



```


```{r}


climate_df %>% 
  ggplot(aes(x = as_factor(Q29_binned), y = Q24_bin_total_pct, fill = Q29_binned)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q24 cumulative score",
       title = "Q24 Score (slow down climate change) by major")

```

```{r}

res <- t.test(Q24_bin_total ~ Q29_binned, data = climate_df, var.equal = FALSE)
res

```







## Q25 Which of the following...
(a) is the most abundant greenhouse gas
(b) amplifies the greenhouse gas effect the most?
(c) should we be most concerned about when thinking about global warming? CO2


```{r}

climate_df <- climate_df %>% 
  mutate(Q25a_bin = case_when(Q25a == 2 ~ 1,
                              TRUE ~ 0),
         Q25b_bin = case_when(Q25b == 3 ~ 1,
                              TRUE ~ 0),
         Q25c_bin = case_when(Q25c == 1 ~ 1,
                              TRUE ~ 0))


```


### Q25a

```{r}


cont_table_Q25a <- table(climate_df$Q29, climate_df$Q25a_bin)
cont_table_Q25a
chisq.test(cont_table_Q25a)


mosaicplot(cont_table_Q25a, shade = TRUE, main = "Major vs Q25a - Most abundant greenhouse gas")


```


```{r}

cont_table_Q25a <- table(climate_df$Q29_binned, climate_df$Q25a_bin)
cont_table_Q25a
chisq.test(cont_table_Q25a)


mosaicplot(cont_table_Q25a, shade = TRUE, main = "Civil vs others - Q25a - Most abundant greenhouse gas")


```




### Q25b


```{r}


cont_table_Q25b <- table(climate_df$Q29, climate_df$Q25b_bin)
cont_table_Q25b
chisq.test(cont_table_Q25b)


mosaicplot(cont_table_Q25b, shade = TRUE, main = "Major vs Q25b - Amplifies greenhouse gas effect most")


```


```{r}

cont_table_Q25b <- table(climate_df$Q29_binned, climate_df$Q25b_bin)
cont_table_Q25b
chisq.test(cont_table_Q25b)


mosaicplot(cont_table_Q25b, shade = TRUE, main = "Civil vs others - Q25b - Amplifies greenhouse gas effect most")


```



Q25c



```{r}


cont_table_Q25c <- table(climate_df$Q29, climate_df$Q25c_bin)
cont_table_Q25c
chisq.test(cont_table_Q25c)


mosaicplot(cont_table_Q25c, shade = TRUE, main = "Major vs Q25c - Most concerning")


```


```{r}

cont_table_Q25c <- table(climate_df$Q29_binned, climate_df$Q25c_bin)
cont_table_Q25c
chisq.test(cont_table_Q25c)


mosaicplot(cont_table_Q25c, shade = TRUE, main = "Civil vs others - Q25c - Most concerning")


```






## Q26 - How much do you agree or disagree with the following statements about Earth's climate?


Recoding Q26 for t/F and then creating a total score out of 8
```{r}

climate_df <- climate_df %>%
  drop_na(Q26a, Q26b, Q26c, Q26d, Q26e, Q26f, Q26g, Q26h) %>% 
  mutate(Q26a_bin = case_when(Q26a == 0 | Q26a == 1 ~ 1,
                                         Q26a == 2 | Q26a == 3 | Q26a == 4 ~ 0)) %>% 
  mutate(Q26b_bin = case_when(Q26b == 0 | Q26b == 1 ~ 1,
                                          Q26b == 2| Q26b == 3 | Q26b == 4 ~ 0)) %>% 
  mutate(Q26c_bin = case_when(Q26c == 0 | Q26c == 1 ~ 1,
                                         Q26c == 2 | Q26c == 3 | Q26c == 4 ~ 0)) %>% 
  mutate(Q26d_bin = case_when(Q26d == 0 | Q26d == 1 | Q26d == 2 ~ 0,
                                         Q26d == 3 | Q26d == 4 ~ 1)) %>% 
  mutate(Q26e_bin = case_when(Q26e == 0 | Q26e == 1 ~ 1,
                                         Q26e == 2| Q26e == 3 | Q26e == 4 ~ 0)) %>% 
  mutate(Q26f_bin = case_when(Q26f == 0 | Q26f == 1 | Q26f == 2 ~ 0,
                                         Q26f == 3 | Q26f == 4 ~ 1)) %>% 
  mutate(Q26g_bin = case_when(Q26g == 0 | Q26g == 1 ~ 1,
                                         Q26g == 2 | Q26g == 3 | Q26g == 4 ~ 0)) %>% 
  mutate(Q26h_bin = case_when(Q26h == 0 | Q26h == 1 ~ 1,
                                         Q26h == 2 | Q26h == 3 | Q26h == 4 ~ 0)) %>% 
  mutate(Q26_bin_total = Q26a_bin + Q26b_bin + Q26c_bin + Q26d_bin + Q26e_bin + Q26f_bin + Q26g_bin + Q26h_bin) %>% 
  mutate(Q26_bin_total_pct = (Q26_bin_total/8) * 100)
  

```



```{r}
climate_df %>% 
  ggplot(aes(x = major, y = Q26_bin_total_pct, fill = major)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q26 percent correct",
       title = "Q26 Score (Statements about Earth's climate) by major")



```


```{r}


climate_df %>% 
  ggplot(aes(x = as_factor(Q29_binned), y = Q26_bin_total, fill = Q29_binned)) +
  geom_boxplot() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q26 cumulative score",
       title = "Q26 Score (Statements about Earth's climate) by major")

```

```{r}

res <- t.test(Q26_bin_total ~ Q29_binned, data = climate_df, var.equal = FALSE)
res

```





### Q26 EFA

```{r}

climate_df <- climate_df %>% 
  mutate(Q26a_rev = 4 - Q26a,
         Q26b_rev = 4 - Q26b,
         Q26c_rev = 4 - Q26c,
         Q26g_rev = 4 - Q26g,
         Q26h_rev = 4 - Q26h)
climate_df %>% select(Q26a, Q26a_rev, Q26b, Q26b_rev, Q26d)

q26_cor <- climate_df %>% 
  select(Q26a_rev, Q26b_rev, Q26c_rev, Q26d, Q26e, Q26f, Q26g_rev, Q26h_rev) %>% 
  drop_na() %>% 
  cor()
  
q26_efa <- fa(r = q26_cor, nfactors = 2)
q26_efa

```



#### There appear to be two factors from Q26 - one for low information (items a, b, c, g, and h) and one for higher information (d, e, f)


Create two new factors for Q26 (Q26_low_info, from the reverse-coded a,b,c,g,h and Q26_high_info from d,e,f)

```{r}

climate_df <- climate_df %>% 
  mutate(Q26_low_info = (Q26a_rev + Q26b_rev + Q26c_rev + Q26g_rev + Q26h_rev) / 5,
         Q26_high_info = (Q26d + Q26e + Q26f) / 3)


```


#### Compare scores for low info among different majors
```{r}

climate_df %>% 
  ggplot(aes(x = major, y = Q26_low_info, fill = major)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q26 cumulative low info score",
       title = "Q26 low info factor Score by major")

```

ANOVA for Q26 factor 1 (low_info score)

```{r}



```





```{r}

climate_df %>% 
  ggplot(aes(x = major, y = Q26_high_info, fill = major)) +
  geom_boxplot() +
  scale_fill_manual(values = major_colors) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Major",
       y = "Q26 cumulative high info score",
       title = "Q26 high info factor Score by major")

```









## Attempt to combine all tests together

### Q23 - I believe that a cause of global climate change is...

```{r}
#Q7_tally_vars <- paste0("Q7", letters[0:22], "_tally")

## NOTE: Q29_binned is civil vs other

Q23_bin_vars <- paste0("Q23", letters[0:10], "_bin")

climate_df %>% drop_na(Q29, Q18c, Q20a, Q20b, Q20d, Q18k, Q22) %>% 
  drop_na(Q23a, Q23b, Q23c, Q23d, Q23e, Q23f, Q23g, Q23h, Q23i, Q23j) %>% 
  drop_na(Q24a, Q24b, Q24c, Q24d, Q24e, Q24f, Q24g, Q24h, Q24i, Q24j, Q24k) %>% 
  drop_na(Q25a, Q25b, Q25c) %>% 
  drop_na(Q26a, Q26b, Q26c, Q26d, Q26e, Q26f, Q26g, Q26h) %>% 
  drop_na(Q28a, Q28b, Q28c, Q28d, Q28e, Q28f, Q28g, Q28h, Q28i, Q28j, Q28k, Q28l)


belief_cause_df <- climate_df %>% 
  select(student_id,
         Q29_binned, 
         Q23_bin_vars) %>% 
  pivot_longer(cols = Q23a_bin:Q23j_bin, 
               names_to = "Q23_bin_item", values_to = "Q23_bin_resp")


belief_cause_df %>% 
  group_by(Q23_bin_item, Q29_binned) %>% 
  count(Q23_bin_resp)

```


            

```{r}
#nested$data[1]

nested <- belief_cause_df %>% 
  mutate(Q29_binned = as_factor(Q29_binned)) %>% 
  group_by(Q23_bin_item) %>% 
  nest(data = c(student_id, Q29_binned, Q23_bin_resp)) %>% 
  mutate(
    Q23_item_name = case_when(
      Q23_bin_item == "Q23a_bin" ~ "Burning fossil fuels", 
      Q23_bin_item == "Q23b_bin" ~ "Nuclear power generation",
      Q23_bin_item == "Q23c_bin" ~ "Ozone hole in upper atmos.",
      Q23_bin_item == "Q23d_bin" ~ "Livestock production",
      Q23_bin_item == "Q23e_bin" ~ "Drumping trash into oceans",
      Q23_bin_item == "Q23f_bin" ~ "Waste rotting in landfills",
      Q23_bin_item == "Q23g_bin" ~ "Agricultural use of chem. fert.",
      Q23_bin_item == "Q23h_bin" ~ "Deforestation",
      Q23_bin_item == "Q23i_bin" ~ "Volcanic eruptions",
      Q23_bin_item == "Q23j_bin" ~ "Acid rain"),
    cont_tab = purrr::map(data, ~table(.$Q29_binned, .$Q23_bin_resp)),
    test = purrr::map(data, ~chisq.test(.$Q29_binned, .$Q23_bin_resp)),
    tidied = purrr::map(test, tidy),
    m_plot = mosaicplot(cont_tab[[1]], shade = TRUE, main = Q23_item_name)
    )




```



```{r}

nested %>% 
  select(Q23_bin_item, Q23_item_name, tidied) %>% 
  unnest(tidied) %>% 
  kable()


```


